### 2015-11-02 paper/chaining.tex
Adding initial version of writeup.

%!TEX TS-program = pdflatexmk

%\documentclass{sig-alt-hotnetscr}
\documentclass[12pt]{article}

\input{setup}

\begin{document}
\clubpenalty=10000
\widowpenalty = 10000
\thispagestyle{empty}

\input{title}
\input{protocol}
\input{discussion}

\bibliographystyle{abbrv}

\bibliography{bibinfo2}

%\endgroup

\end{document}

### 2015-11-02 paper/discussion.tex
Adding initial version of writeup.

\section{Discussion}

\subsection{Correctness of Output}

If all parties behave in an honest or honest-but-curious way in following to the protocols above, then the agencies' outputs will be $\mathbf{C}$ and $\mathbf{H}$. $\mathbf{C}$ will contain agency ciphertexts of all phone numbers at most $k$ phone calls away from $x$, considering only vertices of degree at most $l$. $\mathbf{H}$ will contain the phone numbers in $\mathbf{C}$ that have degree $l$ or greater, not including $x$ itself. This is the desired output. $C$ and $H$ reveal nothing to any agencies unless they all provide their decryption keys. Each encrypted phone number \emph{could} be decrypted by all agencies in pursuit of a lawful investigation, or be used as input to a lawful private set intersection protocol as described in~\cite{bandits}.

Both lists are likely to contain duplicates. There may be multiple paths from one user to another, especially due to triangles and cliques in the graph. Although further investigation should not be affected by these duplicate elements, they could be eliminated from the output sets, if desired. This could be done by modifying the privacy-preserving set intersection protocol of~\cite{bandits}. In that protocol, there is a step where all ciphertexts are encrypted under deterministic encryption, so that repeated elements can be identified. At that step, instead of completing the decryption of repeated elements, the extra ciphertexts can be discarded, and all remaining ciphertexts can be re-encrypted with a probablistic encryption scheme.

\subsection{Privacy}

Both versions of the protocol hide the identities of the chained contacts of $x$. They do allow the agencies to learn about edges between ciphertexts in their output, but these ciphertexts cannot be resolved to phone numbers without the cooperation of all agencies.

The protocol of section~\ref{sec:proto1} allows the agencies to learn which telecoms own the ciphertexts in $\mathbf{C}$ and $\mathbf{H}$. They will learn which telecom owns which ciphertext. This may be a security concern, since some telecoms are relatively small or specialized. If the agencies know that such a such a telecom owns an encrypted phone number, this will not allow them to identify the phone number itself, but might convince the agencies to subject that ciphertext to additional scrutiny. This concern is addressed by our revised protocol. Assuming that the anonymity protocol used in section~\ref{sec:proto2} does not allow its participants to learn who sends each message, then the revised protocol does not leak this information.

The telecoms learn two types of information as part of the lawful contact chaining protocol. First, they learn the warrant. Second, they learn which of the phone numbers they serve have been captured (in encrypted form) by the protocol, and when they were captured. The telecoms might possibly be able to infer some extra information about $G$ from observing when vertices they own are queried by the agencies, but they can probably not be able to learn any particular edges of $G$. For example, an agency may serve two phone numbers, $a$ and $b$, and it may infer from timing information that $a$ is queried at distance 1 from $x$, and $b$ is queried at distance 4 from $x$. In that case, the telecom can infer that there exists a path in $G$ of length 3 between $a$ and $b$. This is a very limited form of information. We note that telecoms do not learn which other phones are involved in that path, and that they are already aware of all paths of length 2 or less between phone numbers they serve.

### 2015-11-02 paper/protocol.tex
Adding initial version of writeup.

\section{Protocols For Privacy-Preserving Contact Chaining}

This is a candidate protocol for privacy-preserving contact chaining. The desired inputs, outputs, and security assumptions are given below.

\subsection{Inputs and Parties to the Protocol}

There are two types of parties in this protocol: Telecommunications companies (telecoms) and government agencies interested in performing lawful contact-chaining (agencies). The protocol is a function of all parties' data.

The telecoms jointly hold an undirected call graph $G=(V,E)$. Each telecom knows only a subset of the edges $E$. In this graph, the vertices in $V$ are labeled with the phone numbers they represent. $E$ contains an edge between $a$ and $b$ if and only if phone number $a$ has dialed phone number $b$ or vice versa within some window of time. The set of existing phone numbers $V$ is public information. Additionally, each phone number $v$ is served by exactly one telecom. We assume all parties to the protocol know (or can discover) which telecom serves which phone number. Each telecom keeps records of all phone calls made by phones they serve, including calls made to phone numbers served by other telecoms. The subgraph known by telecom $T$ is $G_T=(V, E_T)$ where $E_T$ is the set of edges $(a, b)$ such that $a$ or $b$ is a phone number served by $T$. Henceforth, for any phone number $a$, let $T(a)$ be the telecom that serves $a$.

In addition to the public knowledge about $V$ and which telecom serves which phone number, the agencies must each hold a copy of a \emph{warrant} in order to perform this protocol. A warrant must include at least the information $(x, k)$, where $x$ is a target phone number and $k$ is a (small) distance from $x$. For example, if $k=2$, then the agencies only wish to consider users at most 2 phone calls away from their person (or phone number) of interest $x$. Choosing a small limit is important to limiting the scope of the investigation. However, many users' information might still be captured if some phone numbers have very many contacts. Suppose the target $x$ calls the most popular pizza place in town. Now everyone else who has recently called that pizza place is at a distance 2 to $x$.

The warrant must therefore also specify additional mechanisms for limiting the scope of the investigation. We specifically require two additional values to be part of the warrant. The first is a branching limit $l$. If a vertex has degree greater than $l$, the agencies will not consider paths through that vertex in determining whether there is a path of length at most $k$ between two vertices. This mechanism prevents very busy phone numbers, such as that of the pizza restaurant or a taxi service, from introducing very many unrelated phone numbers into the eventual data set. The second is $m$, a maximum number of encrypted users that the agencies are willing to consider in total. Once the agencies have added $m$ encrypted phone numbers to their output, they halt their investigation. This sets an absolute upper limit on the number of users whose data can be captured by contact chaining.

\subsection{Security Assumptions}

We treat all parties to this protocol as honest-but-curious. All telecoms and agencies must have a published public encryption key and private decryption key. The agencies' keys must be for a commutative cryptosystem (i.e. ElGamal). The agencies must also each have private signing keys and public verification keys.

We may assume for this protocol that one of the agencies in particular, which we may call the ``investigating agency'', is responsible for all communication to and from every telecom. The investigating agency itself communicates with one or more other agencies, which we call ``oversight agencies''. Oversight agencies are responsible for approving warrants, collecting statistics and other information about how often the protocol is run, and enforcing the protocol's scope limiting mechanisms.

In the protocol below, we refer to ``the agencies'' sending messages to one or more telecoms, for clarity. What we mean by this is that the investigating agency creates the message, gets a signature on the message from each oversight agency, and sends the message with all signatures to the telecom. If a telecom receives a message without signatures from all oversight agencies, it rejects the message as invalid.

\subsection{Desired Outputs and Security Properties}

The desired output of the protocol is for the agencies to learn an \emph{encryption} of the set of phone numbers within distance $k$ of the targeted phone $x$ in the call graph. Every phone number in this set must be encrypted with each of the agencies' public keys. The encrypted set may exclude a phone number if the only paths of length at most $k$ connecting it to $x$ go through vertices with degree greater than the limit $l$, but then (encryptions of) all such high-degree vertices must also noted in the output. The agencies should all have the same output.

The telecoms do not expect any output from this protocol.

With the encryptions of these phone numbers, the agencies can then act as appropriate to further investigate them. In particular, the encrypted set of phone numbers can be used as an input into a privacy-preserving set intersection protocol, as in~\cite{bandits}.

Below, we present two versions of our protocol. In the basic version, the agencies and telecoms learn some additional information. Specifically, the agencies learn the provider of each phone number in the encrypted set, and a set of encrypted edges between vertices in this set; that is, they learn pairs of the form $(\tilde{a}, \tilde{b})$, where $\tilde{a}$ and $\tilde{b}$ both appear in the agencies' output and $(a, b)\in E$. The telecoms to learn which of the phone numbers it serves appear in the agencies' output, and the distance of each of those phone numbers from the target phone number $x$.

In section \ref{sec:proto2}, we will present a version of the protocol in which the agency \emph{does not} learn any additional information.

The agencies collectively learn \emph{no} information about the edge set $E$ except what is implied by the output. Furthermore, as long as at least one agency does not collude with the others, the remaining agencies must not be able to learn any of the phone numbers that appear in encrypted form in the output, unless it is implied by the size of the encrypted output and the leaked service information.

\subsection{First Protocol: Leaks Telecom Ownership}
\label{sec:proto1}

The protocol below amounts to a distributed breadth-first search of the social graph run by the agencies making queries of the telecoms. However, all messages the agencies receive from the telecoms will be encrypted. The only information that is leaked in the clear to the agencies is \emph{ownership information} about the encrypted phone numbers - specifically, which telecoms own the vertices in the encrypted output.

Let $\Enc_T(m)$ be the encryption of message $m$ under telecom $T$'s public key. Call such an encryption a \emph{telecom ciphertext}. Let $\Enc_\mathcal{A}(m)$ be the encryption of $m$ under the public keys of all agencies, and call such an encryption an \emph{agency ciphertext}.

To manage the breadth-first search, the agencies (or at least the investigating agency) will maintain a queue $\mathbf{Q}$, containing vertices yet to explore. $\mathbf{Q}$ contains triples for unexplored vertices $a$ of the form $(\Enc_{T(a)}(a), T(a), j)$. These tuples contain the telecom ciphertext for $a$, a record of which telecom owns $a$, and an integer $j$ indicating the distance to $a$ from the target vertex.

The agencies will represent their output in the form of two lists: $\mathbf{C}$, containing agency ciphertexts collected as a result of the contact chaining, and $\mathbf{H}$, containing high-degree vertices through which the agencies decided not to chain, along with their distances from the target. The agencies may, after the protocol, decide to decrypt the phone numbers in $\mathbf{H}$, and may then continue chaining through them by running the contact-chaining protocol starting with one of those phone numbers.

The protocol is as follows:

\bce
\item The agencies start by agreeing upon a warrant $(x, k, l)$, where $x$ is the target phone number, $k$ is a maximum distance, and $l$ is an upper limit on the degree of vertices to chain through. They encrypt $x$ under the public key of $T(x)$.
\item The agencies initialize a queue $\mathbf{Q}$. Initially, $\mathbf{Q}$ contains only the triple $(\Enc_{T(x)}(x), T(x), 0)$.
\item The agencies initialize the output lists $\mathbf{C}$ and $\mathbf{H}$ to be empty.
\item While $\mathbf{Q}$ is not empty, do the following:
\bce
\item \label{proto1:top-of-loop} The agencies dequeue $(\Enc_{T(a)}(a), T(a), j)$ from $\mathbf{Q}$. They send the telecom ciphertext $\Enc_{T(a)}(a)$ to $T(a)$.
\item $a$'s provider, $T(a)$, decrypts $a$ from its telecom ciphertext.
\item \label{proto1:first-send} $T(a)$ encrypts $a$ under the agencies' public keys, and sends $\Enc_\mathcal{A}(a)$ to the agencies.
\item The agencies add $\Enc_\mathcal{A}(a)$ to $\mathbf{C}$. If $j=k$, they send the message ``DONE'' to $T(a)$, and go to step~\ref{proto1:top-of-loop}.
\item Otherwise, the agencies send the message ``CONTINUE'' to $T(a)$.
\item Upon receiving the message ``CONTINUE'', $T(a)$ encrypts each neighbor $b$ of $a$ under the public key of $T(b)$, creating a telecom ciphertext for $b$.
\item \label{proto1:second-send} $T(a)$ sends all telecom ciphertexts for $a$'s neighbors to the agencies, in the form of pairs $(\Enc_{T(b)}(b), T(b))$.
\item If the agencies receive more than $l$ ciphertexts in the previous step (and $j\neq 0$), they add $(\Enc_\mathcal{A}(a), j)$ to $\mathbf{H}$. They discard the telecom ciphertexts (i.e., agencies refuse to sign the ciphertexts or send them on to the telecoms).
\item Otherwise, for each telecom ciphertext received, the agencies add the tuple $(\Enc_{T(b)}(b), T(b), j+1)$ to $\mathbf{Q}$.
\ece
\item The agencies' final outputs are the lists $\mathbf{C}$ and $\mathbf{H}$.
\ece

\subsection{Revised Contact Chaining Protocol}
\label{sec:proto2}

The previous version of the protocol allows agencies to learn which telecoms own the phone numbers in its encrypted output. This subsection presents a modification of the previous version of the protocol, which uses a DC-nets-based \emph{anonymity protocol} to hide this information from the agencies.

An anonymity  protocol is run between a number of parties, some of which have a message to send. At the end of the protocol, all parties must learn all messages sent, but no party other than the sender of any given message learns which party sent that message. Dissent~\cite{dissent} and Verdict~\cite{verdict} both satisfy our requirements, although they are more powerful than we need here, since we assume all telecoms are honest-but-curious.

We can use an anonymity protocol to allow the correct telecom to respond anonymously in steps \ref{proto1:first-send} and \ref{proto1:second-send} in the protocol above. This removes the need for the agencies to know which telecom owns which ciphertext.

Now we can present the following modified protocol. This protocol uses the same data structures as in section~\ref{sec:proto1}, except that $\mathbf{Q}$ now contains pairs $(\Enc_{T(a)}(a), j)$ for unexplored vertices $a$.

\bce
\item The agencies start by agreeing upon a warrant $(x, k, l)$, where $x$ is the target phone number, $k$ is a maximum distance, and $l$ is an upper limit on the degree of vertices to chain through. They encrypt $x$ under the public key of $T(x)$.
\item The agencies initialize a queue $\mathbf{Q}$. Initially, $\mathbf{Q}$ contains only the pair $(\Enc_{T(x)}(x), 0)$.
\item The agencies initialize the output lists $\mathbf{C}$ and $\mathbf{H}$ to be empty.
\item While $\mathbf{Q}$ is not empty, do the following:
\bce
\item \label{proto2:dequeue} The agencies dequeue a number of pairs $(\Enc_{T(a)}(a), j)$ from $\mathbf{Q}$. They send each telecom ciphertext $\Enc_{T(a)}(a)$ to all telecoms, along with the message ``CONTINUE'' if $j<k$, or the message ``DONE'' if not.
\item All telecoms attempt to decrypt the telecom ciphertexts. For each vertex $a$, $a$'s provider, $T(a)$, will decrypt $a$. 
\item $T(a)$ encrypts $a$ under the agencies' public keys to produce the agency ciphertext $\Enc_\mathcal{A}(a)$.
\item If $T(a)$ got the message ``CONTINUE'' along with the ciphertext, it also encrypts each neighbor $b$ of $a$ under the public key of $T(b)$, creating a telecom ciphertext for $b$.
\item All parties to this protocol engage in an anonymity protocol. Each telecom's message in the protocol is the set of all agency ciphertexts and all telecom ciphertexts produced in the previous two steps. If the telecom did not produce any messages in the previous two steps, it participates in the protocol but sends no message.
\item When the anonymity protocol is complete, the agencies receive all the ciphertexts.
\item For each agency ciphertext $\Enc_\mathcal{A}(a)$ the agencies receive, they add that ciphertext to $\mathbf{C}$.
\item If the agencies receive more than $l$ telecom ciphertexts for any vertex $a$ in the previous step (and $j\neq 0$), they add $(\Enc_\mathcal{A}(a), j)$ to $\mathbf{H}$. They discard the associated telecom ciphertexts (i.e., agencies refuse to sign the ciphertexts or send them on to the telecoms).
\item Otherwise, for each telecom ciphertext received, the agencies add the pair $(\Enc_{T(b)}(b), j+1)$ to $\mathbf{Q}$.
\ece
\item The agencies' final outputs are the lists $\mathbf{C}$ and $\mathbf{H}$.
\ece

The protocol replaces each query in the protocol of section~\ref{sec:proto1} with broadcast of the telecom ciphertext to all telecoms, and replaces each response with a round of the anonymity protocol. The agencies can in theory dequeue the entire queue in step~\ref{proto2:dequeue}, but they may choose to limit the number of queries made at once for practical purposes.

### 2015-11-24 paper/discussion.tex
Revised paper, including budget mechanism.

@@
 \section{Discussion}
+\label{sec:discuss}
 
@@
 We note that telecoms do not learn which other phones are involved in that path, and that they are already aware of all paths of length 2 or less between phone numbers they serve.
+
+\subsection{Hiding Information From Telecoms}
+\label{sec:oblivious}
+
+In both versions of our protocol, the telecoms learn which of their numbers have been submitted to the agencies.
+They do not know which phone numbers the agencies will actually investigate after running the privacy-preserving set intersection protocol, but they do know which ones \emph{could} be under investigation.
+Since many numbers \emph{could} be investigated, this does not compromise the agencies' investigative power.
+
+We may point out nevertheless that a modification of our protocol from \ref{sec:proto1} could allow the agencies to hide from the telecoms which of their clients is being surveilled.
+The telecoms would need to precompute agency ciphertexts for all of their client numbers, and telecom ciphertexts for all of their clients' contacts.
+With these precomputed databases, the telecoms could then use oblivious transfer to blindly serve the agencies' requests for information about their clients.

### 2015-11-24 paper/intro.tex
Revised paper, including budget mechanism.

\section{Introduction To Contact Chaining}

Contact chaining is a form of government surveillance. The goal of contact chaining is to use information about social connections between identities, such as records of phone calls between one number and another, to identify members of a criminal organization or terrorist group. Starting with one or more suspects whose identities are known, the government aims to consider contacts of those suspects. These can be \emph{direct contacts}, such as two people who spoke on the phone, or \emph{extended contacts}, such as two people connected by a chain of two or more phone calls. If Alice calls Bob, and Bob calls Charlie, then Alice and Bob are direct contacts (as are Bob and Charlie), but Alice and Charlie are extended contacts. We may also say that Alice and Charlie are at a distance of 2 in the social graph (since the shortest number of phone calls that connect Alice to Charlie is 2).

Without mechanisms to preserve privacy, a contact chaining search can collect a surprising large group of users' information. And, unless criminals or terrorists only contact other members of their organizations, most of them are unlikely to be the intended targets of the investigation. This is a large and unnecessary intrusion of privacy. These untargeted users may nevertheless face unwarranted government scrutiny, intrusive investigation, or a risk that their sensitive phone histories may be leaked accidentally.

We propose to replace a contact chaining search in which a single government agency collects user data in the clear from the telecoms who own it with a \emph{privacy-preserving contact chaining protocol}. This protocol involves multiple government agencies, each of whom must actively agree to each step of the search, or the search ends. Instead of revealing to the agencies a large, plaintext list of phone numbers and their connections to each other, it gives the agencies only an encrypted list of phone numbers. The numbers in this list are encrypted using the public keys of all three agencies in a randomized, public-key, commutative cryptosystem (such as ElGamal). This output can then be compared with other encrypted lists, such as encrypted cell tower dumps, watch lists, or the output from another run of this protocol. By using the protocol described in~\cite{bandits}, the phone numbers that appear in multiple lists can be decrypted jointly by the agencies, while other phone numbers remain encrypted and unreadable as long as the government agencies do not all collude.

In section \ref{sec:proto} we discuss the participants, inputs, outputs, and assumptions of our privacy-preserving contact chaining protocol, and present two versions of the protocol itself in sections \ref{sec:proto1} and \ref{sec:proto2}. In section \ref{sec:discuss} we discuss the privacy of our protocol.

### 2015-11-24 paper/protocol.tex
Revised paper, including budget mechanism.

@@
 \section{Protocols For Privacy-Preserving Contact Chaining}
+\label{sec:proto}
 
-This is a candidate protocol for privacy-preserving contact chaining. The desired inputs, outputs, and security assumptions are given below.
+This is a candidate protocol for privacy-preserving contact chaining.
+We discuss the desired inputs, outputs, and security assumptions below, and then present two versions of the protocol in sections \ref{sec:proto1} and \ref{sec:proto2}.
 
@@
 Each telecom knows only a subset of the edges $E$.
-In this graph, the vertices in $V$ are labeled with the phone numbers they represent.
-$E$ contains an edge between $a$ and $b$ if and only if phone number $a$ has dialed phone number $b$ or vice versa within some window of time.
+$V$ contains vertices labeled with the phone numbers they represent, and $E$ contains an edge between $a$ and $b$ if and only if phone number $a$ has dialed phone number $b$ or vice versa within some window of time.
 The set of existing phone numbers $V$ is public information.
@@
 In addition to the public knowledge about $V$ and which telecom serves which phone number, the agencies must each hold a copy of a \emph{warrant} in order to perform this protocol.
-A warrant must include at least the information $(x, k)$, where $x$ is a target phone number and $k$ is a (small) distance from $x$.
+A warrant is a triplet ($x$, $k$, $\mx$).
+$x$ is a target phone number.
+$k$ is a (small) distance from $x$, the distance at which the agencies wish to consider chained contacts.
 For example, if $k=2$, then the agencies only wish to consider users at most 2 phone calls away from their person (or phone number) of interest $x$.
@@
 Now everyone else who has recently called that pizza place is at a distance 2 to $x$.
-
-The warrant must therefore also specify additional mechanisms for limiting the scope of the investigation.
-We specifically require two additional values to be part of the warrant.
-The first is a branching limit $l$.
-If a vertex has degree greater than $l$, the agencies will not consider paths through that vertex in determining whether there is a path of length at most $k$ between two vertices.
-This mechanism prevents very busy phone numbers, such as that of the pizza restaurant or a taxi service, from introducing very many unrelated phone numbers into the eventual data set.
-The second is $m$, a maximum number of encrypted users that the agencies are willing to consider in total.
-Once the agencies have added $m$ encrypted phone numbers to their output, they halt their investigation.
-This sets an absolute upper limit on the number of users whose data can be captured by contact chaining.
+Therefore, the warrant also includes $\mx$, a maximum number of users whose information the protocol can capture.
+We will use a a ``budget'' mechanism based on the capacity assignment mechanism of~\cite{tmls09}.
+We treat $\mx$ as a \emph{budget} of users to be searched.
+This budget will, at each step in the protocol, be subdivided among the neighbors of the vertex being considered - initially $x$, then $x$'s neighbors, etc.
+We specify the protocol in full in sections~\ref{sec:proto1} and \ref{sec:proto2}.
 
@@
 
-We treat all parties to this protocol as honest-but-curious.
+We make a few assumptions about existing cryptographic infrastructure.
 All telecoms and agencies must have a published public encryption key and private decryption key.
@@
 The investigating agency itself communicates with one or more other agencies, which we call ``oversight agencies''.
-Oversight agencies are responsible for approving warrants, collecting statistics and other information about how often the protocol is run, and enforcing the protocol's scope limiting mechanisms.
+Oversight agencies are responsible for approving warrants, collecting statistics and other information about how often the agencies perform a contact-chaining search, and enforcing the protocol's scope limiting mechanisms.
 
@@
 Every phone number in this set must be encrypted with each of the agencies' public keys.
-The encrypted set may exclude a phone number if the only paths of length at most $k$ connecting it to $x$ go through vertices with degree greater than the limit $l$, but then (encryptions of) all such high-degree vertices must also noted in the output.
+The encrypted set may exclude some numbers if the upper bound $\mx$ is less than the total size of the neighborhood of radius $k$ around $x$.
 The agencies should all have the same output.
 
-The telecoms do not expect any output from this protocol.
+The telecoms should not learn the agency's output.
+Instead, each telecom's output should contain only a list of which of the phone numbers it serves were sent to the government agencies.
+This allows the telecoms to play an accountability role in this protocol.
+The government may have an interest in keeping the telecoms from knowing which of their clients were surveilled; we discuss this in section~\ref{sec:oblivious}.
 
@@
 In particular, the encrypted set of phone numbers can be used as an input into a privacy-preserving set intersection protocol, as in~\cite{bandits}.
+
+In particular, we assume that all telecoms honestly follow the protocol and submit accurate information about the phone numbers they serve and the records they keep.
+We assume they send no telecom ciphertexts or agency ciphertexts to the agencies except when called for in the protocol.
+In practice, simple investigative tools commonly in use by the police allow law enforcement agencies to gather information about the phone call history of a suspect with a valid warrant, but such information cannot generally be used for contact chaining purposes.
 
@@
 
-The agencies collectively learn \emph{no} information about the edge set $E$ except what is implied by the output.
-Furthermore, as long as at least one agency does not collude with the others, the remaining agencies must not be able to learn any of the phone numbers that appear in encrypted form in the output, unless it is implied by the size of the encrypted output and the leaked service information.
+As long as all parties honestly follow the protocol, the agencies collectively learn \emph{no} information about the edge set $E$ except what is implied by the output.
+Furthermore, as long as at least one agency follows the protocol honestly and does not collude with the others, the remaining agencies cannot learn any of the phone numbers that appear in encrypted form in the output (unless implied by the size of the encrypted output and the leaked service information), nor can the colluding agencies cause a phone number not within distance $k$ of target $x$ to appear in the output, even in encrypted form.
+Telecoms have the ability to send additional information about their users to agencies or other telecoms at any time, but we assume they will not wish to do so, since they have a business interest to protect user information and comply with the law.
+We assume that all telecoms follow the protocol honestly.
 
@@
 However, all messages the agencies receive from the telecoms will be encrypted.
-The only information that is leaked in the clear to the agencies is \emph{ownership information} about the encrypted phone numbers - specifically, which telecoms own the vertices in the encrypted output.
+The only other information the agencies learn the size of the output and \emph{ownership information} about the encrypted phone numbers - specifically, which telecoms own the vertices in the encrypted output.
 
@@
 To manage the breadth-first search, the agencies (or at least the investigating agency) will maintain a queue $\mathbf{Q}$, containing vertices yet to explore.
-$\mathbf{Q}$ contains triples for unexplored vertices $a$ of the form $(\Enc_{T(a)}(a), T(a), j)$.
-These tuples contain the telecom ciphertext for $a$, a record of which telecom owns $a$, and an integer $j$ indicating the distance to $a$ from the target vertex.
+$\mathbf{Q}$ contains tuples for unexplored vertices $a$ of the form $(\Enc_{T(a)}(a), T(a), j, U)$.
+These tuples contain the telecom ciphertext for $a$, a record of which telecom owns $a$, an integer $j$ indicating the remaining distance out to which neighbors can be chained from $a$, and another integer $U$ indicating the remaining budget of users.
 
-The agencies will represent their output in the form of two lists: $\mathbf{C}$, containing agency ciphertexts collected as a result of the contact chaining, and $\mathbf{H}$, containing high-degree vertices through which the agencies decided not to chain, along with their distances from the target.
-The agencies may, after the protocol, decide to decrypt the phone numbers in $\mathbf{H}$, and may then continue chaining through them by running the contact-chaining protocol starting with one of those phone numbers.
+At the beginning of the protocol, the agencies assign the entire budget $U=\mx$ to the target vertex $x$.
+When the agencies explore $x$ and add its neighbors to $Q$, they decrease the budget by 1 and then subdivide it equally among each of $x$'s neighbors.
+Each neighbor $a$ receives a new budget $U=(\mx-1)/\de(x)$.
+The process continues thus.
+As the agencies explore each new vertex, they share its remaining budget among each of its unexplored neighbors.
+If a vertex's remaining budget is less than the number of neighbors it has, the agencies do not add its neighbors $\mathbf{Q}$ (but keep that vertex itself in their output).
+
+The agencies will represent their output in the form of a list $\mathbf{C}$, containing agency ciphertexts.
+Each telecom $T$ will represent its output in the form of a list $\mathbf{L}_T$, listing plaintext users served by that telecom whose information the agencies requested.
 
@@
 \bce
-\item The agencies start by agreeing upon a warrant $(x, k, l)$, where $x$ is the target phone number, $k$ is a maximum distance, and $l$ is an upper limit on the degree of vertices to chain through.
+\item The agencies start by agreeing upon a warrant $(x, k, \mx)$, where $x$ is the target phone number, $k$ is a maximum distance, and $\mx$ is an upper limit on the number of users whose information they may collect.
 They encrypt $x$ under the public key of $T(x)$.
-\item The agencies initialize a queue $\mathbf{Q}$. Initially, $\mathbf{Q}$ contains only the triple $(\Enc_{T(x)}(x), T(x), 0)$.
-\item The agencies initialize the output lists $\mathbf{C}$ and $\mathbf{H}$ to be empty.
+\item The agencies initialize a queue $\mathbf{Q}$. Initially, $\mathbf{Q}$ contains only the triple $(\Enc_{T(x)}(x), T(x), k, \mx)$.
+\item The agencies initialize the output list $\mathbf{C}$ to be empty.
+\item Each telecom $T$ initializes its output list $\mathbf{L}_T$ to be empty.
 \item While $\mathbf{Q}$ is not empty, do the following:
 \bce
-\item \label{proto1:top-of-loop} The agencies dequeue $(\Enc_{T(a)}(a), T(a), j)$ from $\mathbf{Q}$. They send the telecom ciphertext $\Enc_{T(a)}(a)$ to $T(a)$.
-\item $a$'s provider, $T(a)$, decrypts $a$ from its telecom ciphertext.
+\item \label{proto1:top-of-loop} The agencies dequeue $(\Enc_{T(a)}(a), T(a), j, U)$ from $\mathbf{Q}$. They send the pair ($\Enc_{T(a)}(a), j)$ to $T(a)$.
+\item $a$'s provider, $T(a)$, decrypts $a$ from its telecom ciphertext. It adds $a$ to $\mathbf{L}_T$.
 \item \label{proto1:first-send} $T(a)$ encrypts $a$ under the agencies' public keys, and sends $\Enc_\mathcal{A}(a)$ to the agencies.
-\item The agencies add $\Enc_\mathcal{A}(a)$ to $\mathbf{C}$. If $j=k$, they send the message ``DONE'' to $T(a)$, and go to step~\ref{proto1:top-of-loop}.
-\item Otherwise, the agencies send the message ``CONTINUE'' to $T(a)$.
-\item Upon receiving the message ``CONTINUE'', $T(a)$ encrypts each neighbor $b$ of $a$ under the public key of $T(b)$, creating a telecom ciphertext for $b$.
-\item \label{proto1:second-send} $T(a)$ sends all telecom ciphertexts for $a$'s neighbors to the agencies, in the form of pairs $(\Enc_{T(b)}(b), T(b))$.
-\item If the agencies receive more than $l$ ciphertexts in the previous step (and $j\neq 0$), they add $(\Enc_\mathcal{A}(a), j)$ to $\mathbf{H}$.
-They discard the telecom ciphertexts (i.e., agencies refuse to sign the ciphertexts or send them on to the telecoms).
-\item Otherwise, for each telecom ciphertext received, the agencies add the tuple $(\Enc_{T(b)}(b), T(b), j+1)$ to $\mathbf{Q}$.
+\item If $j=0$, $T(a)$ is done. Go to step \ref{proto1:receive}.
+\item Otherwise, $T(a)$ encrypts each neighbor $b$ of $a$ under the public key of $T(b)$, creating a telecom ciphertext for $b$. $T(a)$ excludes $b$ if it already appears in $\mathbf{L}_T$.
+\item \label{proto1:second-send} $T(a)$ sends the number of ciphertexts generated this way, $\de(a)$, as well as all telecom ciphertexts generated in the previous step, to the agencies.
+$T(a)$ sends the ciphertexts in the form of pairs $(\Enc_{T(b)}(b), T(b))$.
+\item \label{proto1:receive} The agencies add $\Enc_\mathcal{A}(a)$ to $\mathbf{C}$.
+\item If $\de(a)\geq U$, the agencies discard all telecom ciphertexts received for $a$'s neighbors (i.e., oversight agencies refuse to sign the ciphertexts, and the investigating agency does not send them on to the telecoms).
+\item Otherwise, the agencies choose $(U-1)/\de(a)$ as the remaining budget for each new vertex to explore, subtracting 1 to account for $a$ itself and dividing the remaining budget equally.
+For each telecom ciphertext received, the agencies add the tuple $(\Enc_{T(b)}(b), T(b), j-1, (U-1)/\de(a))$ to $\mathbf{Q}$.
 \ece
-\item The agencies' final outputs are the lists $\mathbf{C}$ and $\mathbf{H}$.
+\item The agencies' final output is the list $\mathbf{C}$. Each telecom $T$'s final output is $\mathbf{L}_T$.
 \ece
@@
 Now we can present the following modified protocol.
-This protocol uses the same data structures as in section~\ref{sec:proto1}, except that $\mathbf{Q}$ now contains pairs $(\Enc_{T(a)}(a), j)$ for unexplored vertices $a$.
+This protocol uses the same data structures as in section~\ref{sec:proto1}, except that $\mathbf{Q}$ now contains triples $(\Enc_{T(a)}(a), j, U)$ for unexplored vertices $a$ (omitting the identity of $T(a)$.
 
 \bce
-\item The agencies start by agreeing upon a warrant $(x, k, l)$, where $x$ is the target phone number, $k$ is a maximum distance, and $l$ is an upper limit on the degree of vertices to chain through.
+\item The agencies start by agreeing upon a warrant $(x, k, \mx)$, where $x$ is the target phone number, $k$ is a maximum distance, and $\mx$ is an upper limit on the number of users whose information they may collect.
 They encrypt $x$ under the public key of $T(x)$.
-\item The agencies initialize a queue $\mathbf{Q}$. Initially, $\mathbf{Q}$ contains only the pair $(\Enc_{T(x)}(x), 0)$.
-\item The agencies initialize the output lists $\mathbf{C}$ and $\mathbf{H}$ to be empty.
+\item The agencies initialize a queue $\mathbf{Q}$. Initially, $\mathbf{Q}$ contains only the triple $(\Enc_{T(x)}(x), T(x), 0, \mx)$.
+\item The agencies initialize the output list $\mathbf{C}$ to be empty.
+\item Each telecom $T$ initializes its output lists $\mathbf{L}_T$ to be empty.
 \item While $\mathbf{Q}$ is not empty, do the following:
 \bce
-\item \label{proto2:dequeue} The agencies dequeue a number of pairs $(\Enc_{T(a)}(a), j)$ from $\mathbf{Q}$.
-They send each telecom ciphertext $\Enc_{T(a)}(a)$ to all telecoms, along with the message ``CONTINUE'' if $j<k$, or the message ``DONE'' if not.
-\item All telecoms attempt to decrypt the telecom ciphertexts. For each vertex $a$, $a$'s provider, $T(a)$, will decrypt $a$. 
-\item $T(a)$ encrypts $a$ under the agencies' public keys to produce the agency ciphertext $\Enc_\mathcal{A}(a)$.
-\item If $T(a)$ got the message ``CONTINUE'' along with the ciphertext, it also encrypts each neighbor $b$ of $a$ under the public key of $T(b)$, creating a telecom ciphertext for $b$.
-\item All parties to this protocol engage in an anonymity protocol.
-Each telecom's message in the protocol is the set of all agency ciphertexts and all telecom ciphertexts produced in the previous two steps.
-If the telecom did not produce any messages in the previous two steps, it participates in the protocol but sends no message.
-\item When the anonymity protocol is complete, the agencies receive all the ciphertexts.
-\item For each agency ciphertext $\Enc_\mathcal{A}(a)$ the agencies receive, they add that ciphertext to $\mathbf{C}$.
-\item If the agencies receive more than $l$ telecom ciphertexts for any vertex $a$ in the previous step (and $j\neq 0$), they add $(\Enc_\mathcal{A}(a), j)$ to $\mathbf{H}$.
-They discard the associated telecom ciphertexts (i.e., agencies refuse to sign the ciphertexts or send them on to the telecoms).
-\item Otherwise, for each telecom ciphertext received, the agencies add the pair $(\Enc_{T(b)}(b), j+1)$ to $\mathbf{Q}$.
+\item \label{proto2:dequeue} The agencies dequeue a triple $(\Enc_{T(a)}(a), j, U)$ from $\mathbf{Q}$. They send the pair $(\Enc_{T(a)}(a), j)$ to all telecoms.
+\item All telecoms attempt to decrypt $\Enc_T(a)(a)$. Only $T(a)$ will be able to do so.
+\item $T(a)$ adds $a$ to $\mathbf{L}_T$.
+\item \label{proto2:agencycipher} $T(a)$ encrypts $a$ under the agencies' public keys, producing the agency ciphertext $\Enc_\mathcal{A}(a)$.
+\item \label{proto2:telecomcipher} If $j>0$, $T(a)$ encrypts each neighbor $b$ of $a$ under the public key of $T(b)$, creating a telecom ciphertext for $b$.
+$T(a)$ excludes $b$ if it already appears in $\mathbf{L}_T$.
+\item \label{proto2:anon} All parties to this protocol engage in the anonymity protocol.
+$T(a)$ sends an anonymous message consisting of the agency ciphertext it generated in step~\ref{proto2:agencycipher}; the set of telecom ciphertexts generated in step \ref{proto2:telecomcipher}, and $\de(a)$, the number of telecom ciphertexts being sent.
+The agencies and all telecoms that could not decrypt $\Enc_{T(a)}(A)$ participate but send no anonymous message.
+\item When the anonymity protocol is complete, the agencies receive all the ciphertexts. They add $\Enc_\mathcal{A}(a)$ to $\mathbf{C}$.
+\item If $\de(a)\geq U$, the agencies discard all telecom ciphertexts received for $a$'s neighbors (i.e., oversight agencies refuse to sign the ciphertexts, and the investigating agency does not send them on to the telecoms).
+\item Otherwise, the agencies choose $(U-1)/\de(a)$ as the remaining budget for each new vertex to explore, subtracting 1 to account for $a$ itself and dividing the remaining budget equally.
+For each telecom ciphertext received, the agencies add the tuple $(\Enc_{T(b)}(b), T(b), j-1, (U-1)/\de(a))$ to $\mathbf{Q}$.
 \ece
-\item The agencies' final outputs are the lists $\mathbf{C}$ and $\mathbf{H}$.
+\item The agencies' final output is the list $\mathbf{C}$. Each telecom $T$'s final output is $\mathbf{L}_T$.
 \ece
@@
 The protocol replaces each query in the protocol of section~\ref{sec:proto1} with broadcast of the telecom ciphertext to all telecoms, and replaces each response with a round of the anonymity protocol.
-The agencies can in theory dequeue the entire queue in step~\ref{proto2:dequeue}, but they may choose to limit the number of queries made at once for practical purposes.
+This allows the telecom that owns each phone number to respond with appropriate information about the phone number, but shields the telecom's identity from the agencies (and incidentally from other telecoms).
+
+It should be noted that the agencies and telecoms need not handle one ciphertext at a time.
+In fact, the agencies can in principle dequeue all of $\mathbf{Q}$ in step \ref{proto2:dequeue} and broadcast all pending vertices to the telecoms.
+In step \ref{proto2:anon}, multiple telecoms can submit multiple messages to a single run of the anonymity protocol, with only those telecoms which were unable to decrypt any vertices submitting no message.
+The exact number of messages per instance of the anonymity protocol can be tuned for best efficiency.

### 2015-11-24 src/cc/BigIntegerEncoding.java
Started adding code
Including a version of DataGen that makes a directed graph

@@ -1,0 +1,45 @@
+package cc;
+
+import java.io.UnsupportedEncodingException;
+import java.math.BigInteger;
+
+public class BigIntegerEncoding {
+	/**
+	 * Returns a BigInteger representing string str. If str is longer than
+	 * 127 chars or contains non-ASCII, returns null.
+	 * @param str A string
+	 * @return A BigInteger representing the str
+	 */
+	public static BigInteger encode(String str) {
+		BigInteger out;
+		try {
+			byte[] bytes = str.getBytes("US-ASCII");
+			out = new BigInteger(bytes);
+		} catch (UnsupportedEncodingException e) {
+			e.printStackTrace();
+			return null;
+		}
+		if (out.compareTo(ElGamal.prime1024) > 0) {
+			System.err.println("String too long error: " + str);
+			return null;
+		}
+		return out;
+	}
+
+	/**
+	 * Returns a String that the given integer represents.
+	 * @param bi A BigInteger representing a string
+	 * @return the string
+	 */
+	public static String decode(BigInteger bi) {
+		String out;
+		try {
+			byte[] bytes = bi.toByteArray();
+			out = new String(bytes, "US-ASCII");
+		} catch (UnsupportedEncodingException e) {
+			e.printStackTrace();
+			return null;
+		}
+		return out;
+	}
+}

### 2015-11-24 src/cc/CommutativeElGamal.java

@@ -1,0 +1,221 @@
+package cc;
+
+import java.math.BigInteger;
+
+public class CommutativeElGamal extends ElGamal {
+
+	private static final int MAX_ID = 10000; 
+	
+	private int id;
+
+	/**
+	 * Generates a new CommutativeElGamal object with preset group and generator,
+	 * and randomly generated keys and id.
+	 */
+	public CommutativeElGamal() {
+		super();
+		id = getRNG().nextInt(MAX_ID);
+	}
+
+	/**
+	 * Generates a new ElGamal object with selected group and generator, randomly generated keys,
+	 * and random id.
+	 * @param p A prime number.
+	 * @param g A generator of the group Zp*.
+	 */
+	public CommutativeElGamal(BigInteger p, BigInteger g) {
+		super(p, g);
+		id = getRNG().nextInt(MAX_ID);
+	}
+
+	/**
+	 * Generates a new ElGamal object with selected group, generator, private key, and random id.
+	 * @param p A prime number.
+	 * @param g A generator of the group Zp*.
+	 * @param privateKey A number < p/2.
+	 */
+	public CommutativeElGamal(BigInteger p, BigInteger g, BigInteger privateKey) {
+		super(p, g, privateKey);
+		id = getRNG().nextInt(MAX_ID);
+	}
+
+	/**
+	 * Generates a new ElGamal object with preset group and generator, selected 
+	 * private key, and random id.
+	 * @param id The id for this keypair.
+	 * @param privateKey A number < p/2.
+	 */
+	public CommutativeElGamal(BigInteger privateKey) {
+		super(privateKey);
+		id = getRNG().nextInt(MAX_ID);
+	}
+
+	/**
+	 * Generates a new CommutativeElGamal object with preset group and generator,
+	 * randomly generated keys, and selected id.
+	 * @param id The id for this keypair.
+	 */
+	public CommutativeElGamal(int id) {
+		super();
+		this.id = id;
+	}
+
+	/**
+	 * Generates a new ElGamal object with selected group and generator, randomly generated keys,
+	 * and selected id.
+	 * @param id The id for this keypair.
+	 * @param p A prime number.
+	 * @param g A generator of the group Zp*.
+	 */
+	public CommutativeElGamal(int id, BigInteger p, BigInteger g) {
+		super(p, g);
+		this.id = id;
+	}
+
+	/**
[…]

### 2015-11-24 src/cc/DataGen.java

@@ -1,0 +1,101 @@
+package cc;
+
+import java.io.IOException;
+import java.io.FileOutputStream;
+import java.io.ObjectOutputStream;
+import java.util.ArrayList;
+import java.util.HashMap;
+import java.util.HashSet;
+import java.util.Random;
+
+
+/**
+ * We are going to use 0-indexed integer ids for users and for telecoms.
+ * If nTelcoms is the number of telecoms, then the user with id X
+ *   belongs to telecom (X % nTelcoms).
+ * We are assuming that each user/node has a totally random set of contacts.
+ * The degree of each node is distributed as follows:
+ *   A node has a 99% chance to be "small", and a 1% chance to be "large".
+ *   "Small" nodes have 3-200 contacts (chosen uniformly).
+ *   "Large" nodes have 3-5000 contacts (chosen uniformly).
+ * The large type represent businesses.
+ */
+
+public class DataGen {
+	public static double LARGE_CHANCE = 0.01;
+	public static int SMALL_MIN = 3;
+	public static int SMALL_MAX = 200;
+	public static int LARGE_MIN = 3;
+	public static int LARGE_MAX = 5000;
+
+	public static void usage() {
+		System.err.println("Usage: java cc.DataGen filename numTelecoms numUsers");
+	}
+
+	// Method to return which telecom owns which user id. May be changed later.
+	public static int provider(int userId, int numTelecoms) {
+		return userId % numTelecoms;
+	}
+
+	public static void main(String[] args) {
+		if (args.length < 3) {
+			usage();
+			return;
+		}
+		int nTelecoms = Integer.parseInt(args[1]);
+		int nUsers = Integer.parseInt(args[2]);
+		if (LARGE_MAX >= nUsers) {
+			System.err.println("Please allow for more than " + LARGE_MAX + " users.");
+			return;
+		}
+
+		Random rand = new Random();
+
+		ArrayList<HashMap<Integer, HashSet<Integer>>> graph =
+				new ArrayList<HashMap<Integer, HashSet<Integer>>>();
+		for (int i = 0; i < nTelecoms; i++) {
+			graph.add(new HashMap<Integer, HashSet<Integer>>());
+		}
+
+		// For each user, generate a set of contacts and store it.
+		for (int currId = 0; currId < nUsers; currId++) {
+			HashSet<Integer> userData = new HashSet<Integer>();
[…]

### 2015-11-24 src/cc/ElGamal.java

@@ -1,0 +1,133 @@
+package cc;
+
+import java.security.SecureRandom;
+import java.util.Random;
+import java.math.BigInteger;
+
+public class ElGamal {
+
+	private Random rng;
+	private BigInteger p; // prime number
+	private BigInteger g; // generator
+	private BigInteger privateKey;
+	private BigInteger publicKey;
+
+	public static final BigInteger prime1024 = new BigInteger("FFFFFFFFFFFFFFFFC90FDAA22168C234C4C6628B80D"
+			+ "C1CD129024E088A67CC74020BBEA63B139B22514A08798E3404DDEF9519B3CD3A431B302B0A6DF25F14374FE135"
+			+ "6D6D51C245E485B576625E7EC6F44C42E9A637ED6B0BFF5CB6F406B7EDEE386BFB5A899FA5AE9F24117C4B1FE64"
+			+ "9286651ECE65381FFFFFFFFFFFFFFFF", 16);
+	public static final BigInteger generator1024 = new BigInteger("2");
+	
+	public static final BigInteger prime768 = new BigInteger("FFFFFFFFFFFFFFFFC90FDAA22168C234C4C6628B80DC"
+			+ "1CD129024E088A67CC74020BBEA63B139B22514A08798E3404DDEF9519B3CD3A431B302B0A"
+			+ "6DF25F14374FE1356D6D51C245E485B576625E7EC6F44C42E9A63A3620FFFFFFFFFFFFFFFF",16);
+	public static final BigInteger generator768 = new BigInteger("2");
+
+	/**
+	 * Generates a new ElGamal object with preset group and generator, and randomly generated keys.
+	 */
+	public ElGamal() {
+		rng = new SecureRandom();
+		p = prime1024;
+		g = generator1024;
+		privateKey = new BigInteger(p.bitLength() - 1, rng);
+		publicKey = g.modPow(privateKey, p);
+	}
+
+	/**
+	 * Generates a new ElGamal object with selected group and generator, and randomly generated keys.
+	 * @param p A prime number.
+	 * @param g A generator of the group Zp*.
+	 */
+	public ElGamal(BigInteger p, BigInteger g) {
+		rng = new SecureRandom();
+		this.p = p;
+		this.g = g;
+		privateKey = new BigInteger(p.bitLength() - 1, rng);
+		publicKey = g.modPow(privateKey, p);
+	}
+
+	/**
+	 * Generates a new ElGamal object with selected group, generator, and private key.
+	 * @param p A prime number.
[…]

### 2015-11-24 src/cc/ElGamalTester.java

@@ -1,0 +1,87 @@
+package cc;
+
+import java.math.BigInteger;
+import java.util.Random;
+import java.util.Arrays;
+
+public class ElGamalTester {
+	
+	private static void ShuffleArray(Object[] array)
+	{
+	    Object temp;
+	    int index;
+	    Random random = new Random();
+	    for (int i = array.length - 1; i > 0; i--)
+	    {
+	        index = random.nextInt(i + 1);
+	        temp = array[index];
+	        array[index] = array[i];
+	        array[i] = temp;
+	    }
+	}
+
+	public static void main(String[] args) {
+		int x = 3;
+		Random rand = new Random();
+		CommutativeElGamal[] elgs = new CommutativeElGamal[x];
+		PohligHellman[] phs = new PohligHellman[x];
+		for (int i = 0; i < elgs.length; i++) {
+			phs[i] = new PohligHellman();
+			elgs[i] = new CommutativeElGamal(x-i);
+		}
+		
+		final BigInteger[] datum = {new BigInteger(60, rand)};
+		System.out.println("A : " + datum[0].toString());
+		BigInteger[][] encrypted = new BigInteger[elgs.length][];
+		BigInteger[][] partcrypted = new BigInteger[elgs.length][];
+		BigInteger[][] decrypted = new BigInteger[elgs.length][];
+		encrypted[0] = elgs[0].encrypt(datum);
+		System.out.println("B0:" + Arrays.toString(encrypted[0]));
+		for (int i = 1; i < elgs.length; i++) {
+			encrypted[i] = elgs[i].encrypt(encrypted[i-1]);
+			System.out.println("B" + i + ":" + Arrays.toString(encrypted[i]));
+		}
+		
+		ShuffleArray(elgs);
+		
+		partcrypted[0] = elgs[0].partialDecrypt(encrypted[elgs.length-1]);
+		for (int j = 1; j < partcrypted[0].length; j += 2) {
+			partcrypted[0][j] = phs[0].encrypt(partcrypted[0][j]);
+		}
+		partcrypted[0][partcrypted[0].length - 1] = phs[0].encrypt(partcrypted[0][partcrypted[0].length - 1]); 
+		System.out.println("C0:" + Arrays.toString(partcrypted[0]));
+		for (int i = 1; i < elgs.length; i++) {
+			partcrypted[i] = elgs[i].partialDecrypt(partcrypted[i-1]);
[…]

### 2015-11-24 src/cc/PohligHellman.java

@@ -1,0 +1,105 @@
+package cc;
+
+import java.security.SecureRandom;
+import java.util.Random;
+import java.math.BigInteger;
+
+public class PohligHellman {
+
+	protected Random rng;
+	private BigInteger p; // prime number
+	private BigInteger encryptionKey;
+	private BigInteger decryptionKey;
+	
+	public static BigInteger presetPrime = ElGamal.prime1024;
+	
+
+	/**
+	 * Generates a new PohligHellman object with preset group and randomly generated keys.
+	 */
+	public PohligHellman() {
+		rng = new SecureRandom();
+		p = presetPrime;
+		generateKeys();
+	}
+
+	/**
+	 * Generates a new PohligHellman object with selected group.
+	 * @param p A prime number.
+	 */
+	public PohligHellman(BigInteger p) {
+		rng = new SecureRandom();
+		this.p = p;
+		generateKeys();
+	}
+
+	/**
+	 * Generates a new PohligHellman object with the default group, and selected keys.
+	 * Note that no check is done to ensure that the keys are valid.
+	 * @param encryptionKey The encryption key.
+	 * @param decryptionKey The decryption key. Must have encryptionKey * decryptionKey = 1 mod p-1.
+	 */
+	public PohligHellman(BigInteger encryptionKey, BigInteger decryptionKey) {
+		rng = new SecureRandom();
+		p = presetPrime;
+		this.encryptionKey = encryptionKey;
+		this.decryptionKey = decryptionKey;
+	}
+
+	/**
+	 * Generates a new PohligHellman object with selected group and selected keys.
+	 * Note that no check is done to ensure that the keys are valid.
+	 * @param p A prime number.
+	 * @param encryptionKey The encryption key.
+	 * @param decryptionKey The decryption key. Must have encryptionKey * decryptionKey = 1 mod p-1.
+	 */
+	public PohligHellman(BigInteger p, BigInteger encryptionKey, BigInteger decryptionKey) {
+		rng = new SecureRandom();
+		this.p = p;
+		this.encryptionKey = encryptionKey;
+		this.decryptionKey = decryptionKey;
+	}
+
+	private void generateKeys() {
+		encryptionKey = new BigInteger(p.bitLength()-1, rng);
+		while (!encryptionKey.gcd(p.subtract(BigInteger.ONE)).equals(BigInteger.ONE)) {
[…]

### 2015-11-24 src/cc/Telecom.java

@@ -1,0 +1,8 @@
+package cc;
+
+import java.net.ServerSocket;
+
+public class Telecom {
+	private ServerSocket serverSocket;
+
+}

### 2016-02-27 src/nocrypto/OversightAgency.java
Fix nocrypto bug where OversightAgency would quit too soon

@@ -4,6 +4,7 @@ import java.io.IOException;
 import java.io.ObjectInputStream;
 import java.io.ObjectOutputStream;
 import java.net.Socket;
+import java.net.SocketException;
 import java.net.UnknownHostException;
 import java.util.HashMap;
 
@@ -163,6 +164,16 @@ public class OversightAgency extends Agency {
 		} catch (ClassNotFoundException e) {
 			e.printStackTrace();
 			return;
+		}
+		// Attempt to read FIN, but if connection breaks first then just ignore it.
+		try {
+			leaderIStream.readObject();
+		} catch (SocketException e) {
+			// This is expected; do nothing.
+		} catch (IOException e) {
+			e.printStackTrace();
+		} catch (ClassNotFoundException e) {
+			e.printStackTrace();
 		}
 	}
 

### 2016-02-27 src/nocrypto/OversightFinalResultsThread.java

@@ -28,6 +28,7 @@ public class OversightFinalResultsThread extends cc.CPUTrackingThread {
 			// If the everything has gone perfect, the oversight agency should send
 			// us a True.
 			oversightCpuTime = oSocket.readLong();
+			oSocket.writeObject(true); // FIN
 		} catch (IOException e) {
 			e.printStackTrace();
 			oSocket.close();

### 2016-02-27 oversightNC.sh
Added extra test cases to nocrypto scripts

@@ -1,6 +1,6 @@
 #!/bin/sh
 cd bin
-for i in 10 20 100 200 1000 2000 10000 20000
+for i in 10 20 100 200 1000 2000 10000 20000 100000 200000
 do
 for l in 2 3
 do

### 2016-02-27 src/cc/Keys.java
Baking in assumptions about telecom/agency IDs to reduce bandwidth usage.

@@ -267,7 +267,7 @@ public abstract class Keys {
 	 */
 	public boolean verify(int signerId, SignedTelecomCiphertext signedTC) {
 		Signature verifier = verifiers.get(signerId);
-		byte[] signature = signedTC.getSignatures().get(signerId);
+		byte[] signature = signedTC.getSignature(signerId);
 		if (signature == null) {
 			return false;
 		}

### 2016-02-27 src/cc/LeaderAgency.java

@@ -106,7 +106,8 @@ public class LeaderAgency extends Agency {
 
 		// Search on the first telecom ciphertext. It is different from the others
 		// because it does not have a telecom signature.
-		SignedTelecomCiphertext firstSignedTC =	new SignedTelecomCiphertext(startTCT);
+		SignedTelecomCiphertext firstSignedTC =
+				new SignedTelecomCiphertext(startTCT, numAgencies);
 		firstSignedTC.addSignature(id, keys.sign(firstSignedTC.getCiphertexts()));
 		OversightFirstThread[] firstThreads = new OversightFirstThread[oversight.length];
 		for (int i = 0; i < firstThreads.length; i++) {
@@ -129,13 +130,13 @@ public class LeaderAgency extends Agency {
 		// general loop because we will not care about the degree of this first
 		// vertex.
 		connectTelecom(initialOwner);
-		HashMap<Integer, SignedTelecomResponse> prevResponses =
-				new HashMap<Integer, SignedTelecomResponse>();
+		SignedTelecomResponse[] prevResponses =
+				new SignedTelecomResponse[numTelecoms];
 		try {
 			writeObjectToTelecom(initialOwner, firstSignedTC);
 			SignedTelecomResponse firstSignedResponse =
 					(SignedTelecomResponse) readObjectFromTelecom(initialOwner);
-			prevResponses.put(initialOwner, firstSignedResponse);
+			prevResponses[initialOwner] = firstSignedResponse;
 			recordTelecomCpuTime(firstSignedResponse.getCpuTime());
 			TelecomResponse telecomResponse = firstSignedResponse.getTelecomResponses()[0];
 			if (telecomResponse.getMsgType() ==	TelecomResponse.MsgType.DATA) {
@@ -168,7 +169,8 @@ public class LeaderAgency extends Agency {
 			nextSignedTCs = new HashMap<Integer, SignedTelecomCiphertext>();
 			for (int telecomId : investigationLists.keySet()) {
 				TelecomCiphertext[] ciphertexts = getCiphertexts(telecomId);
-				nextSignedTCs.put(telecomId, new SignedTelecomCiphertext(ciphertexts));
+				nextSignedTCs.put(telecomId,
+						new SignedTelecomCiphertext(ciphertexts, numAgencies));
 				if (distance == maxDistance) {
 					nextSignedTCs.get(telecomId).setType(QueryType.CONCLUDE);
 				}
@@ -218,15 +220,15 @@ public class LeaderAgency extends Agency {
 
[…]

### 2016-02-27 src/cc/OversightAgency.java

@@ -5,7 +5,6 @@ import java.io.ObjectInputStream;
 import java.io.ObjectOutputStream;
 import java.net.Socket;
 import java.net.UnknownHostException;
-import java.util.HashMap;
 
 public class OversightAgency extends Agency {
 
@@ -66,11 +65,13 @@ public class OversightAgency extends Agency {
 	private boolean readResponseFromLeader(int distance)
 			throws ClassNotFoundException, IOException {
 		// Read, verify, and process the response of the previous telecom.
-		@SuppressWarnings("unchecked")
-		HashMap<Integer, SignedTelecomResponse> signedResponses =
-		(HashMap<Integer, SignedTelecomResponse>) leaderIStream.readObject();
-		for (int telecomId : signedResponses.keySet()) {
-			SignedTelecomResponse signedResponse = signedResponses.get(telecomId);
+		SignedTelecomResponse[] signedResponses =
+				(SignedTelecomResponse[]) leaderIStream.readObject();
+		for (int telecomId = 0; telecomId < numTelecoms; telecomId++) {
+			if (signedResponses[telecomId] == null) {
+				continue;
+			}
+			SignedTelecomResponse signedResponse = signedResponses[telecomId];
 			if (!keys.verify(signedResponse)) {
 				// If we failed to verify the signature, complain bitterly and quit.
 				System.err.println("Failed to verify a signature on a response from "
@@ -86,9 +87,14 @@ public class OversightAgency extends Agency {
 		if (distance == 0) {
 			// There is only one SignedTelecomReponse with one TelecomResponse in
 			// it, in this case.
-			int initialOwner = signedResponses.keySet().iterator().next();
-			targetDegree = signedResponses.get(initialOwner).
-					getTelecomResponses()[0].getTelecomCiphertexts().length;
+			int initialOwner;
+			for (initialOwner = 0; initialOwner < numTelecoms; initialOwner++) {
+				if (signedResponses[initialOwner] != null) {
+					break;
+				}
+			}
+			targetDegree = signedResponses[initialOwner].getTelecomResponses()[0].
+					getTelecomCiphertexts().length;
 		}
 		return true;
 	}
@@ -122,9 +128,16 @@ public class OversightAgency extends Agency {
 			// a telecom.
 			SignedTelecomCiphertext signedTC =
 					(SignedTelecomCiphertext) leaderIStream.readObject();
-			//There should be only one signature so far, with the leader's id
[…]

### 2016-02-27 src/cc/OversightFinalResultsThread.java

@@ -1,16 +1,15 @@
 package cc;
 
 import java.io.IOException;
-import java.util.HashMap;
 
 public class OversightFinalResultsThread extends CPUTrackingThread {
 
 	private OversightSocket oSocket;
-	private HashMap<Integer, SignedTelecomResponse> prevResponses;
+	private SignedTelecomResponse[] prevResponses;
 	private long oversightCpuTime = -1;
 
 	public OversightFinalResultsThread(OversightSocket oSocket,
-			HashMap<Integer, SignedTelecomResponse> prevResponses) {
+			SignedTelecomResponse[] prevResponses) {
 		super();
 		this.oSocket = oSocket;
 		this.prevResponses = prevResponses;

### 2016-02-27 src/cc/OversightSearchThread.java

@@ -1,22 +1,20 @@
 package cc;
 
 import java.io.IOException;
-import java.util.HashMap;
 
 public class OversightSearchThread extends CPUTrackingThread {
 
 	private OversightSocket oSocket;
-	private HashMap<Integer, SignedTelecomResponse> prevResponses;
-	private HashMap<Integer, byte[]> signatures = null;
+	private SignedTelecomResponse[] prevResponses;
+	private byte[][] signatures = null;
 
 	public OversightSearchThread(OversightSocket oSocket,
-			HashMap<Integer, SignedTelecomResponse> prevResponses) {
+			SignedTelecomResponse[] prevResponses) {
 		super();
 		this.oSocket = oSocket;
 		this.prevResponses = prevResponses;
 	}
 
-	@SuppressWarnings("unchecked")
 	public void runReal() {
 		if (!oSocket.open) {
 			System.err.println("Error: Oversight socket " + oSocket.getAgencyId() + " is closed!");
@@ -28,7 +26,7 @@ public class OversightSearchThread extends CPUTrackingThread {
 			oSocket.writeObject(prevResponses);
 			// If the oversight agency is in sync with us, they will know what our
 			// final queries should look like, and sign them.
-			signatures = (HashMap<Integer, byte[]>) oSocket.readObject();
+			signatures = (byte[][]) oSocket.readObject();
 		} catch (IOException e) {
 			e.printStackTrace();
 			oSocket.close();
@@ -39,7 +37,7 @@ public class OversightSearchThread extends CPUTrackingThread {
 	}
 
 	public byte[] getSignature(int telecomId){
-		return signatures.get(telecomId);
+		return signatures[telecomId];
 	}
 
 	public int getAgencyId(){

### 2016-02-27 src/cc/SignedTelecomCiphertext.java

@@ -1,7 +1,6 @@
 package cc;
 
 import java.io.Serializable;
-import java.util.HashMap;
 
 public class SignedTelecomCiphertext implements Serializable {
 
@@ -22,20 +21,21 @@ public class SignedTelecomCiphertext implements Serializable {
 	private static final long serialVersionUID = 1L;
 	private QueryType type;
 	private TelecomCiphertext[] telecomCiphertexts;
-	private HashMap<Integer, byte[]> signatures;
+	// Agency ID x will be in signatures[-x-1]
+	private byte[][] signatures;
 	// The maximum degree of users that agencies care about. Ignored if 0.
 	private int maxDegree = 0;
 
-	public SignedTelecomCiphertext(TelecomCiphertext telecomCiphertext) {
+	public SignedTelecomCiphertext(TelecomCiphertext telecomCiphertext, int numAgencies) {
 		telecomCiphertexts = new TelecomCiphertext[1];
 		telecomCiphertexts[0] = telecomCiphertext;
-		signatures = new HashMap<Integer, byte[]>();
+		signatures = new byte[numAgencies][];
 		type = QueryType.SEARCH;
 	}
 
-	public SignedTelecomCiphertext(TelecomCiphertext[] telecomCiphertexts) {
+	public SignedTelecomCiphertext(TelecomCiphertext[] telecomCiphertexts, int numAgencies) {
 		this.telecomCiphertexts = telecomCiphertexts;
-		signatures = new HashMap<Integer, byte[]>();
+		signatures = new byte[numAgencies][];
 		type = QueryType.SEARCH;
 	}
 
@@ -61,15 +61,15 @@ public class SignedTelecomCiphertext implements Serializable {
 	 * @param signature
 	 */
 	public void addSignature(int id, byte[] signature) {
-		signatures.put(id, signature);
+		signatures[-id-1] = signature;
 	}
 
 	/**
-	 * 
-	 * @return All signatures on the ciphertexts.
+	 * @param agencyId The agency whose signature we want
+	 * @return That agency's signature, if present.
 	 */
-	public HashMap<Integer, byte[]> getSignatures() {
-		return signatures;
+	public byte[] getSignature(int agencyId) {
+		return signatures[-agencyId-1];
 	}
 
 	/**

### 2016-02-27 src/nocrypto/Agency.java

@@ -215,20 +215,20 @@ public abstract class Agency {
 	}
 
 	/**
-	 * Returns, in array form, all known telecom ciphertexts for a given telecom.
-	 * @param owner The telecom we want ciphertexts for
+	 * Returns, in array form, all known telecom records for a given telecom.
+	 * @param owner The telecom we want records for
 	 * @return An array of TelecomRecords for that telecom
 	 */
-	protected TelecomRecord[] getCiphertexts(int owner) {
-		TelecomRecord[] ciphertexts = new TelecomRecord[0];
-		ciphertexts = investigationLists.get(owner).toArray(ciphertexts);
-		return ciphertexts;
+	protected TelecomRecord[] getRecords(int owner) {
+		TelecomRecord[] records = new TelecomRecord[0];
+		records = investigationLists.get(owner).toArray(records);
+		return records;
 	}
 
 	/**
-	 * @return the number of telecom ciphertexts in investigationLists
+	 * @return the number of telecom records in investigationLists
 	 */
-	protected int ciphertextsRemaining() {
+	protected int recordsRemaining() {
 		int total = 0;
 		for (ArrayList<TelecomRecord> list : investigationLists.values()) {
 			total += list.size();
@@ -245,7 +245,7 @@ public abstract class Agency {
 				println(telecomResponse.getTelecomRecords().length +
 						" not added to queue. Maximum path length reached");
 			} else if (distance == maxDistance) {
-				println("No ciphertexts added to queue. Maximum path length reached");
+				println("No records added to queue. Maximum path length reached");
 			} else if (telecomResponse.getTelecomRecords().length > maxDegree &&
 					distance > 0){
 				println(telecomResponse.getTelecomRecords().length +
@@ -361,8 +361,8 @@ public abstract class Agency {
 
 
 	/**
-	 * Saves the output agency ciphertexts to a file if a filename is specified,
-	 * or else just prints the number of agency ciphertexts that would have been
+	 * Saves the output agency records to a file if a filename is specified,
+	 * or else just prints the number of agency records that would have been
 	 * saved to file.
 	 * This prints something even if quiet mode is turned on. 
 	 */
@@ -387,7 +387,7 @@ public abstract class Agency {
 			}
 			bw.flush();
 			bw.close();
-			println("Wrote agency ciphertexts to " + config.getProperty(OUTPUT_PATH));
+			println("Wrote agency records to " + config.getProperty(OUTPUT_PATH));
[…]

### 2016-02-27 src/nocrypto/BatchedTelecomRecord.java

@@ -6,10 +6,10 @@ public class BatchedTelecomRecord implements Serializable {
 
 	/**
 	 * There are two kinds of messages.
-	 * SEARCH messages have one telecom ciphertext. In response, we want a
-	 * corresponding agency ciphertext and telecom ciphertexts for the neighbors.
-	 * CONCLUDE messages have many telecom ciphertexts. In response, we want
-	 * corresponding agency ciphertexts, but don't care about neighbors.
+	 * SEARCH messages have one telecom record. In response, we want a
+	 * corresponding agency record and telecom records for the neighbors.
+	 * CONCLUDE messages have many telecom records. In response, we want
+	 * corresponding agency records, but don't care about neighbors.
 	 * @author Aaron Segal
 	 *
 	 */

### 2016-02-27 src/nocrypto/LeaderAgency.java

@@ -105,12 +105,11 @@ public class LeaderAgency extends Agency {
 		investigationLists.put(initialOwner, new ArrayList<TelecomRecord>());
 		TelecomRecord startTCT = new TelecomRecord(targetId, initialOwner);
 
-		// Search on the first telecom ciphertext. It is different from the others
-		// because it does not have a telecom signature.
-		BatchedTelecomRecord firstSignedTC =	new BatchedTelecomRecord(startTCT);
+		// Search on the first telecom record.
+		BatchedTelecomRecord firstBatchedRecord = new BatchedTelecomRecord(startTCT);
 		OversightFirstThread[] firstThreads = new OversightFirstThread[oversight.length];
 		for (int i = 0; i < firstThreads.length; i++) {
-			firstThreads[i] = new OversightFirstThread(oversight[i], firstSignedTC);
+			firstThreads[i] = new OversightFirstThread(oversight[i], firstBatchedRecord);
 			firstThreads[i].start();
 		}
 		for (OversightFirstThread oft : firstThreads) {
@@ -124,19 +123,19 @@ public class LeaderAgency extends Agency {
 
 		println("Got first request for telecom ready to go.");
 
-		// Get response for the first telecom ciphertext. This is different from the
+		// Get response for the first telecom record. This is different from the
 		// general loop because we will not care about the degree of this first
 		// vertex.
 		connectTelecom(initialOwner);
-		HashMap<Integer, BatchedTelecomResponse> prevResponses =
-				new HashMap<Integer, BatchedTelecomResponse>();
+		BatchedTelecomResponse[] prevResponses =
+				new BatchedTelecomResponse[numTelecoms];
 		try {
-			writeObjectToTelecom(initialOwner, firstSignedTC);
-			BatchedTelecomResponse firstSignedResponse =
+			writeObjectToTelecom(initialOwner, firstBatchedRecord);
+			BatchedTelecomResponse firstBatchedResponse =
 					(BatchedTelecomResponse) readObjectFromTelecom(initialOwner);
-			prevResponses.put(initialOwner, firstSignedResponse);
-			recordTelecomCpuTime(firstSignedResponse.getCpuTime());
-			TelecomResponse telecomResponse = firstSignedResponse.getTelecomResponses()[0];
+			prevResponses[initialOwner] = firstBatchedResponse;
+			recordTelecomCpuTime(firstBatchedResponse.getCpuTime());
[…]

### 2016-02-27 src/nocrypto/OversightAgency.java

@@ -6,7 +6,6 @@ import java.io.ObjectOutputStream;
 import java.net.Socket;
 import java.net.SocketException;
 import java.net.UnknownHostException;
-import java.util.HashMap;
 
 public class OversightAgency extends Agency {
 
@@ -58,7 +57,7 @@ public class OversightAgency extends Agency {
 	}
 
 	/**
-	 * Reads a SignedTelecomResponse from the Leader and processes it.
+	 * Reads a BatchedTelecomResponse from the Leader and processes it.
 	 * @param distance The distance remaining at this point in the search.
 	 * @return True if the response validated OK, false if there was a problem.
 	 * @throws ClassNotFoundException
@@ -67,23 +66,30 @@ public class OversightAgency extends Agency {
 	private boolean readResponseFromLeader(int distance)
 			throws ClassNotFoundException, IOException {
 		// Read, verify, and process the response of the previous telecom.
-		@SuppressWarnings("unchecked")
-		HashMap<Integer, BatchedTelecomResponse> signedResponses =
-		(HashMap<Integer, BatchedTelecomResponse>) leaderIStream.readObject();
-		for (int telecomId : signedResponses.keySet()) {
-			BatchedTelecomResponse signedResponse = signedResponses.get(telecomId);
+		BatchedTelecomResponse[] batchedResponses =
+				(BatchedTelecomResponse[]) leaderIStream.readObject();
+		for (int telecomId = 0; telecomId < numTelecoms; telecomId++) {
+			if (batchedResponses[telecomId] == null) {
+				continue;
+			}
+			BatchedTelecomResponse batchedResponse = batchedResponses[telecomId];
 			for (TelecomResponse telecomResponse :
-				signedResponse.getTelecomResponses()) {
+				batchedResponse.getTelecomResponses()) {
 				processTelecomResponse(telecomResponse, distance);
 			}
 		}
 		// Get the degree of the initial target for timing purposes
 		if (distance == 0) {
-			// There is only one SignedTelecomReponse with one TelecomResponse in
+			// There is only one BatchedTelecomReponse with one TelecomResponse in
 			// it, in this case.
-			int initialOwner = signedResponses.keySet().iterator().next();
-			targetDegree = signedResponses.get(initialOwner).
-					getTelecomResponses()[0].getTelecomRecords().length;
+			int initialOwner;
+			for (initialOwner = 0; initialOwner < numTelecoms; initialOwner++) {
[…]

### 2016-02-27 src/nocrypto/OversightFinalResultsThread.java

@@ -1,16 +1,15 @@
 package nocrypto;
 
 import java.io.IOException;
-import java.util.HashMap;
 
 public class OversightFinalResultsThread extends cc.CPUTrackingThread {
 
 	private OversightSocket oSocket;
-	private HashMap<Integer, BatchedTelecomResponse> prevResponses;
+	private BatchedTelecomResponse[] prevResponses;
 	private long oversightCpuTime = -1;
 
 	public OversightFinalResultsThread(OversightSocket oSocket,
-			HashMap<Integer, BatchedTelecomResponse> prevResponses) {
+			BatchedTelecomResponse[] prevResponses) {
 		super();
 		this.oSocket = oSocket;
 		this.prevResponses = prevResponses;

### 2016-02-27 src/nocrypto/OversightFirstThread.java

@@ -23,10 +23,10 @@ public class OversightFirstThread extends cc.CPUTrackingThread {
 			oSocket.writeInt(oSocket.lAgency.getTargetId());
 			oSocket.open = true;
 
-			// Send the signed telecom ciphertext to the oversight agency
+			// Send the batched telecom ciphertext to the oversight agency
 			oSocket.writeObject(stc);
 
-			// Read the new signature back
+			// Read the OK
 			isOkay = (boolean) oSocket.readObject();
 		} catch (IOException e) {
 			e.printStackTrace();

### 2016-02-27 src/nocrypto/OversightSearchThread.java

@@ -1,16 +1,15 @@
 package nocrypto;
 
 import java.io.IOException;
-import java.util.HashMap;
 
 public class OversightSearchThread extends cc.CPUTrackingThread {
 
 	private OversightSocket oSocket;
-	private HashMap<Integer, BatchedTelecomResponse> prevResponses;
+	private BatchedTelecomResponse[] prevResponses;
 	private boolean isOkay;
 
 	public OversightSearchThread(OversightSocket oSocket,
-			HashMap<Integer, BatchedTelecomResponse> prevResponses) {
+			BatchedTelecomResponse[] prevResponses) {
 		super();
 		this.oSocket = oSocket;
 		this.prevResponses = prevResponses;
@@ -26,7 +25,7 @@ public class OversightSearchThread extends cc.CPUTrackingThread {
 			// telecom so they can stay in sync with us.
 			oSocket.writeObject(prevResponses);
 			// If the oversight agency is in sync with us, they will know what our
-			// final queries should look like, and sign them.
+			// final queries should look like, and okay them.
 			isOkay = (boolean) oSocket.readObject();
 		} catch (IOException e) {
 			e.printStackTrace();

### 2016-02-27 src/nocrypto/ResponseWorker.java

@@ -26,7 +26,7 @@ public class ResponseWorker extends cc.CPUTrackingThread {
 	 * Creates TelecomResponses for each TelecomRecord received, starting
 	 * from startIndex until either itemsToDo items have been converted,
 	 * or the end of the array is reached. 
-	 * Duplicate items will appear as null agency ciphertexts.
+	 * Duplicate items will appear as null agency records.
 	 */
 	public void runReal() {
 		for (int i = startIndex; i - startIndex < itemsToDo &&
@@ -48,7 +48,7 @@ public class ResponseWorker extends cc.CPUTrackingThread {
 				continue;
 			}
 
-			// Otherwise, we need to provide telecom ciphertexts for all neighbors.
+			// Otherwise, we need to provide telecom records for all neighbors.
 			int[] neighbors = data.getNeighbors(userId);
 			TelecomRecord[] neighborRecords =
 					new TelecomRecord[neighbors.length];

### 2016-02-27 src/nocrypto/Telecom.java

@@ -39,7 +39,6 @@ public class Telecom {
 	public static final String PUBLIC_KEYS = "PUBLICKEYS";
 	public static final String NUM_AGENCIES = "AGENCIES";
 	public static final String NUM_TELECOMS = "TELECOMS";
-	public static final String SIGNING_KEYPATH = "SIGKEYPATH";
 	public static final String MAX_THREADS = "MAXTHREADS";
 
 	private static void usage() {
@@ -146,14 +145,14 @@ public class Telecom {
 	}
 
 	private void sendResponse(TelecomResponse[] responses) throws IOException {
-		BatchedTelecomResponse signedTR = new BatchedTelecomResponse(responses, id);
+		BatchedTelecomResponse batchedTR = new BatchedTelecomResponse(responses, id);
 		// Add the cpu time from this thread plus all subthreads to this message.
 		long currentCpuTime = bean.getCurrentThreadCpuTime();
 		long cpuTimeToSend = data.getCpuTime() +
 				(currentCpuTime - lastCpuRecording);
 		lastCpuRecording = currentCpuTime;
-		signedTR.setCpuTime(cpuTimeToSend);
-		outputStream.writeObject(signedTR);
+		batchedTR.setCpuTime(cpuTimeToSend);
+		outputStream.writeObject(batchedTR);
 		outputStream.flush();
 	}
 
@@ -175,16 +174,16 @@ public class Telecom {
 				// thread for this, because we only ever expect to have one
 				// connection at a time.
 				while (true) {
-					BatchedTelecomRecord signedTC =
+					BatchedTelecomRecord batchedRecord =
 							(BatchedTelecomRecord) inputStream.readObject();
 
 					// Update maxDegree if we don't already know it
 					if (data.getMaxDegree() == Integer.MAX_VALUE &&
-							signedTC.getMaxDegree() > 0) {
-						data.setMaxDegree(signedTC.getMaxDegree());
+							batchedRecord.getMaxDegree() > 0) {
+						data.setMaxDegree(batchedRecord.getMaxDegree());
 					}
-					sendResponse(data.queryResponse(signedTC.getRecords(),
-							signedTC.getType()));
+					sendResponse(data.queryResponse(batchedRecord.getRecords(),
+							batchedRecord.getType()));
 				}
 			} catch (IOException e) {
 				System.err.println("Connection lost. Waiting for new connection");

### 2016-02-27 src/nocrypto/TelecomData.java

@@ -107,7 +107,7 @@ public class TelecomData {
 		currentResponses = new TelecomResponse[currentRecords.length];
 		int threads = Math.min(currentRecords.length, maxThreads);
 		int itemsPerThread = (currentRecords.length + threads - 1) / threads;
-		// Compute TelecomResponses to TelecomCiphertexts in threads
+		// Compute TelecomResponses to TelecomRecords in threads
 		ResponseWorker[] workers = new ResponseWorker[threads];
 		for (int i = 0; i < workers.length; i++) {
 			workers[i] = new ResponseWorker(this, itemsPerThread * i, 

### 2016-02-27 src/nocrypto/TelecomResponse.java

@@ -46,7 +46,7 @@ public class TelecomResponse implements Serializable {
 	}
 
 	/**
-	 * @return the telecomCiphertexts
+	 * @return the telecomRecords
 	 */
 	public TelecomRecord[] getTelecomRecords() {
 		return telecomRecords;

### 2016-02-27 paper/chaining.tex
Revised paper, including budget mechanism.
Updated paper directory

@@
-%!TEX TS-program = pdflatexmk
+\section{Lawful Contact Chaining}
+Contact chaining is a form of government surveillance with which it is deceptively easy to expose many innocent, untargeted users to government scrutiny.
+The goal of contact chaining is to use information about social connections between identities, such as records of phone calls between one number and another, to identify members of a criminal organization or terrorist group.
+Starting with one or more suspects whose identities are known, the government aims to consider contacts of those suspects.
+These can be \emph{direct contacts}, such as two people who spoke on the phone, or \emph{extended contacts}, such as two people connected by a chain of two or more phone calls.
+If Alice calls Bob, and Bob calls Charlie, then Alice and Bob are direct contacts (as are Bob and Charlie), but Alice and Charlie are extended contacts.
+We may also say that Alice and Charlie are at a distance of 2 in the social graph (since the shortest number of phone calls that connect Alice to Charlie is 2).
 
-%\documentclass{sig-alt-hotnetscr}
-\documentclass[12pt]{article}
+Without mechanisms to preserve privacy, a contact chaining search can collect a surprisingly large group of users' information.
+For example, if the average cell phone user contacts 30 individuals within the period of the investigation, a contact chaining search out to distance 3 would capture 27,000 users on average - or many more if a heavy phone user is swept up by the search.
+With such a large group, it is assured that the vast majority of contacts will not be the targeted collaborators of the primary suspect in the investigation.
+This is a large and unnecessary intrusion of privacy.
+These untargeted users may nevertheless face unwarranted government scrutiny, intrusive investigation, or a risk that their sensitive phone histories may be leaked accidentally.
 
-\input{setup}
+Despite this risk, we recognize the potential law-enforcement value of information about social connections between targeted invidivuals.
+Therefore, we propose a \emph{lawful contact chaining protocol}.
+This protocol permits multiple government agencies working together to provide oversight and accountability, as discussed in \cite{sff-foci2014}.
+Using this protocol, the agencies can retrieve an encrypted set of user data from multiple telecoms, each of which holds only part of a larger social graph.
+This encrypted set contains the identities of users within a certain distance of a target, but the identities cannot be decrypted unless the agencies cooperate.
+Under the lawful processes we propose, this cooperation would take the form of an intersecton with other encrypted sets of data, using the protocol from Section~\ref{sec-intersection}.
+These sets can come from privacy-preserving contact chaining, from cell tower dumps, or from other sources of information about suspects.
+Importantly, while any set may contain encrypted data about many untargeted users, very few users will appear in \emph{all} the sets, and those few users will be suitable targets for further lawful investigation.
 
-\begin{document}
-\clubpenalty=10000
-\widowpenalty = 10000
-\thispagestyle{empty}
+\subsection{Protocols For Privacy-Preserving Contact Chaining}
 
-\input{title}
-\input{protocol}
-\input{discussion}
+\label{sec:proto}
 
-\bibliographystyle{abbrv}
+%This is a candidate protocol for privacy-preserving contact chaining.
+We discuss the desired inputs, outputs, and security assumptions below, and then present two versions of the protocol in sections \ref{sec:proto1} and \ref{sec:proto2}.
 
-\bibliography{bibinfo2}
+\subsubsection{Inputs and Parties to the Protocol}
 
-%\endgroup
+There are two types of parties in this protocol: Telecommunications companies (telecoms) and government agencies interested in performing lawful contact-chaining (agencies).
+The protocol is a function of all parties' data.
 
-\end{document}
+The telecoms jointly hold an undirected contact graph $G=(V,E)$.
+Each telecom knows only a subset of the edges $E$.
+$V$ contains vertices labeled with the phone numbers they represent, and $E$ contains an edge between $a$ and $b$ if and only if phone number $a$ has contacted phone number $b$ or vice versa within some window of time.
+Each phone number $v$ is served by exactly one telecom.
+We assume telecoms know which telecom serves which phone number.
+Each telecom keeps records of all phone calls made by phones they serve, including calls made to phone numbers served by other telecoms.
+The subgraph known by telecom $T$ is $G_T=(V, E_T)$ where $E_T$ is the set of edges $(a, b)$ such that $a$ or $b$ is a phone number served by $T$.
+Henceforth, for any phone number $a$, let $T(a)$ be the telecom that serves $a$.
+
+In addition to the public knowledge which telecom serves which phone number, the agencies must each hold a copy of a \emph{warrant} in order to perform this protocol.
+A warrant is a triplet ($x$, $k$, $d$).
+$x$ is a target phone number.
+$k$ is a (small) distance from $x$, the distance at which the agencies wish to consider chained contacts.
+For example, if $k=2$, then the agencies only wish to consider users at most 2 phone calls away from their person (or phone number) of interest $x$.
+Choosing a small limit is important to limiting the scope of the investigation.
+However, many users' information might still be captured if some phone numbers have very many contacts.
+Suppose the target $x$ calls the most popular pizza place in town.
+Now everyone else who has recently called that pizza place is at a distance 2 to $x$.
+Therefore, the warrant also includes $d$, an upper bound on the degree of users the agencies are willing to ``chain'' through.
+If a phone number has more than $d$ contacts, then the agencies do not consider paths to other users through that phone number in their search.
+The agencies disregarded for the initial target $x$, however.
+
+We specify the protocol in full in sections~\ref{sec:proto1} and \ref{sec:proto2}.
+
+\subsubsection{Security Assumptions}
+
+We make a few assumptions about existing cryptographic infrastructure.
+All telecoms and agencies must have a public encryption key known to all other parties to the protocol and a private decryption key.
+For the purpose of interoperability with lawful intersection, agencies' keys must be for a commutative cryptosystem (i.e.
+ElGamal).
+The parties must also each have private signing keys and public verification keys.
+
+In the protocol below, we refer to ``the agencies'' sending messages to one or more telecoms.
+Exactly which agency transmits messages to the telecoms is not important to our protocol, but a telecom will disregard any message not accompanied by signatures from every agency.
+One simple topology is for a single agency to handle all direct communication with telecoms and with other agencies, forwarding reponses from the telecoms on to the other agencies and signatures on agency messages to the telecoms.
+
+\subsubsection{Desired Outputs and Security Properties}
+
+The desired output of the protocol is for the agencies to learn an encryption of the set of phone numbers within distance $k$ of the targeted phone $x$ in the call graph.
+The set should exclude numbers for which the only paths from $x$ use an intermediate vertex of degree greater than $d$.
+
+Every phone number in this set must be encrypted with each of the agencies' public ElGamal keys. The agencies should all have the same output.
+
+The telecoms should not learn the agency's output.
+Instead, each telecom's output should contain only a list of which of the phone numbers it serves were sent to the government agencies.
+This allows the telecoms to play an additional accountability role in this protocol.
+The government may have an interest in keeping the telecoms from knowing which of their clients were surveilled; we discuss this in section~\ref{sec:oblivious}.
+
+With the encryptions of these phone numbers, the agencies can then act as appropriate to further investigate them.
+In particular, the encrypted set of phone numbers can be used as an input into a lawful set intersection protocol.
+
+We assume that all telecoms honestly follow the protocol and submit accurate information about the phone numbers they serve and the records they keep.
+We assume they send no ciphertexts to the agencies except when called for in the protocol.
+In practice, existing legal tools allow law enforcement agencies to gather information about the phone call history of a suspect with a valid warrant, but such information cannot generally be used for further contact chaining.
+
+Below, we present two versions of our protocol.
+In the first version, the agencies and telecoms learn some additional information.
+Specifically, the agencies learn the provider of each phone number in the encrypted set, and the distance from $x$ of each encrypted phone number.
+Each telecom learns which of the phone numbers it serves appear in the agencies' output, as well as the distance of each of those phone numbers from the target phone number $x$.
+
+In section \ref{sec:proto2}, we will present a second version of the protocol in which the agency \emph{does not} learn which telecom serves which encrypted phone number.
+
+As long as all parties honestly follow the protocol, the agencies collectively learn \emph{no} information about the edge set $E$ except what is implied by the output.
+Furthermore, as long as at least one agency follows the protocol honestly and does not collude with the others, the remaining agencies cannot learn any of the phone numbers that appear in encrypted form in the output (unless implied by the size of the encrypted output and the leaked service information), nor can the colluding agencies cause a phone number not within distance $k$ of target $x$ to appear in the output, even in encrypted form.
+Telecoms have the ability to send additional information about their users to agencies or other telecoms at any time, but we assume they will not wish to do so, since they have a business interest to protect user information and comply with the law.
+We assume that all telecoms follow the protocol honestly.
+
+\subsubsection{First Lawful Contact-Chaining Protocol}
+
+\label{sec:proto1}
+
+The protocol below amounts to a distributed breadth-first search of the social graph run by the agencies making queries of the telecoms.
+However, all messages the agencies receive from the telecoms will be encrypted.
+They will know which message come from which telecoms, and will therefore know which telecoms serve which ciphertexts.
+
+Let $\Enc_T(m)$ be the encryption of message $m$ under telecom $T$'s public key.
+Call such an encryption a \emph{telecom ciphertext}.
+Let $\Enc_\mathcal{A}(m)$ be the encryption of $m$ under the public keys of all agencies, and call such an encryption an \emph{agency ciphertext}.
+
+To manage the breadth-first search, the agencies (or at least the investigating agency) will maintain a queue $\mathbf{Q}$, containing vertices yet to explore.
+$\mathbf{Q}$ contains tuples for unexplored vertices $a$ of the form $(\Enc_{T(a)}(a), T(a), j)$.
+These tuples contain the telecom ciphertext for $a$, a record of which telecom owns $a$, and an integer $j$ indicating the remaining distance out to which neighbors can be chained from $a$.
+
+The agencies will represent their output in the form of a list $\mathbf{C}$, containing agency ciphertexts.
+Each telecom $T$ will represent its output in the form of a list $\mathbf{L}_T$, listing plaintext users served by that telecom whose information the agencies requested.
+
+The protocol is as follows:
+
+\begin{enumerate}
+
+\item The agencies start by agreeing upon a warrant $(x, k, d)$, where $x$ is the target phone number, $k$ is a maximum distance, and $d$ is an upper limit on the degree of vertices to chain through.
+They encrypt $x$ under the public key of $T(x)$.
+
+\item The agencies initialize a queue $\mathbf{Q}$. Initially, $\mathbf{Q}$ contains only the triple $(\Enc_{T(x)}(x), T(x), k)$.
+
+\item The agencies initialize the output list $\mathbf{C}$ to be empty.
+
+\item Each telecom $T$ initializes its output list $\mathbf{L}_T$ to be empty.
+
+\item While $\mathbf{Q}$ is not empty, do the following:
+
+\begin{enumerate}
+
+\item \label{proto1:top-of-loop} The agencies dequeue $(\Enc_{T(a)}(a), T(a), j)$ from $\mathbf{Q}$. They send the pair ($\Enc_{T(a)}(a), j)$ to $T(a)$.
+
+\item $a$'s provider, $T(a)$, decrypts $a$ from its telecom ciphertext. It adds $a$ to $\mathbf{L}_T$.
+
+\item \label{proto1:first-send} $T(a)$ encrypts $a$ under the agencies' public keys, and sends $\Enc_\mathcal{A}(a)$ to the agencies.
+
+\item If $j=0$, $T(a)$ is done. Go to step \ref{proto1:receive}.
+
+\item Otherwise, $T(a)$ encrypts each neighbor $b$ of $a$ under the public key of $T(b)$, creating a telecom ciphertext for $b$.
+
+\item \label{proto1:second-send} $T(a)$ sends the number of ciphertexts generated this way, $\de(a)$, as well as all telecom ciphertexts generated in the previous step, to the agencies.
+$T(a)$ sends the ciphertexts in the form of pairs $(\Enc_{T(b)}(b), T(b))$.
+
+\item \label{proto1:receive} The agencies add $\Enc_\mathcal{A}(a)$ to $\mathbf{C}$.
+
+\item If $\de(a)>d$ and $j\neq k$ (i.e.
+$a\neq x$), the agencies discard all telecom ciphertexts received for $a$'s neighbors (i.e., agencies refuse to sign these ciphertexts in future steps of the protocol, and do not send them on to the telecoms).
+
+\item Otherwise, for each telecom ciphertext received, the agencies add $(\Enc_{T(b)}(b), T(b), j-1)$ to $\mathbf{Q}$.
+
+\end{enumerate}
+
+\item The agencies' final output is the list $\mathbf{C}$. Each telecom $T$'s final output is $\mathbf{L}_T$.
+
+\end{enumerate}
+
+For the sake of efficiency, it is worth noting that the inner loop can be executed many times in parallel, up to the point of completely emptying $\mathbf{Q}$ at the beginning of the loop.
+Many messages to the same telecom can also be batched and sent together, reducing the number of signing and verifying operations to depend only on $k$ and not on the size of the input or output.
+
+\subsubsection{Ownership-Hiding Lawful Contact-Chaining Protocol}
+
+\label{sec:proto2}
+
+The previous version of the protocol allows agencies to learn which telecoms own the phone numbers in its encrypted output.
+This subsection presents a modification of the previous version of the protocol, which uses a DC-nets-based \emph{anonymity protocol} to hide this information from the agencies (except with respect to the initial target $x$).
+
+An anonymity protocol is run between a number of parties, some of which have a message to send.
+At the end of the protocol, all parties must learn all messages sent, but no party other than the sender of any given message learns which party sent that message.
+Dissent~\cite{dissent} and Verdict~\cite{verdict} both satisfy our requirements, although they are more powerful than we need here, since we assume all telecoms are honest-but-curious.
+
+We can use an anonymity protocol to allow the correct telecom to respond anonymously in steps \ref{proto1:first-send} and \ref{proto1:second-send} in the protocol above.
+This removes the need for the agencies to know which telecom owns which ciphertext.
+
+Now we can present the following modified protocol.
+This protocol uses the same data structures as in section~\ref{sec:proto1}, except that $\mathbf{Q}$ now contains pairs $(\Enc_{T(a)}(a), j)$ for unexplored vertices $a$ (omitting the identity of $T(a)$.
+
+\begin{enumerate}
+
+\item The agencies start by agreeing upon a warrant $(x, k, d)$, where $x$ is the target phone number, $k$ is a maximum distance, and $d$ is an upper limit on the degree of vertices to chain through.
+They encrypt $x$ under the public key of $T(x)$.
+
+\item The agencies initialize a queue $\mathbf{Q}$. Initially, $\mathbf{Q}$ contains only the pair $(\Enc_{T(x)}(x), k)$.
+
+\item The agencies initialize the output list $\mathbf{C}$ to be empty.
+
+\item Each telecom $T$ initializes its output lists $\mathbf{L}_T$ to be empty.
+
+\item While $\mathbf{Q}$ is not empty, do the following:
+
+\begin{enumerate}
+
+\item \label{proto2:dequeue} The agencies dequeue a pair $(\Enc_{T(a)}(a), j)$ from $\mathbf{Q}$. They send the pair $(\Enc_{T(a)}(a), j)$ to all telecoms.
+
+\item All telecoms attempt to decrypt $\Enc_T(a)(a)$ with their decryption keys. Only $T(a)$ will be able to do so. Other telecoms skip to step~\ref{proto2:anon}.
+
+\item $T(a)$ adds $a$ to $\mathbf{L}_T$.
+
+\item \label{proto2:agencycipher} $T(a)$ encrypts $a$ under the agencies' public keys, producing the agency ciphertext $\Enc_\mathcal{A}(a)$.
+
+\item \label{proto2:telecomcipher} If $j>0$, $T(a)$ encrypts each neighbor $b$ of $a$ under the public key of $T(b)$, creating a telecom ciphertext for $b$.
+
+\item \label{proto2:anon} All parties to this protocol engage in the anonymity protocol.
+$T(a)$ sends an anonymous message consisting of the agency ciphertext it generated in step~\ref{proto2:agencycipher}; the set of telecom ciphertexts generated in step \ref{proto2:telecomcipher}, and $\de(a)$, the number of telecom ciphertexts being sent.
+The agencies and all telecoms that could not decrypt $\Enc_{T(a)}(A)$ participate but send no anonymous message.
+
+\item When the anonymity protocol is complete, the agencies receive all the ciphertexts. They add $\Enc_\mathcal{A}(a)$ to $\mathbf{C}$.
+
+\item If $\de(a)>d$ and $j\neq k$ (i.e.
+$a\neq x$), the agencies discard all telecom ciphertexts received for $a$'s neighbors (i.e., agencies refuse to sign these ciphertexts in future steps of the protocol, and do not send them on to the telecoms).
+
+\item Otherwise, for each telecom ciphertext received, the agencies add $(\Enc_{T(b)}(b), j-1)$ to $\mathbf{Q}$.
+
+\end{enumerate}
+
+\item The agencies' final output is the list $\mathbf{C}$. Each telecom $T$'s final output is $\mathbf{L}_T$.
+
+\end{enumerate}
+
+The protocol replaces each query in the protocol of section~\ref{sec:proto1} with broadcast of the telecom ciphertext to all telecoms, and replaces each response with a round of the anonymity protocol.
+This allows the telecom that owns each phone number to respond with appropriate information about the phone number, but shields the telecom's identity from the agencies (and incidentally from other telecoms).
+
+As in the previous section, It should be noted that the agencies and telecoms need not handle one ciphertext at a time.
+The agencies can in principle dequeue all of $\mathbf{Q}$ in step \ref{proto2:dequeue} and broadcast all pending vertices to the telecoms.
+In step \ref{proto2:anon}, multiple telecoms can submit multiple messages to a single run of the anonymity protocol, with only those telecoms which were unable to decrypt any vertices submitting no message.
+The exact number of messages per instance of the anonymity protocol can be tuned for best efficiency.
+
+\subsection{Discussion of Lawful Contact-Chaining}
+
+\label{sec:discuss}
+
+We now take a moment to discuss the correctness and privacy properties of both variants of our lawful contact-chaining protocol.
+
+\subsubsection{Correctness of Output}
+
+If all parties behave in an honest or honest-but-curious way in following to the protocols above, then the agencies' outputs will be $\mathbf{C}$.
+$\mathbf{C}$ will contain agency ciphertexts of all phone numbers at most $k$ phone calls away from $x$, considering only vertices of degree at most $d$.
+This is the desired output.
+$C$ reveals nothing to any agencies unless they all provide their decryption keys.
+To continue the process of lawful investigation, the agencies should combine the output $\mathbf{C}$ with other sets of potential suspects (such as from further runs of this protocol, or from cell tower dumps) in a lawful intersection protocol.
+
+\subsubsection{Privacy}
+
+Both versions of the protocol hide the identities of the chained contacts of $x$.
+They do allow the agencies to learn the distance from $x$ of each ciphertext in their output, but these ciphertexts cannot be resolved to phone numbers without the cooperation of all agencies.
+
+The protocol of section~\ref{sec:proto1} allows the agencies to learn which telecoms owns which ciphertexts in $\mathbf{C}$.
+This may be a security concern, since some telecoms are relatively small, specialized, or localized to a particular country or region.
+If the agencies know that such a such a telecom owns an encrypted phone number, this will not allow them to identify the phone number itself, but might convince the agencies to subject that ciphertext to additional scrutiny, up to the point of decrypting it outside the context of lawful surveillance.
+This would still require the collusion of all agencies, however.
+Our revised protocol mitigates this concern.
+Assuming that the anonymity protocol used in section~\ref{sec:proto2} does not allow its participants to learn who sends each message, then the revised protocol does not leak ciphertext ownership information.
+
+The telecoms learn two types of information as part of the lawful contact chaining protocol.
+First, they learn the warrant.
+Second, they learn which of the phone numbers they serve have been captured (in encrypted form) by the protocol, and when they were captured.
+The telecoms might possibly be able to infer some extra information about $G$ from observing when vertices they own are queried by the agencies, but only of a very limited form.
+For instance, an agency may serve two phone numbers, $a$ and $b$, which the agencies query at distance 1 and 4 from $x$, respectively .
+In that case, the telecom can infer that there exists a path in $G$ of length 3 between $a$ and $b$.
+The telecom does not learn which other phones are involved in that path, and is already aware of all paths of length 2 or less between phone numbers it serves.
+Therefore, this potential information leak is of little concern.
+
+\subsubsection{Hiding Information From Telecoms}
+
+\label{sec:oblivious}
+
+In both versions of our protocol, the telecoms learn which of their numbers have been submitted to the agencies.
+They do not know which phone numbers the agencies will actually investigate after running the privacy-preserving set intersection protocol, but they do know which ones \emph{could} be under investigation.
+Since many numbers \emph{could} be investigated, this does not compromise the agencies' investigative power.
+
+We may point out nevertheless that a modification of our protocol from \ref{sec:proto1} could allow the agencies to hide from the telecoms which of their clients is being surveilled.
+The telecoms would need to precompute agency ciphertexts for all of their client numbers, and telecom ciphertexts for all of their clients' contacts.
+With these precomputed databases, the telecoms could then use oblivious transfer to blindly serve the agencies' requests for information about their clients.
+
+\subsection{Performance of Privacy-Preserving Contact Chaining Protocol}
+
+\label{sec:implementation}
+
+We implemented the privacy-preserving contact chaining search protocol of~\ref{sec:proto1} in Java and tested the implementation's running time, CPU time used, and data sent over the network.
+Below, we describe our implementation and its experimental setup, and then summarize our results.
+
+\subsubsection{Java Implementation}
+
+Our Java implementation uses the variant of our protocol in which the agencies completely exhaust the search queue $\mathbf{Q}$ each round, sending all queries at any given distance from $x$ to the telecoms at once in batches.
+Ths variant allows for greater parallelism.
+All of the telecoms receive their batch of queries at the same time, and operate on those queries using eight parallel threads of computation.
+
+We use 2048-bit DSA signatures, 2048-bit RSA encryption for the telecoms, and ElGamal encryption for the agencies' output to provide compatability with the lawful intersection protocol of~\cite{sff-foci2014}.
+
+Our Java program supports any number of agencies and telecoms, but we chose to run tests with three government agencies and four telecoms.
+Each agency and telecom has a dedicated server in our cloud testbed.
+As mentioned in~\cite{sff-foci2014}, three is a reasonable choice for the number of agencies, corresponding to three branches of government.
+Four telecoms should cover most users in any given mobile phone market, and increasing the number of telecoms in our experiments only serves to decrease the protocol's total running time by splitting the same users over more servers.
+
+\subsubsection{Experimental Setup}
+
+For our underlying contact graph, we used an anonymized data set provided by~\cite{snapnets} containing 1.6 million users from Pokec, a Slovakian social network.
+To replicate the multi-provider environment of the real telephone network, we assigned each user to one of four telecom servers.
+The telecoms were each given a different number of the users, in proportion to the subscriber base of the largest four telecoms in the world~\cite{mobiforge}.
+
+To experiment with differently sized output sets, we ran our protocol many times, varying $x$, $k$, and $d$.
+We chose a variety of different-degree starting targets $x$, varied the maximum path length $k$ between 2 and 3, and varied $d$ from 25 to 500.
+For each run, we measured the total running time of the protocol, the CPU time spent by the agencies and telecoms, and the amount of data sent over the network in total.
+
+%These results are important in evaluating how practical our lawful contact-chaining protocol would be it were put into practice by government agencies and telecoms.
+However, our data set is relatively small compared to the databases held by real telecommunications companies, and each company handles that data using different technologies.
+The absolute running time and CPU usage of executing this protocol could vary from telecom to telecom.
+Therefore, we also produced a implementation of the contact-chaining protocol which omits all cryptographic operations.
+This version of the protocol does not preserve the privacy of users.
+By comparing the performance of our lawful contact-chaining protocol with the zero-privacy contact-chaining protocol, however, we can get a sense of the ``cost'' of privacy and accountability as compared to the practice of releasing plaintext data to government surveillance.
+
+\subsubsection{Results}
+
+\begin{figure*}[t]
+
+\centering
+
+\begin{subfigure}{.33\textwidth}
+
+\centering
+
+\includegraphics[width=0.99\textwidth]{runtime.pdf}
+
+\captionsetup{justification=centering}
+
+\caption{Protocol Runtime}
+
+\label{fig:runtime}
+
+\end{subfigure}\hfill
+
+\begin{subfigure}{.33\textwidth}
+
+\centering
+
+\includegraphics[width=0.99\textwidth]{cputime.pdf}
+
+\captionsetup{justification=centering}
+
+\caption{CPU Time}
+
+\label{fig:cputime}
+
+\end{subfigure}\hfill
+
+\begin{subfigure}{.33\textwidth}
+
+\centering
+
+\includegraphics[width=0.99\textwidth]{bandwidth.pdf}
+
+\captionsetup{justification=centering}
+
+\caption{Network Data}
+
+\label{fig:data}
+
+\end{subfigure}
+
+\caption{Performance of Lawful Contact-Chaining}
+
+\label{fig:performance}
+
+\end{figure*}
+
+Our implementation of lawful contact-chaining performed well.
+Our experiments showed a linear relationship between the number of ciphertexts in the output and the running time, CPU time, and data usage of the protocol.
+We display graphs of our recorded data in Figure~\ref{fig:performance}.
+Taking the average of all cases with $d>25$, the telecoms used 58.2 ms of CPU time per ciphertext.
+The agencies used, again in the average case, 2.0 ms of CPU time per ciphertext.
+Note that these times are the sums taken over all telecoms and all agencies respectively.
+Because the agencies have do very little cryptography in this protocol, we focus on the telecoms' CPU time in our evaluation.
+
+We found that our protocol was able to process, in the average case, 197.4 ciphertexts per second.
+To return to our example from earlier of a network with an average of 30 contacts per user, a lawful contact-chaining search with $k=2$ would have 900 users in the output, and a search with $k=3$ would have 27,000 users in the output.
+To compare these times to some of our acutal experiments, we found that a search that returned 937 ciphertexts took 6.86 seconds to run, and a search that returned 27,338 ciphertexts took 109.55 seconds to run.
+To provide another point of comparison, \cite{sff-foci2014} referred to the ``High Country Bandits'' case, in which the FBI performed an intersection of 150,000 phone number to help solve a series of bank robberies.
+In one of our experiments with lawful contact chaining, we find that a similarly sized data set of 149,535 ciphertexts took 625.08 seconds - 10.4 minutes - to compile with our protocol.
+Given the context of a criminal investigation, we feel these running times are quite reasonable.

### 2016-02-27 paper/intersection.tex
Updated paper directory

\section{Lawful Intersection Warrants}\label{sec-intersection}
In this section, we present an improved implementation of the lawful
set-intersection protocol of~\cite{sff-foci2014}. 
{\bf Create Subsections 3.1 and 3.2.  Add something about why this protocol
satisfies the openness principle.}

The participants in this
protocol are government agencies. Before executing the protocol, the 
agencies must agree on which sets of encrypted user data they wish to 
intersect. These sets are then retrieved from a repository, which stores 
only ciphertexts encrypted with the ElGamal public keys of all agencies.

Each agency's input is its ElGamal private key and a set of this encrypted data. For each execution of the protocol, the agencies also generate temporary 
Pohlig-Hellman keys, which they securely delete after the protocol is complete. 
The protocol works by converting ciphertexts in the probabilistic ElGamal 
cryptosystem to ciphertexts in the deterministic Pohlig-Hellman 
cryptosystem without revealing information about the encrypted data in the 
process. Because Pohlig-Hellman is deterministic, two identical user 
identifiers will have identical Pohlig-Hellman encryptions.

These two cryptosystems, ElGamal and Pohlig-Hellman, allow this 
conversion to take place because they are \emph{mutually commutative} with 
each other. That is, a ciphertext encrypted under some combination of 
multiple ElGamal encryption keys, multiple Pohlig-Hellman encryption keys, 
or a mixture of the two types of keys can be decrypted only by the 
corresponding set of decryption keys \emph{in any order}. ElGamal and 
Pohlig-Hellman are randomized and deterministic, respectively, and they 
satisfy the mutual commutativity requirement.

During the protocol, each agency in turn runs the ElGamal decryption 
algorithm on the ciphertexts using its private key, then runs the 
Pohlig-Hellman encryption algorithm using its temporary Pohlig-Hellman key. 
Because the ciphertexts are also encrypted under the keys of the other 
agencies, the agency does not learn anything about the underlying user 
data during this process. The agency then passes the altered ciphertexts on 
to the next agency, which does the same with its keys. At the conclusion of 
this process, the agencies have converted the ciphertexts from randomized 
ElGamal encryption to determinstic Pohlig-Hellman encryption, without 
ever revealing the plaintext data.

The agencies can then directly compare Pohlig-Hellman ciphertexts to each 
other to determine which appear in the intersection of all three sets of data. 
If the intersection is much larger than expected, any one of the agencies can 
delete its Pohlig-Hellman decryption key to prevent any user data from being 
revealed until a more narrowly scoped warrant can be agreed upon. Otherwise, 
the agencies finish the protocol by using their Pohlig-Hellman decryption keys 
to reveal only the ciphertexts in the intersection of all three sets.

\subsection{Improved Implementation of Lawful Intersection}

In \cite{sff-foci2014}, the authors presented a Java implementation of the 
lawful set-intersection protocol. It ran on three PlanetLab computers 
representing the participating government agencies. 
Although the servers split the data sets between them, the implementation 
handled each set in a sequential manner, decrypting and encrypting 
ciphertexts one by one.

{\bf Add something about the argument that SFF made about their protocol's
being fast enough.}

We have produced an improved implementation
that takes advantage of parallel processing and more advanced computational 
hardware, thus showing that lawful set-intersection can be performed 
much more quickly than originally descrbied in~\cite{sff-foci2014}.

In our upgraded implementation, the agencies decrypt and encrypt 
multiple ciphertexts in parallel, rather than operating on them one by one. 
We use eight compute threads for each server. Instead of PlanetLab computers, 
which vary in speed and reliability, we use three separate hosts on a private 
cloud-computer system running on Open Stack with a Ceph storage backend.

Compared with the orginal, sequential version of the protocol, our version 
requires only about 10\% as much time to run to completion. In the 
largest test case, which contains a total of 
150,000 ciphertexts (50,000 per server), our implementation takes 10.5 minutes, 
compared with 116.2 minutes for the orginal one. A full comparison of our 
results with the those of~\cite{sff-foci2014} is presented in 
Figure~\ref{fig:isectgraph}.

\begin{figure}
\centering
\includegraphics[width=0.99\columnwidth]{intersectionchart.pdf}
\caption{Comparison of Lawful Intersection Performance}
\label{fig:isectgraph}
\end{figure}

### 2016-02-27 paper/intro.tex
Updated paper directory

@@
-\section{Introduction To Contact Chaining}
+\section{Introduction}
+As networked devices become more available, more capable, and more ubiquitous
+in everyday life, tension mounts between users' desire to safeguard their 
+personal information and government agencies' desire to use that personal 
+information in their pursuit of criminals and terrorists.  For example, 
+both the heated (and still unresolved) discussion about the Snowden 
+revelations that started in 2013 and the ongoing dispute between Apple and 
+the US Justice Department are understood by many people
+as examples of an unpleasant, stark choice: Citizens can either have
+secure devices and control over their personal information, or they can have
+law-enforcement and intelligence agencies with the tools that they need to
+keep the country safe. We regard this stark choice as a false dichotomy and 
+assert that, by deploying appropriate security technology in the context of 
+sound policy and the rule of law, we can have both user privacy and effective 
+law enforcement and intelligence.
 
-Contact chaining is a form of government surveillance.
-The goal of contact chaining is to use information about social connections between identities, such as records of phone calls between one number and another, to identify members of a criminal organization or terrorist group.
-Starting with one or more suspects whose identities are known, the government aims to consider contacts of those suspects.
-These can be \emph{direct contacts}, such as two people who spoke on the phone, or \emph{extended contacts}, such as two people connected by a chain of two or more phone calls.
-If Alice calls Bob, and Bob calls Charlie, then Alice and Bob are direct contacts (as are Bob and Charlie), but Alice and Charlie are extended contacts.
-We may also say that Alice and Charlie are at a distance of 2 in the social graph (since the shortest number of phone calls that connect Alice to Charlie is 2).
-
-Without mechanisms to preserve privacy, a contact chaining search can collect a surprising large group of users' information.
-And, unless criminals or terrorists only contact other members of their organizations, most of them are unlikely to be the intended targets of the investigation.
-This is a large and unnecessary intrusion of privacy.
-These untargeted users may nevertheless face unwarranted government scrutiny, intrusive investigation, or a risk that their sensitive phone histories may be leaked accidentally.
-
-We propose to replace a contact chaining search in which a single government agency collects user data in the clear from the telecoms who own it with a \emph{privacy-preserving contact chaining protocol}.
-This protocol involves multiple government agencies, each of whom must actively agree to each step of the search, or the search ends.
-Instead of revealing to the agencies a large, plaintext list of phone numbers and their connections to each other, it gives the agencies only an encrypted list of phone numbers.
-The numbers in this list are encrypted using the public keys of all three agencies in a randomized, public-key, commutative cryptosystem (such as ElGamal).
-This output can then be compared with other encrypted lists, such as encrypted cell tower dumps, watch lists, or the output from another run of this protocol.
-By using the protocol described in~\cite{bandits}, the phone numbers that appear in multiple lists can be decrypted jointly by the agencies, while other phone numbers remain encrypted and unreadable as long as the government agencies do not all collude.
-
-In section \ref{sec:proto} we discuss the participants, inputs, outputs, and assumptions of our privacy-preserving contact chaining protocol, and present two versions of the protocol itself in sections \ref{sec:proto1} and \ref{sec:proto2}.
-In section \ref{sec:discuss} we discuss the privacy of our protocol.
+At first blush, it may seem that a symposium on ``privacy-enhancing 
+technologies'' is an odd place for results about ``accountable surveillance.''
+No doubt some in the PETS community wish to prevent government agencies 
+(as well as large corporations and other powerful entities) from conducting 
+{\it any} surveillance whatsoever.  As explained in \cite{sff-foci2014}, a 
+global communication system entirely free of surveillance may be appealing in
+the abstract, but it is not a very useful goal in practice.  Law enforcement
+and intelligence agencies have always been and will continue to be active 
+on the Internet and in all national- and global-scale communication systems.
+The challenge for the technical community is to build systems that enable
+government agencies to collect relevant data that they are legally authorized
+to collect, to be held accountable to the citizens they serve, and to respect 
+privacy of innocent users.

### 2016-02-27 paper/open.tex
Updated paper directory

\section{The Openness Principle in Lawful Surveillance}
In this section, we review the openness principle put forth by Segal 
{\it et al.}~\cite{sff-foci2014}.  Readers familiar with \cite{sff-foci2014} 
may skip to the next section.

Necessary to any meaningful discussion of ``accountable surveillance'' is an
established foundation of rule of law and democratic processes that subject
the laws to evaluation, debate, and revision.  Bulk surveillance must follow
{\it open processes}, {\it i.e.}, unclassified procedures laid out in public 
laws that all citizens have the right to read, to understand, and to challenge
through the political process.  Processes that are not open, public, and
unclassified in this sense are referred to as {\it secret processes}.  
Although government agencies need not always disclose all of the details of a 
particular investigation, they do need to follow the open processes 
established for all bulk surveillance.

More precisely, Segal {\it et al.}~\cite{sff-foci2014} draw a distinction 
between two classes of communication-system users.  {\it Targeted users} are 
those who are under suspicion and are targets of properly authorized warrants.
All others are {\it untargeted users}; they are the vast majority of all 
users of a general-purpose, mass-communication system.  Segal {\it et 
al.}~\cite{sff-foci2014} posit that the
following {\it Openness Principle} should govern all surveillance activity
in a democratic society:

\begin{enumerate}
\item[I]
Any surveillance or law-enforcement process
that obtains or uses private information
about untargeted users shall be
an open, public, unclassified process.
\item[II]
Any secret surveillance or law-enforcement processes shall use only:
\begin{enumerate}
\item[(a)] public information, and
\item[(b)] private information about targeted users obtained under 
authorized warrants via open surveillance processes.
\end{enumerate}
\end{enumerate}
Segal {\it et al.} interpret this principle as a requirement that an open
``privacy firewall'' be placed between government agencies and citizens'
private information in a mass-communication network.  Processes that move
untargeted users' private information through the firewall must be open
processes.  More generally, the openness principle asserts that, by using
appropriate security technology, government agencies can make their 
data-collection {\it processes} fully public without revealing sensitive
{\it content} of a specific investigation.  For a more detailed explanation,
see Section 2 of \cite{sff-foci2014}.

### 2016-02-27 paper/submission.tex
Updated paper directory

\documentclass[USenglish,oneside,twocolumn]{article}

\usepackage[utf8]{inputenc}%(only for the pdftex engine)
%\RequirePackage[no-math]{fontspec}%(only for the luatex or the xetex engine)
\usepackage[big]{dgruyter_NEW}

\DOI{foobar}

\cclogo{\includegraphics{by-nc-nd.pdf}}

\DeclareMathOperator{\Enc}{Enc}

\DeclareMathOperator{\Dec}{Dec}

\DeclareMathOperator{\de}{deg}

\usepackage{subcaption}

\begin{document}

  %\author*[1]{Aaron Segal}
  \author[1]{Names withheld}

  %\author[2]{Bryan Ford}

  %\author[3]{Joan Feigenbaum}

  %\affil[1]{Yale Univ., E-mail: Aaron.Segal@yale.edu}
  \affil[1]{Affiliations and email addresses withheld}

  %\affil[2]{EPFL, E-mail: Bryan.Ford@epfl.ch}

  %\affil[3]{Yale Univ., E-mail: Joan.Feigenbaum@yale.edu}

  \title{\huge Open, privacy-preserving protocols for lawful surveillance}

  \runningtitle{Privacy-preserving, lawful surveillance}

  %\subtitle{...}

  \begin{abstract}
{As demonstrated, {\it e.g.}, by Snowden's revelation of controversial NSA 
activity and by Apple's refusal to obey a Justice Department's order to break 
an iPhone security mechanism, the question of how government agencies can
acquire actionable, useful information about legitimate but unknown targets 
without intruding upon the electronic activity of innocent parties is 
extremely important.  We address this question by providing experimental
evidence that actionable, useful information can indeed be obtained in a manner
that preserves the privacy of innocent parties and that holds government
agencies accountable.  In particular, we present practical, privacy-preserving
protocols for two operations that law-enforcement and intelligence agencies
have used effectively: {\it set intersection} and {\it contact chaining}.}
  \end{abstract}
  \keywords{Privacy, Secure multiparty computation, Surveillance}
%  \classification[PACS]{}
 % \communicated{...}
 % \dedication{...}

  \journalname{Proceedings on Privacy Enhancing Technologies}
\DOI{Editor to enter DOI}
  \startpage{1}
  \received{February 29, 2016}
  %\revised{..}
  %\accepted{..}

  \journalyear{2016}
  \journalvolume{2016}
  \journalissue{4}

\maketitle

\input{intro}
\input{open}
\input{intersection}
\input{chaining}
\input{related}
\input{conc}
%\input{acks}

%% ###################################################################

\begin{thebibliography}{99}
%\bibitem{journal-1} A.~P.~Raposo, H.~J.~Weber, D.~E.~Alvarez--Castillo, M.~Kirchbach, Cent. Eur. J. Phys. 5, 253 (2007)
%\bibitem{journal-2} J.~Barth et al. (SAPHIR Collaboration), Phys. Lett. B 572, 127 (2003)
%\bibitem{journal-3} S.~Chekanov et al., Eur. Phys. J. C 51, 289 (2007)
%\bibitem{journal-4} K.~Malarz, Postepy Fizyki 57, 235 (2006) (in Polish)
%\bibitem{journal-5} G.~Meng, Cent. Eur. J. Phys., DOI:10.2478/s11534-007-0038-1
%\bibitem{journal-6} R.~Hegselmann, U.~Krause, Journal of Artificial Societies and Social Simulation (2006), https://urldefense.proofpoint.com/v2/url?u=http-3A__jasss.soc.surrey.ac.uk_9_3_10.html&d=AwIGaQ&c=-dg2m7zWuuDZ0MUcV7Sdqw&r=TO0xacJWWmvm7m0roFn_liAsIL2PkxELeLGL8JNJXFw&m=Ka2FvolwqKNW8vu0FjJrZZz-0NBFnF_Zu-dQp-fjTto&s=370GY1pBTDyr9NSQToGqkNR8K-Xy1z0bsX64GpcLiPk&e= 
%\bibitem{journal-7} A.~Dybala, Cent. Eur. J. Chem. (in press)
%\bibitem{journal-8} A.~Dybala, Przeglad chemiczny (in Polish, in press)
%\bibitem{book} M.~Lister, Fundamentals of Operating Systems, 3rd edition (Springer-Verlag, New York, 1984)
%\bibitem{chapter} C.~K.~Clenshaw, K.~Lord, In: B.~K.~P.~Scaife (Ed.), Studies in Numerical Analysis (Academic Press, London and New York, 1974) 95
%\bibitem{arxiv-1} M.~Majewski, K.~Malarz, arXiv:cond-mat/0609635v2 [cond-mat.stat-mech]
%\bibitem{arxiv-2} J.~A.~C.~E.~Solano, arXiv:0707.1343v1 [astro-ph]
\bibitem{sff-foci2014} A.~Segal, B.~Ford, J.~Feigenbaum, 
In: J. Crandall and V. Paxson (Eds.), $4^{th}$ Workshop on Free and 
Open Communications on the Internet, August 18, 2014, San Diego, 
USA (USENIX, Berkeley, 2014)

\bibitem{dissent} H.~Corrigan-Gibbs, B.~Ford, In: A.~D.~Keromytis and 
V.~Shmatikov (Eds.), $17^{th}$ Conference on Computer and Communications 
Security, Oct. 4-8, 2010, Chicago, USA (ACM, New York, 2010)

\bibitem{verdict} H.~Corrigan-Gibbs, D.~I.~Wolinsky, and B.~Ford, In: 
S.~King (Ed.), $22^{nd}$ Security Symposium, August 14-16, 2013, 
Washington, D.C., USA (USENIX, Berkeley, 2013)

\bibitem{snapnets} J.~Leskovec and A.~Krevl, SNAP Datasets: 
Stanford Large Network Dataset Collection, 
http://snap.stanford.edu/data

\bibitem{mobiforge} MobiForge, Global mobile statistics 2014 Part A: 
Mobile subscribers; handset market share; mobile operators,\\ 
https://mobiforge.com/research-analysis/global-mobile-\\
statistics-2014-part-a-mobile-subscribers-handset-market-\\
share-mobile-operators\#topmnos

\bibitem{krwy-pnas16} M. Kearns, A. Roth, Z. S. Wu, G. Yaroslavtsev, 
Proc.~Natl.~Acad.~Scis. 113, 913 (2016)

%\bibitem{proceedings} A.~Kaczanowski, K.~Malarz, K.~Kulakowski, In: T.~E.~Simos (Ed.), International Conference of Computational Methods in Science and Engineering, Sep. 12-16, 2003, Kastoria, Greece (World Scientific, Singapore 2003) 258
%\bibitem{thesis} A.~J.~Agutter, Ph.D. thesis, Edinburgh University (Edinburgh, UK, 1995)
%\bibitem{newspaper-1} A.~Sherwin, The Times, Jul. 13, 2007, 1
%\bibitem{newspaper-2} M.~Dzierzanowski, Wprost, Jul. 8, 2007, 18 (in Polish)
%\bibitem{patent} Philip Morris Inc., European patent application 0021165 A1, Jan. 7, 1981
%\bibitem{standard-1} ISO 2108:1992, Information and documentation --- International standard book numbering (ISBN)
%\bibitem{standard-2} ISO/TR 9544:1988, Information processing --- Computer-assisted publishing --- Vocabulary
\end{thebibliography}

\end{document}

### 2016-02-27 paper/submission.tex
corrected a typo in one of the bibitems in submission.tex

@@
 V.~Shmatikov (Eds.), $17^{th}$ Conference on Computer and Communications 
-Security, Oct. 4-8, 2010, Chicago, USA (ACM, New York, 2010)
+Security, October 4-8, 2010, Chicago, USA (ACM, New York, 2010)
 

### 2016-02-27 paper/chaining.tex
Adding no-crypto text and updated graphs.

@@
 
-%These results are important in evaluating how practical our lawful contact-chaining protocol would be it were put into practice by government agencies and telecoms.
+These results are important in evaluating how practical our lawful contact-chaining protocol would be it were put into practice by government agencies and telecoms.
 However, our data set is relatively small compared to the databases held by real telecommunications companies, and each company handles that data using different technologies.
@@
 This version of the protocol does not preserve the privacy of users.
-By comparing the performance of our lawful contact-chaining protocol with the zero-privacy contact-chaining protocol, however, we can get a sense of the ``cost'' of privacy and accountability as compared to the practice of releasing plaintext data to government surveillance.
+By comparing the performance of our lawful contact-chaining protocol with the zero-cryptography contact-chaining protocol, however, we can get a sense of the ``cost'' of privacy and accountability as compared to the practice of releasing plaintext data to government surveillance.
 
@@
 
+%Adding additional line breaks to this section will interfere with the formatting.
 \begin{figure*}[t]
-
 \centering
-
 \begin{subfigure}{.33\textwidth}
-
 \centering
-
 \includegraphics[width=0.99\textwidth]{runtime.pdf}
-
 \captionsetup{justification=centering}
-
 \caption{Protocol Runtime}
-
 \label{fig:runtime}
-
 \end{subfigure}\hfill
-
 \begin{subfigure}{.33\textwidth}
-
 \centering
-
 \includegraphics[width=0.99\textwidth]{cputime.pdf}
-
 \captionsetup{justification=centering}
-
 \caption{CPU Time}
-
 \label{fig:cputime}
-
 \end{subfigure}\hfill
-
 \begin{subfigure}{.33\textwidth}
-
 \centering
-
 \includegraphics[width=0.99\textwidth]{bandwidth.pdf}
-
 \captionsetup{justification=centering}
-
 \caption{Network Data}
-
 \label{fig:data}
-
 \end{subfigure}
-
 \caption{Performance of Lawful Contact-Chaining}
-
 \label{fig:performance}
-
 \end{figure*}
@@
 Given the context of a criminal investigation, we feel these running times are quite reasonable.
+
+The zero-cryptography version of our program ran, predictably, more quickly than the lawful privacy-preserving version.
+The total CPU time across all telecoms needed for our zero-crypto implementation never rose above ten seconds, even in the largest cases.
+This result allows us to disambiguate the cost of \emph{information retrieval} from \emph{privacy protection}.
+The linear relationship between the size of the encrypted user data set and the performance in terms of running time, CPU time, and network data usage of the protocol all remain even when we subrtract out the time to run all non-cryptgraphic parts of the protocol.
+We therefore conclude that, even given the potental database operations real telecoms would have to contend with, the cost of adding privacy-preservation to the contact-chaining protocol will remain reasonable.

### 2016-02-28 paper/intro.tex
...
fleshed out intro and biblio

@@
 
+Continuing the approach taken by Segal {\it et al.}~\cite{sff-foci2014}, we
+seek to design and implement protocols for {\it accountable surveillance}.
+We require that government surveillance be conducted according to {\it open
+processes}, as defined in Section~\ref{sec-open} below, and that the privacy
+of {\it untargeted users} be protected.  We consider the surveillance goals
+of {\it set intersection} and {\it contact chaining} and show that both can 
+be achieved in a privacy-preserving, accountable fashion.
+
+The utility of set-intersection protocols was demonstrated in the 
+High Country Bandits case~\cite{anderson13cell}.
+After obtaining cell-tower dumps -- sets of about 150,000 total users
+whose cell phones had been in the vicinity of three banks at the times
+that those banks were robbed -- the FBI intersected the sets and discovered 
+that a single phone had been used at all of the relevant times in all of the 
+relevant places.  They arrested the owner
+of that phone and were able to prove that he was one of the robbers.
+Although this FBI dragnet was effective in catching robbers, it also swept
+in the cell-phone numbers of approximately 149,999 innocent bystanders.
+Segal {\it et al.}~\cite{sff-foci2014} provide an accountable protocol for
+set intersection that preserves the privacy of innocent bystanders.  Their
+rudimentary implementation requires just under two hours on a test instance
+with 150,000 total users.  In Section~\ref{sec-intersection} below, we provide
+a more careful implementation that is faster by a factor of 10; in particular,
+it runs for approximately 10.5 minutes on the test instance of 150,000 users.
+
+In Section~\ref{sec-chaining}, we turn our attention to 
+accountable-surveillance protocols for contact chaining.
+
 At first blush, it may seem that a symposium on ``privacy-enhancing 

### 2016-02-28 paper/open.tex
fleshed out intro and biblio

@@
-\section{The Openness Principle in Lawful Surveillance}
+\section{The Openness Principle in Lawful Surveillance}\label{sec-open}
 In this section, we review the openness principle put forth by Segal 
@@
 in a democratic society:
-
 \begin{enumerate}
@@
 untargeted users' private information through the firewall must be open
-processes.  More generally, the openness principle asserts that, by using
+processes.  The targeted class contains both {\it known} users, {\it i.e.},
+those for whom the government has a name, address, phone number, email address,
+or other piece of personally identifying information, and {\it unknown} users.
+It is not, as it may seem on the surface, oxymoronic to call a user both
+``targeted'' and ``unknown,'' because ambient information may justify the
+targeting of an individual without identifying him or her in any standard sense
+of ``identify.''  For example, a government agency may obtain a ``John Doe
+warrant''~\cite{bieber-penn2002} to investigate users who were present in
+locations $L_i$ at times $T_i$, for $1\leq i\leq k$, without being able to 
+identify those users, because relevant events occurred at those locations at
+those times. Segal {\it et al.}~\cite{sff-foci2014} show how an 
+accountable-surveillance protocol can be used to obtain a large set of
+{\it encrypted} data about both targeted and untargeted users, feed it into a 
+cryptographic protocol that winnows it down to the records of users targeted by
+the John Doe warrant, and decrypt {\it only} those records.  Thus, targeted
+unknown users can be identified ({\it i.e.}, turned into targeted, known users)
+without government agencies' identifying any untargeted users whose 
+encrypted records are touched by the surveillance process.
+
+The essence of the openness principle is that, by using
 appropriate security technology, government agencies can make their 

### 2016-02-28 paper/chaining.tex
...

@@
-\section{Lawful Contact Chaining}
+\section{Lawful Contact Chaining}\label{sec-chaining}
 Contact chaining is a form of government surveillance with which it is deceptively easy to expose many innocent, untargeted users to government scrutiny.

### 2016-02-28 paper/intro.tex
finished draft of intro.tex

@@
-\section{Introduction}
+\section{Introduction}\label{sec-introduction}
 As networked devices become more available, more capable, and more ubiquitous
@@
 
-Continuing the approach taken by Segal {\it et al.}~\cite{sff-foci2014}, we
+Adopting the approach taken by Segal {\it et al.}~\cite{sff-foci2014}, we
 seek to design and implement protocols for {\it accountable surveillance}.
@@
 accountable-surveillance protocols for contact chaining.
+The goal of contact chaining is to use the topology of a {\it communication 
+graph} ({\it e.g.}, a phone-call graph, email graph, or social network) 
+in order to identify associates (or ``contacts'') of lawfully targeted users. 
+Government agencies can then investigate those associates to determine whether
+they deserve further attention.\footnote{Note that contact chaining is not
+tantamount to ``guilt by association.''  Rather, it is tantamount to
+``suspicion by association,'' which is in fact a time-honored principal in
+law enforcement.  When investigating a murder, rape, or other violent felony,
+police departments first turn their attention to the associates of the victim.
+Accountable-surveillance practices require that contacts who are suspected,
+investigated, and found {\it not} to be involved in illegal activity be 
+cleared of suspicion and that their personal information be deleted from 
+agencies' databases.} It is useful to consider both direct contacts, 
+{\it i.e.}, users who are neighbors in the communication graph, and
+extended contacts, {\it i.e.}, users who are at distance $k$ in the 
+communication graph, for an appropriate constant $k$.
+In a phone-call graph, if Alice calls Bob, 
+and Bob calls Charlie, then Alice and Bob are direct contacts (as are Bob and 
+Charlie), but Alice and Charlie are extended contacts (more precisely,
+contacts at distance 2).  Without accountability and security mechanisms to
+limit an investigation's scope, contact chaining in a mass-communication
+network can sweep in a huge number of untargeted users.
+In Section~\ref{sec-chaining}, we provide an accountable contact-chaining
+protocol that bounds the scope of the search, uses encryption to protect 
+untargeted users, and is computationally efficient (in that its time
+complexity and space complexity are both linear in the size of the output).
 

### 2016-02-28 paper/related.tex
corrected two typos

\section{Related Work}\label{sec-related}
Privacy-preserving computation has been studied extensively. An overview
of the approaches taken by the cryptographic-research community is provided by
Perry {\it et al.}~\cite{pgfw-scn2014}; an overview of of the data-mining
approach is provided by Aggarwal and Yu~\cite{ay2008}.  Kamara~\cite{kamara}
and Kroll {\it et al.}~\cite{kroll} used cryptographic protocols to 
achieve privacy and accountability in the surveillance of known targets.
Segal {\it et al.}~\cite{sff-foci2014} formulated the openness principle that
we have followed and were the first to design privacy-preserving protocols for
the surveillance of unknown targets.  Kearns {\it et al.}~\cite{krwy-pnas16}
present efficient graph-search algorithms that distinguish targeted users from
untargeted users while preserving the privacy of direct contacts of untargeted
users; unlike our privacy-preserving contact-chaining algorithms, which rely
on cryptographic techniques, their search algorithms rely on 
differential-privacy techniques.

### 2016-02-28 paper/submission.tex
fleshed out intro and biblio
corrected two typos

@@
 
+\bibitem{anderson13cell} N.~Anderson, arstechnica, August 29, 2013.
+
+\bibitem{bieber-penn2002} M.~Bieber, Univ.~Penn.~Law Review, 150, 1079 (2002)
+
 \bibitem{dissent} H.~Corrigan-Gibbs, B.~Ford, In: A.~D.~Keromytis and 
@@
 
+\bibitem{pgfw-scn2014} J. Perry, D. Gupta, J. Feigenbaum, and R. Wright,
+In: M. Abdalla and R. De Prisco (eds.), $9^{th}$ Conference on Security and 
+Cryptography for Networks, September 3-5, 2014, Amalfi, Italy (Springer,
+Berlin, 2014)
+
+\bibitem{ay2008} C.~Aggarwal and P.~Yu, In: C.~Aggarwal and P.~Yu (Eds.), 
+Privacy-Preserving Data Mining: Models and Algorithms 
+(Springer, Berlin, 2008) 11
+
+\bibitem{kamara} S.~Kamara, In: M.~Brenner and M.~Smith (eds.), 
+$2^{nd}$ Workshop on Applied Homomorphic Cryptography and Encrypted Computing, 
+March 7, 2014, Barbados, West Indies (Springer, Berlin, 2014)
+
+\bibitem{kroll} J.~Kroll, E. Felten, and D. Boneh, Secure protocols for
+accountable warrant execution, April 2, 2014,\\
+https://freedom-to-tinker.com/blog/felten/\\
+secure-protocols-for-accountable-warrant-execution/
+
 \bibitem{krwy-pnas16} M. Kearns, A. Roth, Z. S. Wu, G. Yaroslavtsev, 

### 2016-02-28 paper/intersection.tex
Enlarged intersection.tex

@@
 set-intersection protocol of~\cite{sff-foci2014}. 
-{\bf Create Subsections 3.1 and 3.2.  Add something about why this protocol
-satisfies the openness principle.}
+\subsection{Intersections and Privacy}
+
+As described in Section~\ref{sec-intro} and in~\cite{sff-foci2014}, the FBI used
+set intersection to search for phone numbers that appeared in three sets of
+cell-tower dumps. This procedure did not follow the the openness principle.
+The FBI did not distinguish between targeted and untargeted users when
+collecting the data. It only arrested the user in the intersection of the sets
+it collected, as far as we know, but as there was no established accountability
+procedure, we do not know whether the FBI retained the phone numbers of
+untargeted users collected during the search, whether it subjected any of those
+other phone numbers to additional investigation, whether it shared the data sets
+of 150,000 total users with other government agencies, \it{etc}.
+
+Segal \it{et al.}~\cite{sff-foci2014} presented a private set intersection
+protocol to address these specific concerns. We present a summary of that protocol
+in Section~\ref{sec-isectproto}. This protocol reveals \emph{only} the identities
+of users in the intersection of the sets under consideration, leaving the other,
+untargeted users' identities hidden by encryption. To provide accountability and
+oversight, the protocol requires multiple government agencies to participate. This
+provides a division of authority. No one agency can uncover users' identities
+without other agencies being able to collect records about how often intersection
+warrants are used and set restrictions on how many users the agencies can identify
+under a single warrant.
+
+The lawful contact chaining protocol we present in Section~\ref{sec-chaining} will
+produce large, encrypted sets of user identities. These sets can then be used as
+inputs into the lawful set intersection protocol, to reveal the small, targeted
+group of identities that appear in multiple sets (whether those sets come from cell
+tower dumps as in the High Country Bandits case, contact chaining, or some other
+legally obtained source of information).
+
+\subsection{Lawful Intersection Protocol}\label{sec-isectproto}
 
@@
 
-Each agency's input is its ElGamal private key and a set of this encrypted data. For each execution of the protocol, the agencies also generate temporary 
+Each agency's input is its ElGamal private key and a set of this encrypted
+data. For each execution of the protocol, the agencies also generate temporary 
 Pohlig-Hellman keys, which they securely delete after the protocol is complete. 
@@
 The agencies can then directly compare Pohlig-Hellman ciphertexts to each 
-other to determine which appear in the intersection of all three sets of data. 
+other to determine which appear in the intersection of all sets of data. 
 If the intersection is much larger than expected, any one of the agencies can 
@@
 the agencies finish the protocol by using their Pohlig-Hellman decryption keys 
-to reveal only the ciphertexts in the intersection of all three sets.
+to reveal only the ciphertexts in the intersection of all sets.
 
-\subsection{Improved Implementation of Lawful Intersection}
+\subsection{Improved Implementation of Lawful Intersection}\label{sec-isectimpl}
 
@@
 
-{\bf Add something about the argument that SFF made about their protocol's
-being fast enough.}
+In an experiment with 150,000 users - the same number of users as the FBI
+examined in the High Country Bandits case - that implementation took
+approximately two hours to run to completeion. As the authors argued an FBI
+investigation is likely to take days to lead to an arrest, even without the
+use of this privacy-preserving technology. Therefore, a two-hour running time
+may not be a major obstacle in this context.
 
-We have produced an improved implementation
-that takes advantage of parallel processing and more advanced computational 
+But because we offer a new use of the lawful intersection protocol, we
+also offer a speedier implementation of it. Our improved implementation
+takes advantage of parallel processing and more advanced computational 
 hardware, thus showing that lawful set-intersection can be performed 
-much more quickly than originally descrbied in~\cite{sff-foci2014}.
+much more quickly than originally described in~\cite{sff-foci2014}.
 

### 2016-02-28 paper/intersection.tex
Fixing bug in intersection.tex

@@
 
-As described in Section~\ref{sec-intro} and in~\cite{sff-foci2014}, the FBI used
+As described in Section~\ref{sec-introduction} and in~\cite{sff-foci2014}, the FBI used
 set intersection to search for phone numbers that appeared in three sets of
@@
 other phone numbers to additional investigation, whether it shared the data sets
-of 150,000 total users with other government agencies, \it{etc}.
+of 150,000 total users with other government agencies, \emph{etc}.
 
-Segal \it{et al.}~\cite{sff-foci2014} presented a private set intersection
+Segal \emph{et al.}~\cite{sff-foci2014} presented a private set intersection
 protocol to address these specific concerns. We present a summary of that protocol

### 2016-02-28 paper/intersection.tex
Fix graph in Sec. 3

@@
 \centering
-\includegraphics[width=0.99\columnwidth]{intersectionchart.pdf}
+\begin{tikzpicture}
+\begin{loglogaxis}[
+	title={Parallel vs. Sequential Running Time},
+	xlabel={Total Set Size [Ciphertexts]},
+	ylabel={Running Time [min]},
+	xmin=10, xmax=200000,
+	ymin=0.01, ymax=1000,
+	%xtick={10, 100, 1000, 10000, 100000},
+	%ytick={0.01, 0.1, 1, 10, 100, 1000},
+	log ticks with fixed point,
+	legend pos=north west,
+	ymajorgrids=true,
+	xmajorgrids=true,
+	grid style=dashed,
+]
+
+\addplot[
+	color=blue,
+	mark=o,
+	]
+	table [x=Items, y=Parallel, col sep=comma] {intersection.csv};
+
+\addplot[
+	color=red,
+	mark=square,
+	]
+	table [x=Items, y=Sequential, col sep=comma] {intersection.csv};
+
+\legend{Parallel, Sequential}
+\end{loglogaxis}
+\end{tikzpicture}
+\captionsetup{justification=centering}
 \caption{Comparison of Lawful Intersection Performance}

### 2016-02-28 paper/chaining.tex
Fix graph in Sec. 3
Fix graphs in sec. 4

@@
 \centering
-\begin{subfigure}{.33\textwidth}
+\begin{subfigure}{0.66\columnwidth}
 \centering
-\includegraphics[width=0.99\textwidth]{runtime.pdf}
-\captionsetup{justification=centering}
-\caption{Protocol Runtime}
+\begin{tikzpicture}[scale=0.66]
+\begin{loglogaxis}[
+	title={Protocol Runtime},
+	title style={font=\Large,},
+	xlabel={Ciphertexts in Result},
+	ylabel={Running Time [min]},
+	ylabel style={overlay, anchor=north,},
+	xmin=10, xmax=1000000,
+	ymin=0.01, ymax=100,
+	%xtick={10, 100, 1000, 10000, 100000},
+	%ytick={0.01, 0.1, 1, 10, 100, 1000},
+	log ticks with fixed point,
+	legend pos=north west,
+	ymajorgrids=true,
+	xmajorgrids=true,
+	grid style=dashed,
+	legend style={cells={anchor=west}},
+]
+\addplot[
+	color=blue,
+	mark=o,
+	only marks,
+	mark size=1pt,
+	]
+	table [x=Ciphertexts, y=RunningTime, col sep=comma] {chainingrsa.csv};	
+\addplot[
+	color=red,
+	mark=square,
+	only marks,
+	mark size=1pt,
+	]
+	table [x=Ciphertexts, y=RunningTime, col sep=comma] {chainingnocrypto.csv};
+\legend{Lawful contact-chaining, Zero-crypto}
+\end{loglogaxis}
+\end{tikzpicture}
+%\captionsetup{justification=centering}
+%\caption{Protocol Runtime}
 \label{fig:runtime}
 \end{subfigure}\hfill
-\begin{subfigure}{.33\textwidth}
+\begin{subfigure}{0.66\columnwidth}
 \centering
-\includegraphics[width=0.99\textwidth]{cputime.pdf}
-\captionsetup{justification=centering}
-\caption{CPU Time}
+\begin{tikzpicture}[scale=0.66]
+\begin{loglogaxis}[
+	title={All-Telecom CPU Time},
+	title style={font=\Large,},
+	xlabel={Ciphertexts in Result},
+	ylabel={Total CPU Time [min]},
+	ylabel style={overlay, anchor=north,},
+	xmin=10, xmax=1000000,
+	ymin=0.1, ymax=1000,
+	%xtick={10, 100, 1000, 10000, 100000},
+	%ytick={0.01, 0.1, 1, 10, 100, 1000},
+	log ticks with fixed point,
+	legend pos=north west,
+	ymajorgrids=true,
+	xmajorgrids=true,
+	grid style=dashed,
+	legend style={cells={anchor=west}},
+]
+\addplot[
+	color=blue,
+	mark=o,
+	only marks,
+	mark size=1pt,
+	]
+	table [x=Ciphertexts, y=CPUTime, col sep=comma] {chainingrsa.csv};
+\addplot[
+	color=red,
+	mark=square,
+	only marks,
+	mark size=1pt,
+	]
+	table [x=Ciphertexts, y=CPUTime, col sep=comma] {chainingnocrypto.csv};
+\legend{Lawful contact-chaining, Zero-crypto}
+\end{loglogaxis}
+\end{tikzpicture}
+%\captionsetup{justification=centering}
+%\caption{CPU Time}
 \label{fig:cputime}
 \end{subfigure}\hfill
-\begin{subfigure}{.33\textwidth}
+\begin{subfigure}{0.66\columnwidth}
 \centering
-\includegraphics[width=0.99\textwidth]{bandwidth.pdf}
-\captionsetup{justification=centering}
-\caption{Network Data}
+\begin{tikzpicture}[scale=0.66]
+\begin{loglogaxis}[
+	title={Data transferred},
+	title style={font=\Large,},
+	xlabel={Ciphertexts in Result},
+	ylabel={Data transferred [MB]},
+	ylabel style={overlay, anchor=north,},
+	xmin=10, xmax=1000000,
+	ymin=0.1, ymax=10000,
+	%xtick={10, 100, 1000, 10000, 100000},
+	%ytick={0.01, 0.1, 1, 10, 100, 1000},
+	log ticks with fixed point,
+	legend pos=north west,
+	ymajorgrids=true,
+	xmajorgrids=true,
+	grid style=dashed,
+	legend style={cells={anchor=west}},
+]
+\addplot[
+	color=blue,
+	mark=o,
+	only marks,
+	mark size=1pt,
+	]
+	table [x=Ciphertexts, y=Bytes, col sep=comma] {chainingrsa.csv};	
+\addplot[
+	color=red,
+	mark=square,
+	only marks,
+	mark size=1pt,
+	]
+	table [x=Ciphertexts, y=Bytes, col sep=comma] {chainingnocrypto.csv};
+\legend{Lawful contact-chaining, Zero-crypto}
+\end{loglogaxis}
+\end{tikzpicture}
+%\captionsetup{justification=centering}
+%\caption{Network Data}
 \label{fig:data}
 \end{subfigure}
+\captionsetup{justification=centering}
 \caption{Performance of Lawful Contact-Chaining}

### 2016-02-28 paper/chaining.tex
Make titles of 4.1.4 and 4.1.5 correspond
s/social graph/communication graph/g

@@
 If Alice calls Bob, and Bob calls Charlie, then Alice and Bob are direct contacts (as are Bob and Charlie), but Alice and Charlie are extended contacts.
-We may also say that Alice and Charlie are at a distance of 2 in the social graph (since the shortest number of phone calls that connect Alice to Charlie is 2).
+We may also say that Alice and Charlie are at a distance of 2 in the communication graph (since the shortest number of phone calls that connect Alice to Charlie is 2).
 
@@
 This protocol permits multiple government agencies working together to provide oversight and accountability, as discussed in \cite{sff-foci2014}.
-Using this protocol, the agencies can retrieve an encrypted set of user data from multiple telecoms, each of which holds only part of a larger social graph.
+Using this protocol, the agencies can retrieve an encrypted set of user data from multiple telecoms, each of which holds only part of a larger communication graph.
 This encrypted set contains the identities of users within a certain distance of a target, but the identities cannot be decrypted unless the agencies cooperate.
@@
 
-\subsubsection{First Lawful Contact-Chaining Protocol}
+\subsubsection{Ownership-Revealing Lawful Contact-Chaining Protocol}
 
@@
 
-The protocol below amounts to a distributed breadth-first search of the social graph run by the agencies making queries of the telecoms.
+The protocol below amounts to a distributed breadth-first search of the communication graph run by the agencies making queries of the telecoms.
 However, all messages the agencies receive from the telecoms will be encrypted.

### 2016-02-28 paper/chaining.tex
Minor Corrections

@@
 There are two types of parties in this protocol: Telecommunications companies (telecoms) and government agencies interested in performing lawful contact-chaining (agencies).
-The protocol is a function of all parties' data.
+The protocol computes a function of all parties' data.
 
@@
 
-In addition to the public knowledge which telecom serves which phone number, the agencies must each hold a copy of a \emph{warrant} in order to perform this protocol.
+The agencies must each hold a copy of a \emph{warrant} in order to perform this protocol.
 A warrant is a triplet ($x$, $k$, $d$).
 $x$ is a target phone number.
+We assume, since $x$ belongs to a user targeted by the agencies, that they also know which telecom serves $x$.
 $k$ is a (small) distance from $x$, the distance at which the agencies wish to consider chained contacts.
@@
 If a phone number has more than $d$ contacts, then the agencies do not consider paths to other users through that phone number in their search.
-The agencies disregarded for the initial target $x$, however.
+The agencies disregard $d$ for the initial target $x$, however.
 

### 2016-02-28 paper/chaining.tex
More fixes to Sec. 4

@@
 
-\label{sec:proto}
+\label{sec-proto}
 
 %This is a candidate protocol for privacy-preserving contact chaining.
-We discuss the desired inputs, outputs, and security assumptions below, and then present two versions of the protocol in sections \ref{sec:proto1} and \ref{sec:proto2}.
+We discuss the desired inputs, outputs, and security assumptions below, and then present two versions of the protocol in sections \ref{sec-proto1} and \ref{sec-proto2}.
 
@@
 Now everyone else who has recently called that pizza place is at a distance 2 to $x$.
+
+We can assume that business phone numbers have many more contacts than personal phone numbers do.
+In most cases, knowing that two individuals have contacted the same business phone number does not indicate that those individuals have a personal relationship.
 Therefore, the warrant also includes $d$, an upper bound on the degree of users the agencies are willing to ``chain'' through.
@@
 The agencies disregard $d$ for the initial target $x$, however.
+The high-degree users themselves will also be present in the agencies' outputs.
 
-We specify the protocol in full in sections~\ref{sec:proto1} and \ref{sec:proto2}.
+This provides a reasonable limit to the scope of the investigation and hides what are very likely to be untargeted users from the government.
+In the uncommon scenario where a business number with many contacts also functions as a front or hub for a criminal organization to be revealed, the government is still able to conduct further investigation on it, perhaps even beginning a new contact-chaining search with that number as the initial target.
+
+We specify the protocol in full in sections~\ref{sec-proto1} and \ref{sec-proto2}.
 
@@
 
-In section \ref{sec:proto2}, we will present a second version of the protocol in which the agency \emph{does not} learn which telecom serves which encrypted phone number.
+In section \ref{sec-proto2}, we will present a second version of the protocol in which the agency \emph{does not} learn which telecom serves which encrypted phone number.
 
@@
 
-\label{sec:proto1}
+\label{sec-proto1}
 
@@
 
-\label{sec:proto2}
+\label{sec-proto2}
 
@@
 Now we can present the following modified protocol.
-This protocol uses the same data structures as in section~\ref{sec:proto1}, except that $\mathbf{Q}$ now contains pairs $(\Enc_{T(a)}(a), j)$ for unexplored vertices $a$ (omitting the identity of $T(a)$.
+This protocol uses the same data structures as in section~\ref{sec-proto1}, except that $\mathbf{Q}$ now contains pairs $(\Enc_{T(a)}(a), j)$ for unexplored vertices $a$ (omitting the identity of $T(a)$.
 
@@
 
-The protocol replaces each query in the protocol of section~\ref{sec:proto1} with broadcast of the telecom ciphertext to all telecoms, and replaces each response with a round of the anonymity protocol.
+The protocol replaces each query in the protocol of section~\ref{sec-proto1} with broadcast of the telecom ciphertext to all telecoms, and replaces each response with a round of the anonymity protocol.
 This allows the telecom that owns each phone number to respond with appropriate information about the phone number, but shields the telecom's identity from the agencies (and incidentally from other telecoms).
@@
 
-If all parties behave in an honest or honest-but-curious way in following to the protocols above, then the agencies' outputs will be $\mathbf{C}$.
+The agencies' outputs from the protocols in sections~\ref{sec-proto1} and \ref{sec-proto2} will be $\mathbf{C}$.
 $\mathbf{C}$ will contain agency ciphertexts of all phone numbers at most $k$ phone calls away from $x$, considering only vertices of degree at most $d$.
@@
 
-The protocol of section~\ref{sec:proto1} allows the agencies to learn which telecoms owns which ciphertexts in $\mathbf{C}$.
+The protocol of section~\ref{sec-proto1} allows the agencies to learn which telecoms owns which ciphertexts in $\mathbf{C}$.
 This may be a security concern, since some telecoms are relatively small, specialized, or localized to a particular country or region.
@@
 Our revised protocol mitigates this concern.
-Assuming that the anonymity protocol used in section~\ref{sec:proto2} does not allow its participants to learn who sends each message, then the revised protocol does not leak ciphertext ownership information.
+Assuming that the anonymity protocol used in section~\ref{sec-proto2} does not allow its participants to learn who sends each message, then the revised protocol does not leak ciphertext ownership information.
 
@@
 
-We may point out nevertheless that a modification of our protocol from \ref{sec:proto1} could allow the agencies to hide from the telecoms which of their clients is being surveilled.
+We may point out nevertheless that a modification of our protocol from \ref{sec-proto1} could allow the agencies to hide from the telecoms which of their clients is being surveilled.
 The telecoms would need to precompute agency ciphertexts for all of their client numbers, and telecom ciphertexts for all of their clients' contacts.
@@
 
-We implemented the privacy-preserving contact chaining search protocol of~\ref{sec:proto1} in Java and tested the implementation's running time, CPU time used, and data sent over the network.
+We implemented the privacy-preserving contact chaining search protocol of~\ref{sec-proto1} in Java and tested the implementation's running time, CPU time used, and data sent over the network.
 Below, we describe our implementation and its experimental setup, and then summarize our results.
@@
 
-%Adding additional line breaks to this section will interfere with the formatting.
+%NOTE: Adding blank lines to this environment will interfere with the formatting.
 \begin{figure*}[t]

### 2016-02-29 paper/chaining.tex
small edits plus corrected description of Kearns's results

@@
 If Alice calls Bob, and Bob calls Charlie, then Alice and Bob are direct contacts (as are Bob and Charlie), but Alice and Charlie are extended contacts.
-We may also say that Alice and Charlie are at a distance of 2 in the communication graph (since the shortest number of phone calls that connect Alice to Charlie is 2).
+We may also say that Alice and Charlie are at distance 2 in the communication graph (because the smallest number of phone calls that connect Alice to Charlie is 2).
 
@@
 %This is a candidate protocol for privacy-preserving contact chaining.
-We discuss the desired inputs, outputs, and security assumptions below, and then present two versions of the protocol in sections \ref{sec-proto1} and \ref{sec-proto2}.
+We discuss the desired inputs, outputs, and security assumptions below, and then present two versions of the protocol in Sections \ref{sec-proto1} and \ref{sec-proto2}.
 
@@
 
-We specify the protocol in full in sections~\ref{sec-proto1} and \ref{sec-proto2}.
+We specify the protocol in full in Sections~\ref{sec-proto1} and \ref{sec-proto2}.
 
@@
 
-The agencies' outputs from the protocols in sections~\ref{sec-proto1} and \ref{sec-proto2} will be $\mathbf{C}$.
+The agencies' outputs from the protocols in Sections~\ref{sec-proto1} and \ref{sec-proto2} will be $\mathbf{C}$.
 $\mathbf{C}$ will contain agency ciphertexts of all phone numbers at most $k$ phone calls away from $x$, considering only vertices of degree at most $d$.

### 2016-02-29 paper/intro.tex
small edits plus corrected description of Kearns's results

@@
 untargeted users, and is computationally efficient (in that its time
-complexity and space complexity are both linear in the size of the output).
+complexity and communication complexity are both linear in the size of the 
+output).
 

### 2016-02-29 paper/related.tex
small edits plus corrected description of Kearns's results

@@
 Perry {\it et al.}~\cite{pgfw-scn2014}; an overview of of the data-mining
-approach is provided by Aggarwal and Yu~\cite{ay2008}.  Kamara~\cite{kamara}
+approach is provided by Aggarwal and Yu~\cite{ay2008}.
+
+Kamara~\cite{kamara}
 and Kroll {\it et al.}~\cite{kroll} used cryptographic protocols to 
@@
 we have followed and were the first to design privacy-preserving protocols for
-the surveillance of unknown targets.  Kearns {\it et al.}~\cite{krwy-pnas16}
-present efficient graph-search algorithms that distinguish targeted users from
-untargeted users while preserving the privacy of direct contacts of untargeted
-users; unlike our privacy-preserving contact-chaining algorithms, which rely
-on cryptographic techniques, their search algorithms rely on 
+the surveillance of unknown targets.
+
+Kearns {\it et al.}~\cite{krwy-pnas16} present efficient graph-search 
+algorithms that distinguish targeted users from untargeted users; for each 
+untargeted user $u$, the set of direct contacts of $u$ remains private.
+Unlike our privacy-preserving contact-chaining algorithms, which rely
+on cryptographic techniques, their graph-search algorithms rely on 
 differential-privacy techniques.

### 2016-02-29 paper/submission.tex
Fix graph in Sec. 3
Attempt to fix compile error
small edits plus corrected description of Kearns's results

@@
 \documentclass[USenglish,oneside,twocolumn]{article}
-
+\usepackage{etex}
 \usepackage[utf8]{inputenc}%(only for the pdftex engine)
@@
 \usepackage{subcaption}
+\usepackage{pgfplots}
 
@@
 
-\bibitem{verdict} H.~Corrigan-Gibbs, D.~I.~Wolinsky, and B.~Ford, In: 
+\bibitem{verdict} H.~Corrigan-Gibbs, D.~I.~Wolinsky, B.~Ford, In: 
 S.~King (Ed.), $22^{nd}$ Security Symposium, August 14-16, 2013, 
@@
 
-\bibitem{snapnets} J.~Leskovec and A.~Krevl, SNAP Datasets: 
+\bibitem{snapnets} J.~Leskovec, A.~Krevl, SNAP Datasets: 
 Stanford Large Network Dataset Collection, 
@@
 
-\bibitem{pgfw-scn2014} J. Perry, D. Gupta, J. Feigenbaum, and R. Wright,
+\bibitem{pgfw-scn2014} J. Perry, D. Gupta, J. Feigenbaum, R. Wright,
 In: M. Abdalla and R. De Prisco (eds.), $9^{th}$ Conference on Security and 
@@
 
-\bibitem{ay2008} C.~Aggarwal and P.~Yu, In: C.~Aggarwal and P.~Yu (Eds.), 
+\bibitem{ay2008} C.~Aggarwal, P.~Yu, In: C.~Aggarwal and P.~Yu (Eds.), 
 Privacy-Preserving Data Mining: Models and Algorithms 
@@
 
-\bibitem{kroll} J.~Kroll, E. Felten, and D. Boneh, Secure protocols for
+\bibitem{kroll} J.~Kroll, E. Felten, D. Boneh, Secure protocols for
 accountable warrant execution, April 2, 2014,\\

### 2016-02-29 paper/chaining.tex
Honest but curious, clarify "call" terminology

@@
 This is a large and unnecessary intrusion of privacy.
-These untargeted users may nevertheless face unwarranted government scrutiny, intrusive investigation, or a risk that their sensitive phone histories may be leaked accidentally.
+These untargeted users may nevertheless face unwarranted government scrutiny, intrusive investigation, or a risk that their sensitive communications histories may be leaked accidentally.
 
@@
 This protocol permits multiple government agencies working together to provide oversight and accountability, as discussed in \cite{sff-foci2014}.
+Our protocol focuses on the case in which the government seeks information from multiple telecommunications providers about the communication graph formed by phone calls and text messages.
 Using this protocol, the agencies can retrieve an encrypted set of user data from multiple telecoms, each of which holds only part of a larger communication graph.
@@
 Importantly, while any set may contain encrypted data about many untargeted users, very few users will appear in \emph{all} the sets, and those few users will be suitable targets for further lawful investigation.
+
+The same principles of oversight and accountability provided by multiple government agencies can apply to contact chaining searches in other types of communication graphs, such as the social network graph of Twitter or Facebook.
+These cases do not require our protocol, however, since if one provider knows the entire communication graph, it can compute the output of the protocol without any interactivity needed.
 
@@
 
-The telecoms jointly hold an undirected contact graph $G=(V,E)$.
+The telecoms jointly hold an undirected communication graph $G=(V,E)$.
 Each telecom knows only a subset of the edges $E$.
@@
 
+Our protocol preserves the privacy of untargeted users as long as all parties execute the protocol in an honest-but-curious manner, all of the government agencies do not collude together, and no telecoms collude with government agencies.
+A colluding group containing all agencies would be equivalent to the current situation n which the government does not provide meaningful accountability of its own surveillance activities; what we propose is a replacement for this situation, but it does require the government to follow its own laws, once set.
+A telecom colluding with a government agency would amount to sending that agency free information about its users, or submitting incorrect information to the protocol.
+But telecoms have no business purpose to deviate from the protocol and risk legal action.
+In practice, existing legal tools allow law enforcement agencies to gather information about the phone history of a suspect with a valid warrant, but such information cannot generally be used for further contact chaining.
+
 \subsubsection{Desired Outputs and Security Properties}
 
-The desired output of the protocol is for the agencies to learn an encryption of the set of phone numbers within distance $k$ of the targeted phone $x$ in the call graph.
+The desired output of the protocol is for the agencies to learn an encryption of the set of phone numbers within distance $k$ of the targeted phone $x$ in the communication graph.
 The set should exclude numbers for which the only paths from $x$ use an intermediate vertex of degree greater than $d$.
@@
 
-We assume that all telecoms honestly follow the protocol and submit accurate information about the phone numbers they serve and the records they keep.
-We assume they send no ciphertexts to the agencies except when called for in the protocol.
-In practice, existing legal tools allow law enforcement agencies to gather information about the phone call history of a suspect with a valid warrant, but such information cannot generally be used for further contact chaining.
-
 Below, we present two versions of our protocol.
@@
 
-As long as all parties honestly follow the protocol, the agencies collectively learn \emph{no} information about the edge set $E$ except what is implied by the output.
-Furthermore, as long as at least one agency follows the protocol honestly and does not collude with the others, the remaining agencies cannot learn any of the phone numbers that appear in encrypted form in the output (unless implied by the size of the encrypted output and the leaked service information), nor can the colluding agencies cause a phone number not within distance $k$ of target $x$ to appear in the output, even in encrypted form.
-Telecoms have the ability to send additional information about their users to agencies or other telecoms at any time, but we assume they will not wish to do so, since they have a business interest to protect user information and comply with the law.
-We assume that all telecoms follow the protocol honestly.
+As long as our security assumptions for this protocol hold, the agencies collectively learn \emph{no} information about the edge set $E$ except what is implied by the output.
+Furthermore, the agencies cannot learn any of the phone numbers that appear in encrypted form in the output (unless implied by the size of the encrypted output and the leaked service information), nor can agencies cause a phone number not within distance $k$ of target $x$ to appear in the output, even in encrypted form.
 

### 2016-02-29 paper/chaining.tex
Resolving merge conflict

@@
 Therefore, we propose a \emph{lawful contact chaining protocol}.
-This protocol permits multiple government agencies working together to provide oversight and accountability, as discussed in \cite{sff-foci2014}.
+This protocol permits multiple government agencies working together to provide oversight and accountability, as advocated in \cite{sff-foci2014}.
 Our protocol focuses on the case in which the government seeks information from multiple telecommunications providers about the communication graph formed by phone calls and text messages.
@@
 
-The desired output of the protocol is for the agencies to learn an encryption of the set of phone numbers within distance $k$ of the targeted phone $x$ in the communication graph.
-The set should exclude numbers for which the only paths from $x$ use an intermediate vertex of degree greater than $d$.
+The goal of the protocol is for the agencies to obtain a set of ciphertexts, each of which is the encryption of a phone number $v$ such that the distance in the communication graph from $v$ to the targeted phone number $x$ is at most $k$.
+The set should not contain encryptions of numbers $v$ such that each path from $x$ to $v$ of length at most $k$ contains an intermediate vertex of degree greater than $d$.
+Here the ``intermediate'' vertices in a path are all vertices except the endpoints $x$ and $v$.
 
@@
 For the sake of efficiency, it is worth noting that the inner loop can be executed many times in parallel, up to the point of completely emptying $\mathbf{Q}$ at the beginning of the loop.
-Many messages to the same telecom can also be batched and sent together, reducing the number of signing and verifying operations to depend only on $k$ and not on the size of the input or output.
+Many messages to the same telecom can also be batched and sent together, thereby reducing the number of signing and verifying operations so that they depend only on $k$ and not on the size of the input or output.
 
@@
 
-An anonymity protocol is run between a number of parties, some of which have a message to send.
-At the end of the protocol, all parties must learn all messages sent, but no party other than the sender of any given message learns which party sent that message.
-Dissent~\cite{dissent} and Verdict~\cite{verdict} both satisfy our requirements, although they are more powerful than we need here, since we assume all telecoms are honest-but-curious.
+An anonymity protocol is run by a number of parties, some of which have messages to send.
+At the end of the protocol, all parties must learn all messages sent, but no party other than the sender of any given message can learn which party sent that message.
+Dissent~\cite{dissent} and Verdict~\cite{verdict} both satisfy our requirements; they are more powerful than we need, however, because we assume all telecoms are honest-but-curious.
 

### 2016-02-29 paper/conc.tex
Adding conc.tex

\section{Open Problems and Future Work}\label{sec-future}
Segal {\it et al.} noted in \cite[Section 6.1]{sff-foci2014} that
set intersection is but one type of computation that can be of use
to law-enforcement and intelligence agencies.  They observed that it 
would be interesting to identify other such computational problems 
and to devise accountable, privacy-preserving protocols to solve them.  
The work in this paper on contact chaining represents progress in that
direction.

Another problem of potential interest is the retrieval of
targeted users' postings on Facebook and other social networks, including 
those that are shared only with a small subset of the targeted user's 
``friends.'' Accountable surveillance of social-network postings may present 
novel protocol-design challenges, because it deals with one-to-many 
communication, whereas previous work in the area dealt with pairwise 
communication.

For contact chaining, it may be possible to speed up our protocols by using
elliptic-curve cryptography instead of RSA.  It may also be interesting to 
generalize the differential-privacy approach of Kearns {\it et 
al.}~\cite{krwy-pnas16} so that it applies to indirect contacts as well as
direct contacts.

Finally, the Openness Principle put forth in \cite{sff-foci2014} is but one step
toward a full understanding of how democratic processes and the rule of law
can be carried into the digital world.  Further investigation, much of it
interdisciplinary, is needed.

### 2016-02-29 paper/intersection.tex
s/dumps/records/

@@
 set intersection to search for phone numbers that appeared in three sets of
-cell-tower dumps. This procedure did not follow the the openness principle.
+cell-tower records. This procedure did not follow the the openness principle.
 The FBI did not distinguish between targeted and untargeted users when

### 2016-02-29 paper/intro.tex
Tiny changes to abstract and intro

@@
 to collect, to be held accountable to the citizens they serve, and to respect 
-privacy of innocent users.
+the privacy of innocent users.

### 2016-02-29 paper/submission.tex
Tiny changes to abstract and intro

@@
 {As demonstrated, {\it e.g.}, by Snowden's revelation of controversial NSA 
-activity and by Apple's refusal to obey a Justice Department's order to break 
+activity and by Apple's refusal to obey a Justice Department order to break 
 an iPhone security mechanism, the question of how government agencies can

### 2016-02-29 paper/chaining.tex
Fixes

@@
 \section{Lawful Contact Chaining}\label{sec-chaining}
-Contact chaining is a form of government surveillance with which it is deceptively easy to expose many innocent, untargeted users to government scrutiny.
+Contact chaining~\cite{techdirt} is a form of government surveillance with which it is deceptively easy to expose many innocent, untargeted users to government scrutiny.
 The goal of contact chaining is to use information about social connections between identities, such as records of phone calls between one number and another, to identify members of a criminal organization or terrorist group.
@@
 	%ytick={0.01, 0.1, 1, 10, 100, 1000},
-	log ticks with fixed point,
+	%log ticks with fixed point,
 	legend pos=north west,

### 2016-02-29 paper/intersection.tex
Fixes

@@
 Segal \emph{et al.}~\cite{sff-foci2014} presented a private set intersection
-protocol to address these specific concerns. We present a summary of that protocol
+protocol, based on the ElGamal~\cite{elgamal} and Pohlig-Hellman~\cite{pohlighellman}
+cryptosystems, to address these specific concerns. We present a summary of that protocol
 in Section~\ref{sec-isectproto}. This protocol reveals \emph{only} the identities
@@
 	%ytick={0.01, 0.1, 1, 10, 100, 1000},
-	log ticks with fixed point,
 	legend pos=north west,
@@
 
-\legend{Parallel, Sequential}
+\legend{New prototype (8 threads), Old prototype (1 thread)}
 \end{loglogaxis}

### 2016-02-29 paper/submission.tex
Fixes

@@
 
+\bibitem{elgamal} T.~ElGamal, IEEE Transactions on Information Theory, IT-31 No. 4 (1985)
+
+\bibitem{pohlighellman} S.~Pohlig, M.~Hellman, IEEE Transactions on Information Theory, IT-24 No. 1 (1978)
+
+\bibitem{techdirt} T.~Cushing, techdirt.com, Jul.
+3rd, 2014, \url{https://www.techdirt.com/articles/20140629/16130227727/nsa-appears-to-be-chaining-calls-using-phone-numbers-one-hop-out-as-new-originating-selectors.shtml}
+
 %\bibitem{proceedings} A.~Kaczanowski, K.~Malarz, K.~Kulakowski, In: T.~E.~Simos (Ed.), International Conference of Computational Methods in Science and Engineering, Sep.

### 2016-02-29 paper/chaining.tex
Graph changes

@@
 	ylabel={Running Time [min]},
-	ylabel style={overlay, anchor=north,},
+	ylabel style={overlay},
+	ticklabel style = {font=\large},
 	xmin=10, xmax=1000000,
@@
 	only marks,
-	mark size=1pt,
+	mark size=1.5pt,
 	]
@@
 	ylabel style={overlay, anchor=north,},
+	ticklabel style = {font=\large},
 	xmin=10, xmax=1000000,

### 2016-02-29 paper/chaining.tex
s/Segal et al./Bandits/g

@@
 To compare these times to some of our acutal experiments, we found that a search that returned 937 ciphertexts took 6.86 seconds to run, and a search that returned 27,338 ciphertexts took 109.55 seconds to run.
-To provide another point of comparison, \cite{sff-foci2014} referred to the ``High Country Bandits'' case, in which the FBI performed an intersection of 150,000 phone number to help solve a series of bank robberies.
+To provide another point of comparison, Bandits~\cite{sff-foci2014} refers to the ``High Country Bandits'' case, in which the FBI performed an intersection of 150,000 phone number to help solve a series of bank robberies.
 In one of our experiments with lawful contact chaining, we find that a similarly sized data set of 149,535 ciphertexts took 625.08 seconds - 10.4 minutes - to compile with our protocol.

### 2016-02-29 paper/conc.tex
s/Segal et al./Bandits/g

@@
 \section{Open Problems and Future Work}\label{sec-future}
-Segal {\it et al.} noted in \cite[Section 6.1]{sff-foci2014} that
+Bandits noted in \cite[Section 6.1]{sff-foci2014} that
 set intersection is but one type of computation that can be of use

### 2016-02-29 paper/intersection.tex
s/Segal et al./Bandits/g

@@
 
-Segal \emph{et al.}~\cite{sff-foci2014} presented a private set intersection
+Bandits~\cite{sff-foci2014} presented a private set intersection
 protocol, based on the ElGamal~\cite{elgamal} and Pohlig-Hellman~\cite{pohlighellman}

### 2016-02-29 paper/intro.tex
s/Segal et al./Bandits/g

@@
 
-Adopting the approach taken by Segal {\it et al.}~\cite{sff-foci2014}, we
+Adopting the approach taken by Bandits~\cite{sff-foci2014}\footnote{For the
+purpose of anonymization, we present an anonymized version of this manuscript and
+refer to the authors throughout as ``Bandits''.}, we
 seek to design and implement protocols for {\it accountable surveillance}.
@@
 in the cell-phone numbers of approximately 149,999 innocent bystanders.
-Segal {\it et al.}~\cite{sff-foci2014} provide an accountable protocol for
+Bandits~\cite{sff-foci2014} provide an accountable protocol for
 set intersection that preserves the privacy of innocent bystanders.  Their

### 2016-02-29 paper/open.tex
s/Segal et al./Bandits/g

@@
 \section{The Openness Principle in Lawful Surveillance}\label{sec-open}
-In this section, we review the openness principle put forth by Segal 
-{\it et al.}~\cite{sff-foci2014}.  Readers familiar with \cite{sff-foci2014} 
+In this section, we review the openness principle put forth by
+Bandits~\cite{sff-foci2014}.  Readers familiar with \cite{sff-foci2014} 
 may skip to the next section.
@@
 
-More precisely, Segal {\it et al.}~\cite{sff-foci2014} draw a distinction 
+More precisely, Bandits~\cite{sff-foci2014} draw a distinction 
 between two classes of communication-system users.  {\it Targeted users} are 
@@
 All others are {\it untargeted users}; they are the vast majority of all 
-users of a general-purpose, mass-communication system.  Segal {\it et 
-al.}~\cite{sff-foci2014} posit that the
-following {\it Openness Principle} should govern all surveillance activity
-in a democratic society:
+users of a general-purpose, mass-communication system. Bandits~\cite{sff-foci2014}
+posit that the following {\it Openness Principle} should govern all surveillance
+activity in a democratic society:
 \begin{enumerate}
@@
 \end{enumerate}
-Segal {\it et al.} interpret this principle as a requirement that an open
+Bandits interpret this principle as a requirement that an open
 ``privacy firewall'' be placed between government agencies and citizens'
@@
 identify those users, because relevant events occurred at those locations at
-those times. Segal {\it et al.}~\cite{sff-foci2014} show how an 
+those times. Bandits~\cite{sff-foci2014} show how an 
 accountable-surveillance protocol can be used to obtain a large set of

### 2016-02-29 paper/related.tex
s/Segal et al./Bandits/g

@@
 achieve privacy and accountability in the surveillance of known targets.
-Segal {\it et al.}~\cite{sff-foci2014} formulated the openness principle that
+Bandits~\cite{sff-foci2014} formulated the openness principle that
 we have followed and were the first to design privacy-preserving protocols for

### 2016-02-29 paper/submission.tex
s/Segal et al./Bandits/g

@@
 %\bibitem{arxiv-2} J.~A.~C.~E.~Solano, arXiv:0707.1343v1 [astro-ph]
-\bibitem{sff-foci2014} A.~Segal, B.~Ford, J.~Feigenbaum, 
-In: J. Crandall and V. Paxson (Eds.), $4^{th}$ Workshop on Free and 
-Open Communications on the Internet, August 18, 2014, San Diego, 
-USA (USENIX, Berkeley, 2014)
+%\bibitem{sff-foci2014} A.~Segal, B.~Ford, J.~Feigenbaum, 
+%In: J. Crandall and V. Paxson (Eds.), $4^{th}$ Workshop on Free and 
+%Open Communications on the Internet, August 18, 2014, San Diego, 
+%USA (USENIX, Berkeley, 2014)
+
+\bibitem{sff-foci2014} Bandits, Catching Bandits and Only Bandits:
+Privacy-Preserving Intersection Warrants for Lawful Surveillance,
+\url{https://drive.google.com/file/d/0BwK1bcoczINtbUhPaFI0Mk1DVk0/view}
+(2016)
 

### 2016-02-29 paper/submission.tex
Introduction edits

@@
   \begin{abstract}
-{As demonstrated, {\it e.g.}, by Snowden's revelation of controversial NSA 
-activity and by Apple's refusal to obey a Justice Department order to break 
-an iPhone security mechanism, the question of how government agencies can
+{The question of how government agencies can
 acquire actionable, useful information about legitimate but unknown targets 
@@
 protocols for two operations that law-enforcement and intelligence agencies
-have used effectively: {\it set intersection} and {\it contact chaining}.}
+have used effectively: {\it set intersection} and {\it contact chaining}.
+Experiments with our protocols suggest
+that privacy-preserving contact chaining can perform
+a 3-hop privacy-preserving graph traversal producing 27,000 ciphertexts
+in under two minutes.
+These ciphertexts are usable in turn via private set
+intersection to pinpoint potential unknown targets within a body of 150,000
+total ciphertexts within 10 minutes,
+without exposing personal information about non-targets.
+}
   \end{abstract}

### 2016-02-29 paper/intro.tex
Intro edits

@@
 information in their pursuit of criminals and terrorists.  For example, 
-both the heated (and still unresolved) discussion about the Snowden 
-revelations that started in 2013 and the ongoing dispute between Apple and 
-the US Justice Department are understood by many people
-as examples of an unpleasant, stark choice: Citizens can either have
-secure devices and control over their personal information, or they can have
+the heated (and still unresolved) discussion about the Snowden 
+revelations that started in 2013 is understood by many people
+as an example of an unpleasant, stark choice: Citizens can either have
+control over their personal information, or they can have
 law-enforcement and intelligence agencies with the tools that they need to
@@
 
-Adopting the approach taken by Bandits~\cite{sff-foci2014}\footnote{For the
+We draw a distinction between law enforcment access to
+third-party records held by businesses such as telephone companies,
+and encrypted information stored on an individual's personal devices:
+our work focuses on the former, not the latter.
+In particular, we believe that lawful searches of third-party records
+can be made much more security- and privacy-preserving than they currently are
+without compromising law enforcement search capabilities.
+We are {\em not} suggesting support for ``key escrowed'' encryption
+or general backdoors in personal devices,
+as is the topic of the ongoing conflict between the FBI and Apple.
+
+Adopting the approach to third-party records search
+taken by Bandits~\cite{sff-foci2014}\footnote{For the
 purpose of anonymization, we present an anonymized version of this manuscript and

### 2016-02-29 paper/intro.tex
Refine footnote 1

@@
 Adopting the approach to third-party records search
-taken by Bandits~\cite{sff-foci2014}\footnote{For the
-purpose of anonymization, we present an anonymized version of this manuscript and
-refer to the authors throughout as ``Bandits''.}, we
+taken by Bandits~\cite{sff-foci2014}\footnote{Throughout this submission, we
+cite an anonymized version of an existing paper on accountable surveillance
+and use the pseudonym ``Bandits'' instead of the names of the authors.}, we
 seek to design and implement protocols for {\it accountable surveillance}.

### 2016-02-29 paper/conc.tex
Added future work idea

@@
 For contact chaining, it may be possible to speed up our protocols by using
-elliptic-curve cryptography instead of RSA.  It may also be interesting to 
+elliptic-curve cryptography instead of RSA. Additionally, our assumption that
+all parties behave in an honest-but-curious manner might be weakened. By using
+standard zero-knowledge proof techniques, it might be possible to create a version
+of the protocols in Section~\ref{sec-chaining} which are resistant even to, for
+example, a rogue agent maliciously modifying telecom-supplied data to falsely
+incriminate a victim. It may also be interesting to 
 generalize the differential-privacy approach of Kearns {\it et 

### 2016-02-29 paper/conc.tex
changes to latest version of paper

--- 2016-02-29 paper/conc.tex
@@
 For contact chaining, it may be possible to speed up our protocols by using
-elliptic-curve cryptography instead of RSA.  It may also be interesting to 
+elliptic-curve cryptography instead of RSA. Additionally, our assumption that
+all parties behave in an honest-but-curious manner might be weakened. By using
+standard zero-knowledge proof techniques, it might be possible to create versions
+of the protocols in Section~\ref{sec-chaining} that are secure against, for
+example, a rogue agent's maliciously modifying telecom-supplied data in order
+to falsely incriminate a victim. It may also be interesting to 
 generalize the differential-privacy approach of Kearns {\it et 

### 2016-02-29 paper/intro.tex
changes to latest version of paper

@@
 
-We draw a distinction between law enforcment access to
-third-party records held by businesses such as telephone companies,
-and encrypted information stored on an individual's personal devices:
+We draw a distinction between law-enforcement access to
+third-party records held by businesses such as telephone companies
+and encrypted information stored on an individual's personal devices;
 our work focuses on the former, not the latter.
@@
 can be made much more security- and privacy-preserving than they currently are
-without compromising law enforcement search capabilities.
+without compromising law-enforcement search capabilities.
 We are {\em not} suggesting support for ``key escrowed'' encryption
@@
 of {\it untargeted users} be protected.  We consider the surveillance goals
-of {\it set intersection} and {\it contact chaining} and show that both can 
+of {\it set intersection} and {\it contact chaining}~\cite{techdirt} and show that both can 
 be achieved in a privacy-preserving, accountable fashion.

### 2016-02-29 paper/submission.tex
changes to latest version of paper

@@
 in under two minutes.
-These ciphertexts are usable in turn via private set
+These ciphertexts are usable in turn via privacy-preserving set
 intersection to pinpoint potential unknown targets within a body of 150,000
@@
 %\bibitem{arxiv-2} J.~A.~C.~E.~Solano, arXiv:0707.1343v1 [astro-ph]
+
 %\bibitem{sff-foci2014} A.~Segal, B.~Ford, J.~Feigenbaum, 
@@
 
+\vskip 2\baselineskip %needed to compile correctly
+
 \bibitem{sff-foci2014} Bandits, Catching Bandits and Only Bandits:
 Privacy-Preserving Intersection Warrants for Lawful Surveillance,
-\url{https://drive.google.com/file/d/0BwK1bcoczINtbUhPaFI0Mk1DVk0/view}
-(2016)
+February 2016 \url{https://drive.google.com/file/d/0BwK1bcoczINtbUhPaFI0Mk1DVk0/view}
+
+\bibitem{techdirt} T.~Cushing, techdirt.com, Jul.
+3rd, 2014, \url{https://www.techdirt.com/articles/20140629/16130227727/nsa-appears-to-be-chaining-calls-using-phone-numbers-one-hop-out-as-new-originating-selectors.shtml}
 
@@
 
-\bibitem{techdirt} T.~Cushing, techdirt.com, Jul.
-3rd, 2014, \url{https://www.techdirt.com/articles/20140629/16130227727/nsa-appears-to-be-chaining-calls-using-phone-numbers-one-hop-out-as-new-originating-selectors.shtml}
-
 %\bibitem{proceedings} A.~Kaczanowski, K.~Malarz, K.~Kulakowski, In: T.~E.~Simos (Ed.), International Conference of Computational Methods in Science and Engineering, Sep.

### 2016-02-29 paper/intro.tex
Moving cite

@@
 without compromising law-enforcement search capabilities.
-We are {\em not} suggesting support for ``key escrowed'' encryption
+We are {\em not} suggesting support for ``key-escrowed'' encryption
 or general backdoors in personal devices,
@@
 of {\it untargeted users} be protected.  We consider the surveillance goals
-of {\it set intersection} and {\it contact chaining}~\cite{techdirt} and show that both can 
+of {\it set intersection} and {\it contact chaining} and show that both can 
 be achieved in a privacy-preserving, accountable fashion.
@@
 graph} ({\it e.g.}, a phone-call graph, email graph, or social network) 
-in order to identify associates (or ``contacts'') of lawfully targeted users. 
+in order to identify associates (or ``contacts'') of lawfully targeted users~\cite{techdirt}. 
 Government agencies can then investigate those associates to determine whether

### 2016-02-29 paper/submission.tex
Moving cite

@@
 
-\vskip 2\baselineskip %needed to compile correctly
+\vskip 1\baselineskip %needed to compile correctly
 
@@
 Privacy-Preserving Intersection Warrants for Lawful Surveillance,
-February 2016 \url{https://drive.google.com/file/d/0BwK1bcoczINtbUhPaFI0Mk1DVk0/view}
+February 2016, \url{https://drive.google.com/file/d/0BwK1bcoczINtbUhPaFI0Mk1DVk0/view}
+
+\bibitem{anderson13cell} N.~Anderson, arstechnica, August 29, 2013.
 
@@
 3rd, 2014, \url{https://www.techdirt.com/articles/20140629/16130227727/nsa-appears-to-be-chaining-calls-using-phone-numbers-one-hop-out-as-new-originating-selectors.shtml}
-
-\bibitem{anderson13cell} N.~Anderson, arstechnica, August 29, 2013.
 

### 2016-04-14 rebuttal.txt
Adding rebuttal.txt

Reviewers C and D seem to base their "reject" scores on the notion that
section 3 is our main contribution. Actually, section 3 is intended as
relevant background from our previous paper. Sections 4 and 5 are our
main results, as reviewer A noted. A camera-ready version without
author anonymity requirements would make this relationship clear.

Section 3.3 is indeed merely an engineering result, which we never
intended to carry the weight of the paper. We included it in order to
respond to specific concerns raised after the presentation of our last
paper. It could be moved to an appendix.

Reviewer A:

We selected the social network to experiment on because we preferred
real data to simulated data, and because the actual phone call graph is
not freely available. But we do have similar results for simulated
graphs which we could include in the camera-ready version.

Reviewer B:

If the law enforcement agency already holds part of the database, we
can treat that agency as a "telecom" for the purpose of the protocol
without (further) compromising privacy.

Our understanding is that the changes to the "215" program mean that
the telecoms store user data until it is searched by the government.
Although we did not say so explicitly, that is the model our
contact-chaining algorithm uses.

Reviewer C:

It is true that telecoms have colluded with law enforcement in the
past, but no system can account for telecoms arbitrarily sending data
to other parties, except perhaps for a legal evidentiary hearing.

Reviewer D:

We agree that a solution resistant to all agencies colluding would be
excellent, but the notion of distributed trust is also well-founded in
the literature. On the other hand, neither of the alternatives reviewer
D mentions serve for the purpose of mass surveillance that we address,
and neither of them have considered contact-chaining, our main
contribution.

We are familiar with accountable anonymity, but the problem of mass
surveillance is fundamentally different. Accountable anonymity treats
each user as a party to the protocol. In papers such as Tsang et al.,
"revoked" users are not deanonymized, and the authority responsible for
revoking users is assumed to be honest. In dining-cryptographers-based
accountable anonymity protocols, the identities of all users must be
known in advance, and individual users can be held accountable only
through a deviation from the protocol in some way, and potentially at
great computational cost. Neither type of accountable anonymity is
fully collusion-resistant.

Revokable privacy is similar to privacy-preserving surveillance in many
ways, but the crucial distinction is that revokable privacy has been
studied primarily in theoretical contexts involving fairly small
amounts of data, whereas our work focuses on practicality, scalability,
and *mass* surveillance. Lueks et al. offer no sense of how long it
would take to run forward-secure distributed encryption on commercial
hardware, and their protocols are exponential. The common use case of
hundreds of cars driving down a highway is not scalable to hundreds of
thousands (or more) of users on a communication network.

### 2016-07-12 paper/conc.tex
More-or-less revised for arXiv preprint submission. Bibliography is a terrible mess though.

@@
 interdisciplinary, is needed.
+
+\subsection*{Acknowledgments}
+
+The first author was supported by a Google Faculty Research Award.
+The second author was supported by NSF grants CNS-1407454 and CNS-1409599, DHS grant FA8750-16-2-0034, and William and Flora Hewlett Foundation grant 2016-3834.
+The third author was supported by EPFL, the AXA Research Fund, and DHS grant FA8750-16-2-0034.

### 2016-07-12 paper/intro.tex
More-or-less revised for arXiv preprint submission. Bibliography is a terrible mess though.

@@
 Adopting the approach to third-party records search
-taken by Bandits~\cite{sff-foci2014}\footnote{Throughout this submission, we
-cite an anonymized version of an existing paper on accountable surveillance
-and use the pseudonym ``Bandits'' instead of the names of the authors.}, we
-seek to design and implement protocols for {\it accountable surveillance}.
+taken by Bandits~\cite{sff-foci2014},
+%\footnote{Throughout this submission, we
+%cite an anonymized version of an existing paper on accountable surveillance
+%and use the pseudonym ``Bandits'' instead of the names of the authors.}
+we seek to design and implement protocols for {\it accountable surveillance}.
 We require that government surveillance be conducted according to {\it open

### 2016-07-12 paper/submission.tex
More-or-less revised for arXiv preprint submission. Bibliography is a terrible mess though.

@@
 %\RequirePackage[no-math]{fontspec}%(only for the luatex or the xetex engine)
-\usepackage[big]{dgruyter_NEW}
+%\usepackage[big]{dgruyter_NEW}
+\usepackage{amsmath}
+\usepackage{hyperref}
 
-\DOI{foobar}
+%\DOI{foobar}
 
-\cclogo{\includegraphics{by-nc-nd.pdf}}
+%\cclogo{\includegraphics{by-nc-nd.pdf}}
 
@@
 
-\begin{document}
+  \title{Open, privacy-preserving protocols for lawful surveillance}
+  \author{
+	Aaron Segal and Joan Feigenbaum \\
+	Yale University \\
+	New Haven, CT, USA
+	\and
+	Bryan Ford \\
+	Swiss Federal Institute of Technology (EPFL) \\
+	Lausanne, Switzerland}
+  \date{}
 
   %\author*[1]{Aaron Segal}
-  \author[1]{Names withheld}
+  %\author[1]{Names withheld}
 
@@
   %\affil[1]{Yale Univ., E-mail: Aaron.Segal@yale.edu}
-  \affil[1]{Affiliations and email addresses withheld}
+  %\affil[1]{Affiliations and email addresses withheld}
 
@@
 
-  \title{\huge Open, privacy-preserving protocols for lawful surveillance}
+  %\title{\huge Open, privacy-preserving protocols for lawful surveillance}
 
-  \runningtitle{Privacy-preserving, lawful surveillance}
+  %\runningtitle{Privacy-preserving, lawful surveillance}
 
   %\subtitle{...}
+
+\begin{document}
+
+\maketitle
 
@@
   \end{abstract}
-  \keywords{Privacy, Secure multiparty computation, Surveillance}
+%  \keywords{Privacy, Secure multiparty computation, Surveillance}
 %  \classification[PACS]{}
@@
 
-  \journalname{Proceedings on Privacy Enhancing Technologies}
-\DOI{Editor to enter DOI}
-  \startpage{1}
-  \received{February 29, 2016}
+  %\journalname{Proceedings on Privacy Enhancing Technologies}
+  %\DOI{Editor to enter DOI}
+  %\startpage{1}
+  %\received{February 29, 2016}
   %\revised{..}
@@
 
-  \journalyear{2016}
-  \journalvolume{2016}
-  \journalissue{4}
+  %\journalyear{2016}
+  %\journalvolume{2016}
+  %\journalissue{4}
 
@@
 
-%\bibitem{sff-foci2014} A.~Segal, B.~Ford, J.~Feigenbaum, 
-%In: J. Crandall and V. Paxson (Eds.), $4^{th}$ Workshop on Free and 
-%Open Communications on the Internet, August 18, 2014, San Diego, 
-%USA (USENIX, Berkeley, 2014)
+\bibitem{sff-foci2014} A.~Segal, B.~Ford, J.~Feigenbaum, 
+In: J. Crandall and V. Paxson (Eds.), $4^{th}$ Workshop on Free and 
+Open Communications on the Internet, August 18, 2014, San Diego, 
+USA (USENIX, Berkeley, 2014)
 
@@
 
-\bibitem{sff-foci2014} Bandits, Catching Bandits and Only Bandits:
-Privacy-Preserving Intersection Warrants for Lawful Surveillance,
-February 2016, \url{https://drive.google.com/file/d/0BwK1bcoczINtbUhPaFI0Mk1DVk0/view}
+%\bibitem{sff-foci2014} Bandits, Catching Bandits and Only Bandits:
+%Privacy-Preserving Intersection Warrants for Lawful Surveillance,
+%February 2016, \url{https://drive.google.com/file/d/0BwK1bcoczINtbUhPaFI0Mk1DVk0/view}
 

### 2016-07-12 paper/submission.tex
Reformat to ACM double column

@@
-\documentclass[USenglish,oneside,twocolumn]{article}
+%\documentclass[USenglish,oneside,twocolumn]{article}
+\documentclass{sig-alternate-05-2015}
+
 \usepackage{etex}
@@
 	Yale University \\
-	New Haven, CT, USA
+	New Haven, CT, USA\\
+	\{aaron.segal,joan.feigenbaum\}@yale.edu\\
 	\and
@@
 	Swiss Federal Institute of Technology (EPFL) \\
-	Lausanne, Switzerland}
+	Lausanne, Switzerland\\
+	bryan.ford@epfl.ch}
   \date{}
@@
 \begin{document}
+
+\setcopyright{acmcopyright}
+%\setcopyright{acmlicensed}
+%\setcopyright{rightsretained}
+%\setcopyright{usgov}
+%\setcopyright{usgovmixed}
+%\setcopyright{cagov}
+%\setcopyright{cagovmixed}
+
+% DOI
+%\doi{10.475/123_4}
+
+% ISBN
+%\isbn{123-4567-24-567/08/06}
+
+%Conference
+\conferenceinfo{WPES '16}{October 24, 2016, Vienna, Austria}
+
+%\acmPrice{\$15.00}
 

### 2016-07-12 paper/submission.tex
Put citations from bibitems into chaining.bib

@@
 %% ###################################################################
-
-\begin{thebibliography}{99}
-%\bibitem{journal-1} A.~P.~Raposo, H.~J.~Weber, D.~E.~Alvarez--Castillo, M.~Kirchbach, Cent. Eur. J. Phys. 5, 253 (2007)
-%\bibitem{journal-2} J.~Barth et al. (SAPHIR Collaboration), Phys. Lett. B 572, 127 (2003)
-%\bibitem{journal-3} S.~Chekanov et al., Eur. Phys. J. C 51, 289 (2007)
-%\bibitem{journal-4} K.~Malarz, Postepy Fizyki 57, 235 (2006) (in Polish)
-%\bibitem{journal-5} G.~Meng, Cent. Eur. J. Phys., DOI:10.2478/s11534-007-0038-1
-%\bibitem{journal-6} R.~Hegselmann, U.~Krause, Journal of Artificial Societies and Social Simulation (2006), https://urldefense.proofpoint.com/v2/url?u=http-3A__jasss.soc.surrey.ac.uk_9_3_10.html&d=AwIGaQ&c=-dg2m7zWuuDZ0MUcV7Sdqw&r=TO0xacJWWmvm7m0roFn_liAsIL2PkxELeLGL8JNJXFw&m=Ka2FvolwqKNW8vu0FjJrZZz-0NBFnF_Zu-dQp-fjTto&s=370GY1pBTDyr9NSQToGqkNR8K-Xy1z0bsX64GpcLiPk&e=
-%\bibitem{journal-7} A.~Dybala, Cent. Eur. J. Chem. (in press)
-%\bibitem{journal-8} A.~Dybala, Przeglad chemiczny (in Polish, in press)
-%\bibitem{book} M.~Lister, Fundamentals of Operating Systems, 3rd edition (Springer-Verlag, New York, 1984)
-%\bibitem{chapter} C.~K.~Clenshaw, K.~Lord, In: B.~K.~P.~Scaife (Ed.), Studies in Numerical Analysis (Academic Press, London and New York, 1974) 95
-%\bibitem{arxiv-1} M.~Majewski, K.~Malarz, arXiv:cond-mat/0609635v2 [cond-mat.stat-mech]
-%\bibitem{arxiv-2} J.~A.~C.~E.~Solano, arXiv:0707.1343v1 [astro-ph]
-
-\bibitem{sff-foci2014} A.~Segal, B.~Ford, J.~Feigenbaum, 
-In: J. Crandall and V. Paxson (Eds.), $4^{th}$ Workshop on Free and 
-Open Communications on the Internet, August 18, 2014, San Diego, 
-USA (USENIX, Berkeley, 2014)
-
-\vskip 1\baselineskip %needed to compile correctly
-
-%\bibitem{sff-foci2014} Bandits, Catching Bandits and Only Bandits:
-%Privacy-Preserving Intersection Warrants for Lawful Surveillance,
-%February 2016, \url{https://drive.google.com/file/d/0BwK1bcoczINtbUhPaFI0Mk1DVk0/view}
-
-\bibitem{anderson13cell} N.~Anderson, arstechnica, August 29, 2013.
-
-\bibitem{techdirt} T.~Cushing, techdirt.com, Jul.
-3rd, 2014, \url{https://www.techdirt.com/articles/20140629/16130227727/nsa-appears-to-be-chaining-calls-using-phone-numbers-one-hop-out-as-new-originating-selectors.shtml}
-
-\bibitem{bieber-penn2002} M.~Bieber, Univ.~Penn.~Law Review, 150, 1079 (2002)
-
-\bibitem{dissent} H.~Corrigan-Gibbs, B.~Ford, In: A.~D.~Keromytis and 
-V.~Shmatikov (Eds.), $17^{th}$ Conference on Computer and Communications 
-Security, October 4-8, 2010, Chicago, USA (ACM, New York, 2010)
-
-\bibitem{verdict} H.~Corrigan-Gibbs, D.~I.~Wolinsky, B.~Ford, In: 
-S.~King (Ed.), $22^{nd}$ Security Symposium, August 14-16, 2013, 
-Washington, D.C., USA (USENIX, Berkeley, 2013)
-
-\bibitem{snapnets} J.~Leskovec, A.~Krevl, SNAP Datasets: 
-Stanford Large Network Dataset Collection, 
-http://snap.stanford.edu/data
-
-\bibitem{mobiforge} MobiForge, Global mobile statistics 2014 Part A: 
-Mobile subscribers; handset market share; mobile operators,\\ 
-https://mobiforge.com/research-analysis/global-mobile-\\
-statistics-2014-part-a-mobile-subscribers-handset-market-\\
-share-mobile-operators\#topmnos
-
-\bibitem{pgfw-scn2014} J. Perry, D. Gupta, J. Feigenbaum, R. Wright,
-In: M. Abdalla and R. De Prisco (eds.), $9^{th}$ Conference on Security and 
-Cryptography for Networks, September 3-5, 2014, Amalfi, Italy (Springer,
-Berlin, 2014)
-
-\bibitem{ay2008} C.~Aggarwal, P.~Yu, In: C.~Aggarwal and P.~Yu (Eds.), 
-Privacy-Preserving Data Mining: Models and Algorithms 
-(Springer, Berlin, 2008) 11
-
-\bibitem{kamara} S.~Kamara, In: M.~Brenner and M.~Smith (eds.), 
-$2^{nd}$ Workshop on Applied Homomorphic Cryptography and Encrypted Computing, 
-March 7, 2014, Barbados, West Indies (Springer, Berlin, 2014)
-
-\bibitem{kroll} J.~Kroll, E. Felten, D. Boneh, Secure protocols for
-accountable warrant execution, April 2, 2014,\\
-https://freedom-to-tinker.com/blog/felten/\\
-secure-protocols-for-accountable-warrant-execution/
-
-\bibitem{krwy-pnas16} M. Kearns, A. Roth, Z. S. Wu, G. Yaroslavtsev, 
-Proc.~Natl.~Acad.~Scis. 113, 913 (2016)
-
-\bibitem{elgamal} T.~ElGamal, IEEE Transactions on Information Theory, IT-31 No. 4 (1985)
-
-\bibitem{pohlighellman} S.~Pohlig, M.~Hellman, IEEE Transactions on Information Theory, IT-24 No. 1 (1978)
-
-%\bibitem{proceedings} A.~Kaczanowski, K.~Malarz, K.~Kulakowski, In: T.~E.~Simos (Ed.), International Conference of Computational Methods in Science and Engineering, Sep.
-12-16, 2003, Kastoria, Greece (World Scientific, Singapore 2003) 258
-%\bibitem{thesis} A.~J.~Agutter, Ph.D. thesis, Edinburgh University (Edinburgh, UK, 1995)
-%\bibitem{newspaper-1} A.~Sherwin, The Times, Jul. 13, 2007, 1
-%\bibitem{newspaper-2} M.~Dzierzanowski, Wprost, Jul. 8, 2007, 18 (in Polish)
-%\bibitem{patent} Philip Morris Inc., European patent application 0021165 A1, Jan. 7, 1981
-%\bibitem{standard-1} ISO 2108:1992, Information and documentation --- International standard book numbering (ISBN)
-%\bibitem{standard-2} ISO/TR 9544:1988, Information processing --- Computer-assisted publishing --- Vocabulary
-\end{thebibliography}
+\bibliography{chaining}
+\bibliographystyle{plain}
 

### 2016-08-03 paper/wpes16/chaining.tex
Joan's edited-down WPES draft as of July 15

--- 2016-02-29 paper/chaining.tex
@@
 \section{Lawful Contact Chaining}\label{sec-chaining}
-Contact chaining~\cite{techdirt} is a form of government surveillance with which it is deceptively easy to expose many innocent, untargeted users to government scrutiny.
-The goal of contact chaining is to use information about social connections between identities, such as records of phone calls between one number and another, to identify members of a criminal organization or terrorist group.
+The goal of contact chaining is to use information about social connections between identities, {\it e.g.}, records of phone calls between one number and another, to identify members of a criminal organization or terrorist group.
 Starting with one or more suspects whose identities are known, the government aims to consider contacts of those suspects.
 These can be \emph{direct contacts}, such as two people who spoke on the phone, or \emph{extended contacts}, such as two people connected by a chain of two or more phone calls.
-If Alice calls Bob, and Bob calls Charlie, then Alice and Bob are direct contacts (as are Bob and Charlie), but Alice and Charlie are extended contacts.
-We may also say that Alice and Charlie are at distance 2 in the communication graph (because the smallest number of phone calls that connect Alice to Charlie is 2).
+If Alice calls Bob, and Bob calls Charlie, then Alice and Bob are direct contacts (as are Bob and Charlie).
+If neither Alice nor Charlie called the other during the period of investigation that defines the graph, then we say that they are extended contacts (or, more precisely, that they are at distance two in the graph).
 
-Without mechanisms to preserve privacy, a contact chaining search can collect a surprisingly large group of users' information.
-For example, if the average cell phone user contacts 30 individuals within the period of the investigation, a contact chaining search out to distance 3 would capture 27,000 users on average - or many more if a heavy phone user is swept up by the search.
-With such a large group, it is assured that the vast majority of contacts will not be the targeted collaborators of the primary suspect in the investigation.
-This is a large and unnecessary intrusion of privacy.
-These untargeted users may nevertheless face unwarranted government scrutiny, intrusive investigation, or a risk that their sensitive communications histories may be leaked accidentally.
+Without mechanisms to preserve privacy, a contact chaining search can collect a surprisingly large group of users' information. For example, if the average 
+cell-phone user contacts 30 individuals within the period of the investigation,
+a contact-chaining search out to distance three would capture 27,000 users on average - or many more if a heavy phone user is swept up by the search.
+In such a large group, the vast majority of contacts will not be collaborators of the the targeted, primary suspect in the investigation.
+These untargeted users may nevertheless face government scrutiny, intrusive investigation, or a risk that their sensitive communications histories may be leaked accidentally.
 
-Despite this risk, we recognize the potential law-enforcement value of information about social connections between targeted invidivuals.
+Despite this risk, 
+we recognize the potential law-enforce\-ment value of information about the social contacts of targeted invidivuals.
 Therefore, we propose a \emph{lawful contact chaining protocol}.
@@
 Our protocol focuses on the case in which the government seeks information from multiple telecommunications providers about the communication graph formed by phone calls and text messages.
-Using this protocol, the agencies can retrieve an encrypted set of user data from multiple telecoms, each of which holds only part of a larger communication graph.
-This encrypted set contains the identities of users within a certain distance of a target, but the identities cannot be decrypted unless the agencies cooperate.
-Under the lawful processes we propose, this cooperation would take the form of an intersecton with other encrypted sets of data, using the protocol from Section~\ref{sec-intersection}.
-These sets can come from privacy-preserving contact chaining, from cell tower dumps, or from other sources of information about suspects.
+Using this protocol, the agencies can retrieve a set of encrypted records from multiple telecoms, {\it each of which holds only part of a larger communication graph}.
+This set of encrypted data
+contains the identities of users within a certain distance of a target, but the identities cannot be decrypted unless the agencies cooperate.
+Under the lawful processes we propose, this cooperation would take the form of intersecton with other sets of encrypted data.
+These sets can come from privacy-preserving contact chaining, from cell-tower dumps, or from other sources of information about suspects.
 Importantly, while any set may contain encrypted data about many untargeted users, very few users will appear in \emph{all} the sets, and those few users will be suitable targets for further lawful investigation.
@@
 The same principles of oversight and accountability provided by multiple government agencies can apply to contact chaining searches in other types of communication graphs, such as the social network graph of Twitter or Facebook.
-These cases do not require our protocol, however, since if one provider knows the entire communication graph, it can compute the output of the protocol without any interactivity needed.
+These cases do not require our protocol, however, since if one provider knows the entire communication graph, it can compute the output of the protocol without any interaction.
 
@@
 Each telecom knows only a subset of the edges $E$.
-$V$ contains vertices labeled with the phone numbers they represent, and $E$ contains an edge between $a$ and $b$ if and only if phone number $a$ has contacted phone number $b$ or vice versa within some window of time.
+$V$ contains vertices labeled with the phone numbers they represent, and $E$ contains an edge between $a$ and $b$ if and only if phone number $a$ has contacted phone number $b$ or {\it vice versa} within the period of the investigation.
 Each phone number $v$ is served by exactly one telecom.
@@
 $x$ is a target phone number.
-We assume, since $x$ belongs to a user targeted by the agencies, that they also know which telecom serves $x$.
-$k$ is a (small) distance from $x$, the distance at which the agencies wish to consider chained contacts.
-For example, if $k=2$, then the agencies only wish to consider users at most 2 phone calls away from their person (or phone number) of interest $x$.
-Choosing a small limit is important to limiting the scope of the investigation.
+Because $x$ belongs to a user targeted by the agencies, we assume that the agencies also know which telecom serves $x$.
+$k$ is the (small) distance from $x$ to which the agencies wish to ``chain out.''
+Choosing a small distance is important to limiting the scope of the investigation.
 However, many users' information might still be captured if some phone numbers have very many contacts.
 Suppose the target $x$ calls the most popular pizza place in town.
-Now everyone else who has recently called that pizza place is at a distance 2 to $x$.
+Now everyone else who has recently called that pizza place is at distance at most two from $x$.
 
 We can assume that business phone numbers have many more contacts than personal phone numbers do.
-In most cases, knowing that two individuals have contacted the same business phone number does not indicate that those individuals have a personal relationship.
-Therefore, the warrant also includes $d$, an upper bound on the degree of users the agencies are willing to ``chain'' through.
-If a phone number has more than $d$ contacts, then the agencies do not consider paths to other users through that phone number in their search.
-The agencies disregard $d$ for the initial target $x$, however.
-The high-degree users themselves will also be present in the agencies' outputs.
+In most cases, knowing that two individuals have contacted the same business does not indicate that those individuals have a personal relationship.
+Therefore, the warrant also includes $d$, an upper bound on the degree of users that the agencies are willing to ``chain through.'' If a phone number has more than $d$ contacts, then the agencies do not follow paths to other users through that phone number in their search (but do include that number in the output).
+The agencies disregard $d$ for the initial target $x$, however, because they have already determined that contacts of $x$ are of potential interest, even if $x$ is a business.
 
 This provides a reasonable limit to the scope of the investigation and hides what are very likely to be untargeted users from the government.
-In the uncommon scenario where a business number with many contacts also functions as a front or hub for a criminal organization to be revealed, the government is still able to conduct further investigation on it, perhaps even beginning a new contact-chaining search with that number as the initial target.
-
-We specify the protocol in full in Sections~\ref{sec-proto1} and \ref{sec-proto2}.
+In the uncommon scenario in which a business with many contacts also functions as a front for a criminal organization, the government could conduct further investigation, perhaps beginning a new contact-chaining search with that number as the initial target.
 
@@
 
-We make a few assumptions about existing cryptographic infrastructure.
-All telecoms and agencies must have a public encryption key known to all other parties to the protocol and a private decryption key.
-For the purpose of interoperability with lawful intersection, agencies' keys must be for a commutative cryptosystem (i.e.
-ElGamal).
-The parties must also each have private signing keys and public verification keys.
+We assume some existing cryptographic infrastructure. 
+All telecoms and agencies must have public encryption keys known to all other parties to the protocol and private decryption keys. 
+For the purpose of interoperability with lawful intersection~\cite{sff-foci2014}, agencies' keys must be for a commutative cryptosystem ({\it e.g.}, ElGamal). 
+Each party must also have a private signing key and a public verification key.
 
-In the protocol below, we refer to ``the agencies'' sending messages to one or more telecoms.
-Exactly which agency transmits messages to the telecoms is not important to our protocol, but a telecom will disregard any message not accompanied by signatures from every agency.
-One simple topology is for a single agency to handle all direct communication with telecoms and with other agencies, forwarding reponses from the telecoms on to the other agencies and signatures on agency messages to the telecoms.
+In the protocol below, we refer to ``the agencies' sending'' messages to one or more telecoms.
+Exactly which agency transmits messages to the telecoms is not important to our protocol, but a telecom will disregard any message not accompanied by signatures from all agencies.
+One simple topology is for a single agency to act as a relay, forwarding reponses from the telecoms to the other agencies and signatures on agency messages to the telecoms.
 
-Our protocol preserves the privacy of untargeted users as long as all parties execute the protocol in an honest-but-curious manner, all of the government agencies do not collude together, and no telecoms collude with government agencies.
-A colluding group containing all agencies would be equivalent to the current situation n which the government does not provide meaningful accountability of its own surveillance activities; what we propose is a replacement for this situation, but it does require the government to follow its own laws, once set.
-A telecom colluding with a government agency would amount to sending that agency free information about its users, or submitting incorrect information to the protocol.
+Our protocol preserves the privacy of untargeted users as long as all parties execute the protocol in an honest-but-curious manner, 
+at least one of the government agencies does not collude with the others, and no telecom colludes with government agencies. 
+A colluding group containing all agencies would be equivalent to the current situation, in which the government does not provide meaningful accountability of its own surveillance activities; what we propose is a replacement for this situation, but it does require the government to follow its own laws, once set.
+A telecom's colluding with a government agency would amount to sending that agency free information about its users or submitting incorrect information to the protocol.
 But telecoms have no business purpose to deviate from the protocol and risk legal action.
@@
 
-\subsubsection{Desired Outputs and Security Properties}
+\subsubsection{Desired Outputs and Privacy Properties}
 
 The goal of the protocol is for the agencies to obtain a set of ciphertexts, each of which is the encryption of a phone number $v$ such that the distance in the communication graph from $v$ to the targeted phone number $x$ is at most $k$.
-The set should not contain encryptions of numbers $v$ such that each path from $x$ to $v$ of length at most $k$ contains an intermediate vertex of degree greater than $d$.
-Here the ``intermediate'' vertices in a path are all vertices except the endpoints $x$ and $v$.
+The set should not contain encryptions of numbers $v$ such that each path from $x$ to $v$ of length at most $k$ contains an intermediate vertex of degree greater than $d$; the ``intermediate'' vertices in a path are all vertices except the endpoints $x$ and $v$.
 
@@
 Instead, each telecom's output should contain only a list of which of the phone numbers it serves were sent to the government agencies.
-This allows the telecoms to play an additional accountability role in this protocol.
-The government may have an interest in keeping the telecoms from knowing which of their clients were surveilled; we discuss this in section~\ref{sec:oblivious}.
+This allows the telecoms to play an additional accountability role.
 
-With the encryptions of these phone numbers, the agencies can then act as appropriate to further investigate them.
-In particular, the encrypted set of phone numbers can be used as an input into a lawful set intersection protocol.
+With the encryptions of these phone numbers, the agencies can act as appropriate to further investigate them.
+In particular, the set of encrypted phone numbers can be intersected with, say, the encrypted numbers of people on a terrorist
+watch list~\cite{sff-foci2014}.
 
-Below, we present two versions of our protocol.
-In the first version, the agencies and telecoms learn some additional information.
-Specifically, the agencies learn the provider of each phone number in the encrypted set, and the distance from $x$ of each encrypted phone number.
+In the basic protocol presented here, the agencies and telecoms learn some additional information.
+Specifically, the agencies learn which provider serves each encrypted phone number in the output set and the distance from $x$ of each encrypted phone number.
 Each telecom learns which of the phone numbers it serves appear in the agencies' output, as well as the distance of each of those phone numbers from the target phone number $x$.
+In \cite[Section 4.1.5]{sff-TR}, we present a modified version of the protocol that uses a DC-net-based anonymity subprotocol to prevent the agencies from learning which telecom serves which encrypted phone numbers.
 
-In section \ref{sec-proto2}, we will present a second version of the protocol in which the agency \emph{does not} learn which telecom serves which encrypted phone number.
+As long as our security assumptions hold, the agencies collectively learn \emph{no} information about the edge set $E$ except what is implied by the output.
+Furthermore, the agencies cannot learn any of the phone numbers that appear in encrypted form in the output (unless implied by the size of the encrypted output and the leaked service information), nor can agencies cause a phone number not within distance $k$ of $x$ to appear in the output, even in encrypted form.
 
-As long as our security assumptions for this protocol hold, the agencies collectively learn \emph{no} information about the edge set $E$ except what is implied by the output.
-Furthermore, the agencies cannot learn any of the phone numbers that appear in encrypted form in the output (unless implied by the size of the encrypted output and the leaked service information), nor can agencies cause a phone number not within distance $k$ of target $x$ to appear in the output, even in encrypted form.
-
-\subsubsection{Ownership-Revealing Lawful Contact-Chaining Protocol}
+\subsubsection{Lawful Contact-Chaining Protocol}
 
@@
 However, all messages the agencies receive from the telecoms will be encrypted.
-They will know which message come from which telecoms, and will therefore know which telecoms serve which ciphertexts.
-
 Let $\Enc_T(m)$ be the encryption of message $m$ under telecom $T$'s public key.
@@
 $\mathbf{Q}$ contains tuples for unexplored vertices $a$ of the form $(\Enc_{T(a)}(a), T(a), j)$.
-These tuples contain the telecom ciphertext for $a$, a record of which telecom owns $a$, and an integer $j$ indicating the remaining distance out to which neighbors can be chained from $a$.
+These tuples contain the telecom ciphertext for $a$, a record of which telecom owns $a$, and an integer $j$ indicating the remaining distance from $a$ still to be covered by the search.
 
-The agencies will represent their output in the form of a list $\mathbf{C}$, containing agency ciphertexts.
-Each telecom $T$ will represent its output in the form of a list $\mathbf{L}_T$, listing plaintext users served by that telecom whose information the agencies requested.
-
+The agencies will represent their output as a list $\mathbf{C}$, containing agency ciphertexts.
+Each telecom $T$ will represent its output as a list $\mathbf{L}_T$, listing plaintext users served by that telecom whose information the agencies requested.
 The protocol is as follows:
 
-\begin{enumerate}
+\begin{compactenum}
 
-\item The agencies start by agreeing upon a warrant $(x, k, d)$, where $x$ is the target phone number, $k$ is a maximum distance, and $d$ is an upper limit on the degree of vertices to chain through.
+\item The agencies start by agreeing upon a warrant $(x, k, d)$. 
 They encrypt $x$ under the public key of $T(x)$.
 
-\item The agencies initialize a queue $\mathbf{Q}$. Initially, $\mathbf{Q}$ contains only the triple $(\Enc_{T(x)}(x), T(x), k)$.
+\item The agencies initialize $\mathbf{Q}$ to contain 
+$(\Enc_{T(x)}(x), T(x), k)$.
 
@@
 
-\begin{enumerate}
+\begin{compactenum}
 
@@
 
-\end{enumerate}
+\end{compactenum}
 
@@
 
-\end{enumerate}
+\end{compactenum}
 
-For the sake of efficiency, it is worth noting that the inner loop can be executed many times in parallel, up to the point of completely emptying $\mathbf{Q}$ at the beginning of the loop.
+Note that the inner loop can be executed many times in parallel, up to the point of completely emptying $\mathbf{Q}$ at the beginning of the loop.
 Many messages to the same telecom can also be batched and sent together, thereby reducing the number of signing and verifying operations so that they depend only on $k$ and not on the size of the input or output.
 
-\subsubsection{Ownership-Hiding Lawful Contact-Chaining Protocol}
-
-\label{sec-proto2}
-
-The previous version of the protocol allows agencies to learn which telecoms own the phone numbers in its encrypted output.
-This subsection presents a modification of the previous version of the protocol, which uses a DC-nets-based \emph{anonymity protocol} to hide this information from the agencies (except with respect to the initial target $x$).
-
-An anonymity protocol is run by a number of parties, some of which have messages to send.
-At the end of the protocol, all parties must learn all messages sent, but no party other than the sender of any given message can learn which party sent that message.
-Dissent~\cite{dissent} and Verdict~\cite{verdict} both satisfy our requirements; they are more powerful than we need, however, because we assume all telecoms are honest-but-curious.
-
-We can use an anonymity protocol to allow the correct telecom to respond anonymously in steps \ref{proto1:first-send} and \ref{proto1:second-send} in the protocol above.
-This removes the need for the agencies to know which telecom owns which ciphertext.
-
-Now we can present the following modified protocol.
-This protocol uses the same data structures as in section~\ref{sec-proto1}, except that $\mathbf{Q}$ now contains pairs $(\Enc_{T(a)}(a), j)$ for unexplored vertices $a$ (omitting the identity of $T(a)$.
-
-\begin{enumerate}
-
-\item The agencies start by agreeing upon a warrant $(x, k, d)$, where $x$ is the target phone number, $k$ is a maximum distance, and $d$ is an upper limit on the degree of vertices to chain through.
-They encrypt $x$ under the public key of $T(x)$.
-
-\item The agencies initialize a queue $\mathbf{Q}$. Initially, $\mathbf{Q}$ contains only the pair $(\Enc_{T(x)}(x), k)$.
-
-\item The agencies initialize the output list $\mathbf{C}$ to be empty.
-
-\item Each telecom $T$ initializes its output lists $\mathbf{L}_T$ to be empty.
-
-\item While $\mathbf{Q}$ is not empty, do the following:
-
-\begin{enumerate}
-
-\item \label{proto2:dequeue} The agencies dequeue a pair $(\Enc_{T(a)}(a), j)$ from $\mathbf{Q}$. They send the pair $(\Enc_{T(a)}(a), j)$ to all telecoms.
-
-\item All telecoms attempt to decrypt $\Enc_T(a)(a)$ with their decryption keys. Only $T(a)$ will be able to do so. Other telecoms skip to step~\ref{proto2:anon}.
-
-\item $T(a)$ adds $a$ to $\mathbf{L}_T$.
-
-\item \label{proto2:agencycipher} $T(a)$ encrypts $a$ under the agencies' public keys, producing the agency ciphertext $\Enc_\mathcal{A}(a)$.
-
-\item \label{proto2:telecomcipher} If $j>0$, $T(a)$ encrypts each neighbor $b$ of $a$ under the public key of $T(b)$, creating a telecom ciphertext for $b$.
-
-\item \label{proto2:anon} All parties to this protocol engage in the anonymity protocol.
-$T(a)$ sends an anonymous message consisting of the agency ciphertext it generated in step~\ref{proto2:agencycipher}; the set of telecom ciphertexts generated in step \ref{proto2:telecomcipher}, and $\de(a)$, the number of telecom ciphertexts being sent.
-The agencies and all telecoms that could not decrypt $\Enc_{T(a)}(A)$ participate but send no anonymous message.
-
-\item When the anonymity protocol is complete, the agencies receive all the ciphertexts. They add $\Enc_\mathcal{A}(a)$ to $\mathbf{C}$.
-
-\item If $\de(a)>d$ and $j\neq k$ (i.e.
-$a\neq x$), the agencies discard all telecom ciphertexts received for $a$'s neighbors (i.e., agencies refuse to sign these ciphertexts in future steps of the protocol, and do not send them on to the telecoms).
-
-\item Otherwise, for each telecom ciphertext received, the agencies add $(\Enc_{T(b)}(b), j-1)$ to $\mathbf{Q}$.
-
-\end{enumerate}
-
-\item The agencies' final output is the list $\mathbf{C}$. Each telecom $T$'s final output is $\mathbf{L}_T$.
-
-\end{enumerate}
-
-The protocol replaces each query in the protocol of section~\ref{sec-proto1} with broadcast of the telecom ciphertext to all telecoms, and replaces each response with a round of the anonymity protocol.
-This allows the telecom that owns each phone number to respond with appropriate information about the phone number, but shields the telecom's identity from the agencies (and incidentally from other telecoms).
-
-As in the previous section, It should be noted that the agencies and telecoms need not handle one ciphertext at a time.
-The agencies can in principle dequeue all of $\mathbf{Q}$ in step \ref{proto2:dequeue} and broadcast all pending vertices to the telecoms.
-In step \ref{proto2:anon}, multiple telecoms can submit multiple messages to a single run of the anonymity protocol, with only those telecoms which were unable to decrypt any vertices submitting no message.
-The exact number of messages per instance of the anonymity protocol can be tuned for best efficiency.
-
-\subsection{Discussion of Lawful Contact-Chaining}
-
-\label{sec:discuss}
-
-We now take a moment to discuss the correctness and privacy properties of both variants of our lawful contact-chaining protocol.
-
-\subsubsection{Correctness of Output}
-
-The agencies' outputs from the protocols in Sections~\ref{sec-proto1} and \ref{sec-proto2} will be $\mathbf{C}$.
-$\mathbf{C}$ will contain agency ciphertexts of all phone numbers at most $k$ phone calls away from $x$, considering only vertices of degree at most $d$.
-This is the desired output.
-$C$ reveals nothing to any agencies unless they all provide their decryption keys.
-To continue the process of lawful investigation, the agencies should combine the output $\mathbf{C}$ with other sets of potential suspects (such as from further runs of this protocol, or from cell tower dumps) in a lawful intersection protocol.
-
-\subsubsection{Privacy}
-
-Both versions of the protocol hide the identities of the chained contacts of $x$.
-They do allow the agencies to learn the distance from $x$ of each ciphertext in their output, but these ciphertexts cannot be resolved to phone numbers without the cooperation of all agencies.
-
-The protocol of section~\ref{sec-proto1} allows the agencies to learn which telecoms owns which ciphertexts in $\mathbf{C}$.
-This may be a security concern, since some telecoms are relatively small, specialized, or localized to a particular country or region.
-If the agencies know that such a such a telecom owns an encrypted phone number, this will not allow them to identify the phone number itself, but might convince the agencies to subject that ciphertext to additional scrutiny, up to the point of decrypting it outside the context of lawful surveillance.
-This would still require the collusion of all agencies, however.
-Our revised protocol mitigates this concern.
-Assuming that the anonymity protocol used in section~\ref{sec-proto2} does not allow its participants to learn who sends each message, then the revised protocol does not leak ciphertext ownership information.
-
-The telecoms learn two types of information as part of the lawful contact chaining protocol.
-First, they learn the warrant.
-Second, they learn which of the phone numbers they serve have been captured (in encrypted form) by the protocol, and when they were captured.
-The telecoms might possibly be able to infer some extra information about $G$ from observing when vertices they own are queried by the agencies, but only of a very limited form.
-For instance, an agency may serve two phone numbers, $a$ and $b$, which the agencies query at distance 1 and 4 from $x$, respectively .
-In that case, the telecom can infer that there exists a path in $G$ of length 3 between $a$ and $b$.
-The telecom does not learn which other phones are involved in that path, and is already aware of all paths of length 2 or less between phone numbers it serves.
-Therefore, this potential information leak is of little concern.
-
-\subsubsection{Hiding Information From Telecoms}
-
-\label{sec:oblivious}
-
-In both versions of our protocol, the telecoms learn which of their numbers have been submitted to the agencies.
-They do not know which phone numbers the agencies will actually investigate after running the privacy-preserving set intersection protocol, but they do know which ones \emph{could} be under investigation.
-Since many numbers \emph{could} be investigated, this does not compromise the agencies' investigative power.
-
-We may point out nevertheless that a modification of our protocol from \ref{sec-proto1} could allow the agencies to hide from the telecoms which of their clients is being surveilled.
-The telecoms would need to precompute agency ciphertexts for all of their client numbers, and telecom ciphertexts for all of their clients' contacts.
-With these precomputed databases, the telecoms could then use oblivious transfer to blindly serve the agencies' requests for information about their clients.
+Correctness and privacy of the basic protocol are argued 
+in~\cite[Section 4.2]{sff-TR}.
 
@@
 
-\label{sec:implementation}
+We implemented the basic protocol in Java and tested the implementation's 
+running time, CPU time used, and data sent over the network. 
+Our implementation uses the variant of our protocol in which the agencies 
+completely exhaust the search queue $\mathbf{Q}$ each round, 
+sending all queries at any given distance from $x$ to the 
+telecoms at once in batches. This variant allows for greater parallelism. 
+All of the telecoms receive their batch of queries at the same time and 
+operate on those queries using eight parallel threads of computation.
 
-We implemented the privacy-preserving contact chaining search protocol of~\ref{sec-proto1} in Java and tested the implementation's running time, CPU time used, and data sent over the network.
-Below, we describe our implementation and its experimental setup, and then summarize our results.
+We use 2048-bit DSA signatures, 2048-bit RSA encryption for the telecoms, 
+and ElGamal encryption for the agencies' output. 
+Our Java program supports any number of agencies and telecoms, but we chose to run tests with three government agencies and four telecoms.
 
-\subsubsection{Java Implementation}
-
-Our Java implementation uses the variant of our protocol in which the agencies completely exhaust the search queue $\mathbf{Q}$ each round, sending all queries at any given distance from $x$ to the telecoms at once in batches.
-Ths variant allows for greater parallelism.
-All of the telecoms receive their batch of queries at the same time, and operate on those queries using eight parallel threads of computation.
-
-We use 2048-bit DSA signatures, 2048-bit RSA encryption for the telecoms, and ElGamal encryption for the agencies' output to provide compatability with the lawful intersection protocol of~\cite{sff-foci2014}.
-
-Our Java program supports any number of agencies and telecoms, but we chose to run tests with three government agencies and four telecoms.
-Each agency and telecom has a dedicated server in our cloud testbed.
-As mentioned in~\cite{sff-foci2014}, three is a reasonable choice for the number of agencies, corresponding to three branches of government.
-Four telecoms should cover most users in any given mobile phone market, and increasing the number of telecoms in our experiments only serves to decrease the protocol's total running time by splitting the same users over more servers.
-
-\subsubsection{Experimental Setup}
-
-For our underlying contact graph, we used an anonymized data set provided by~\cite{snapnets} containing 1.6 million users from Pokec, a Slovakian social network.
-To replicate the multi-provider environment of the real telephone network, we assigned each user to one of four telecom servers.
+For our underlying communication graph, we used an a\-no\-ny\-mized data set of 1.6 million users from Pokec, a Slovakian social network~\cite{snapnets}.
+To replicate the multi-provider environment, we assigned each user to one of four telecom servers.
 The telecoms were each given a different number of the users, in proportion to the subscriber base of the largest four telecoms in the world~\cite{mobiforge}.
 
-To experiment with differently sized output sets, we ran our protocol many times, varying $x$, $k$, and $d$.
-We chose a variety of different-degree starting targets $x$, varied the maximum path length $k$ between 2 and 3, and varied $d$ from 25 to 500.
-For each run, we measured the total running time of the protocol, the CPU time spent by the agencies and telecoms, and the amount of data sent over the network in total.
-
 These results are important in evaluating how practical our lawful contact-chaining protocol would be it were put into practice by government agencies and telecoms.
-However, our data set is relatively small compared to the databases held by real telecommunications companies, and each company handles that data using different technologies.
+However, our data set is relatively small compared to the data\-ba\-ses held by real telecommunications companies, and each company handles that data using different technologies.
 The absolute running time and CPU usage of executing this protocol could vary from telecom to telecom.
@@
 This version of the protocol does not preserve the privacy of users.
-By comparing the performance of our lawful contact-chaining protocol with the zero-cryptography contact-chaining protocol, however, we can get a sense of the ``cost'' of privacy and accountability as compared to the practice of releasing plaintext data to government surveillance.
+By comparing the performance of our lawful contact-chaining protocol with the zero-cryptography contact-chaining protocol, however, we can get a sense of the ``cost of privacy and accountability.''
+
+Additional detail about our Java implementation and experimental setup can be found in \cite[Section 4.3]{sff-TR}.
 
@@
 We display graphs of our recorded data in Figure~\ref{fig:performance}.
-Taking the average of all cases with $d>25$, the telecoms used 58.2 ms of CPU time per ciphertext.
+%Taking the average of all cases with $d>25$, the telecoms used 58.2 ms of CPU time per ciphertext.
 The agencies used, again in the average case, 2.0 ms of CPU time per ciphertext.
@@
 To return to our example from earlier of a network with an average of 30 contacts per user, a lawful contact-chaining search with $k=2$ would have 900 users in the output, and a search with $k=3$ would have 27,000 users in the output.
-To compare these times to some of our acutal experiments, we found that a search that returned 937 ciphertexts took 6.86 seconds to run, and a search that returned 27,338 ciphertexts took 109.55 seconds to run.
-To provide another point of comparison, \cite{sff-foci2014} referred to the ``High Country Bandits'' case, in which the FBI performed an intersection of 150,000 phone number to help solve a series of bank robberies.
+To compare these times to some of our actual experiments, we found that a search that returned 937 ciphertexts took 6.86 seconds to run, and a search that returned 27,338 ciphertexts took 109.55 seconds to run.
+%To provide another point of comparison, recall that, in~\cite{sff-foci2014}, we studied the ``High Country Bandits'' case, in which the FBI performed an intersection of 150,000 phone number to help solve a series of bank robberies.
 In one of our experiments with lawful contact chaining, we find that a similarly sized data set of 149,535 ciphertexts took 625.08 seconds - 10.4 minutes - to compile with our protocol.
@@
 The total CPU time across all telecoms needed for our zero-crypto implementation never rose above ten seconds, even in the largest cases.
-This result allows us to disambiguate the cost of \emph{information retrieval} from \emph{privacy protection}.
+%This result allows us to disambiguate the cost of \emph{information retrieval} from \emph{privacy protection}.
 The linear relationship between the size of the encrypted user data set and the performance in terms of running time, CPU time, and network data usage of the protocol all remain even when we subrtract out the time to run all non-cryptgraphic parts of the protocol.
-We therefore conclude that, even given the potental database operations real telecoms would have to contend with, the cost of adding privacy-preservation to the contact-chaining protocol will remain reasonable.
+We conclude that, even given the scale of database operations that real 
+telecoms perform, the cost of adding privacy-preservation to the contact-chaining protocol is reasonable.
+
+More detailed performance analysis is presented in~\cite[Section 4.3]{sff-TR}.

### 2016-08-03 paper/wpes16/conc.tex
Joan's edited-down WPES draft as of July 15

\section{Open Problems and Future Work}\label{sec-future}
Thus far, we have explored accountable, privacy-preserving protocols for
set intersection and contact chaining. 
Another operation of potential interest is the retrieval of
targeted users' postings on Facebook and other social networks, including 
those that are shared only with a small subset of the target's 
``friends.'' Accountable surveillance of social-network postings may present 
novel protocol-design challenges, because it deals with one-to-many 
communication, while previous work dealt with pairwise communication.

It may be possible to speed up our contact-chaining protocols by using
elliptic-curve cryptography instead of RSA. Our assumption that
all parties are honest-but-curious might be weakened, {\it e.g.}, by using 
zero-know\-ledge techniques to obtain versions
of our protocols that are secure against
a rogue agent's maliciously modifying telecom-supplied data in order
to falsely incriminate a victim. One may wish to
generalize the differential-privacy approach of Kearns {\it et 
al.}~\cite{krwy-pnas16} to handle to indirect contacts as well as
direct contacts.

Finally, the Openness Principle of \cite{sff-foci2014} is but one step
toward a full understanding of how democratic processes and the rule of law
can be carried into the digital world.  Further investigation, much of it
interdisciplinary, is needed.

%

### 2016-08-03 paper/wpes16/intro.tex
Joan's edited-down WPES draft as of July 15

\section{Introduction}\label{sec-introduction}
As networked devices become more available, more capable, and more ubiquitous
in everyday life, tension mounts between users' desire to safeguard their 
personal information and government agencies' desire to use that personal 
information in their pursuit of criminals and terrorists.  Many people assert
that we are faced with an unpleasant, stark choice: Citizens can either have
control over their personal information, or they can have
law-enforcement and intelligence agencies with the tools that they need to
keep the country safe. We regard this stark choice as a false dichotomy and 
assert that, by deploying appropriate technology in the context of 
sound policy and the rule of law, we can have both privacy and security.

In this paper, we continue the development of accountable, privacy-preserving 
surveillance that we began in~\cite{sff-foci2014}. We require that government 
surveillance be conducted according to {\it open processes}, {\it i.e.}, 
unclassified procedures laid out in public laws that all citizens have the
right to read, to understand, and to challenge through the politicial process;
procedures that do not have these properties are referred to as {\it secret
processes}.  We distinguish between {\it targeted users}, who are 
under suspicion and the targets of properly authorized warrants, and
{\it untargeted users}; the latter are the vast majority of all 
users in any general-purpose, mass-communication system, and their private
information must be protected from government scrutiny. In \cite{sff-foci2014},
we applied these principles to the problem of {\it set intersection}.

We now apply them to {\it contact chaining}.
The goal is to use the topology of a {\it communication 
graph} ({\it e.g.}, a phone-call graph, email graph, or social network) 
to identify associates (or ``contacts'') of 
lawfully targeted users~\cite{techdirt}. 
Government agencies can then investigate those associates to determine whether
they deserve further attention.
It is useful to consider both direct contacts, 
{\it i.e.}, users who are neighbors in the communication graph, and
extended contacts, {\it i.e.}, users who are at distance $k$ in the 
communication graph, for an appropriate constant $k$.
%In a phone-call graph, if Alice calls Bob, 
%and Bob calls Charlie, then Alice and Bob are direct contacts (as are Bob and 
%Charlie), but Alice and Charlie are extended contacts (more precisely,
%contacts at distance 2).  
Without accountability and security mechanisms to
limit an investigation's scope, contact chaining in a mass-communication
network can sweep in a huge number of untargeted users.
In Section~\ref{sec-chaining}, we provide an accountable contact-chaining
protocol that bounds the scope of the search, uses encryption to protect 
untargeted users, and is computationally efficient (in that its time
complexity and communication complexity are both linear in the size of the 
output).

We posit that the
{\it Openness Principle} put forth in \cite{sff-foci2014} 
should govern all surveillance activity in a democracy.
\begin{compactenum}
\item[I]
Any surveillance or law-enforcement process
that obtains or uses private information
about untargeted users shall be
an open, public, unclassified process.
\item[II]
Any secret surveillance or law-enforcement processes shall use only:
\begin{compactenum}
\item[(a)] public information and
\item[(b)] private information about targeted users obtained under 
authorized warrants via open surveillance processes.
\end{compactenum}
\end{compactenum}
This principle can be viewed as a requirement that an open
``privacy firewall'' be placed between government agencies and citizens'
private information in a mass-communication network.  Processes that move
untargeted users' private information through the firewall must be open
processes.

We briefly present our contact-chaining results in 
Section~\ref{sec-chaining} and our open questions and future directions
in Section~\ref{sec-future}.  More detail on the Openness
Principle, our results on contact chaining and set intersection, related 
work by others, and future directions can be found in 
\cite{sff-TR,sff-foci2014}.

### 2016-08-03 paper/wpes16/chaining.tex
WPES submission edit pass done, down to 4 pages with good formatting

@@
 
-Without mechanisms to preserve privacy, a contact chaining search can collect a surprisingly large group of users' information. For example, if the average 
+Without mechanisms to preserve privacy, a contact-chaining search can collect a surprisingly large group of users' information. For example, if the average 
 cell-phone user contacts 30 individuals within the period of the investigation,
-a contact-chaining search out to distance three would capture 27,000 users on average - or many more if a heavy phone user is swept up by the search.
-In such a large group, the vast majority of contacts will not be collaborators of the the targeted, primary suspect in the investigation.
-These untargeted users may nevertheless face government scrutiny, intrusive investigation, or a risk that their sensitive communications histories may be leaked accidentally.
+a contact-chaining search out to distance three would capture 27,000 users on
+average -- or many more if a heavy phone user is swept up by the search. In
+such a large group, the vast majority of contacts will not be collaborators of
+the targeted, primary suspect in the investigation. These untargeted users
+may nevertheless face government scrutiny, intrusive investigation, or a risk
+that their sensitive communications histories may be leaked accidentally.
 
 Despite this risk, 
-we recognize the potential law-enforce\-ment value of information about the social contacts of targeted invidivuals.
-Therefore, we propose a \emph{lawful contact chaining protocol}.
-This protocol permits multiple government agencies working together to provide oversight and accountability, as advocated in \cite{sff-foci2014}.
-Our protocol focuses on the case in which the government seeks information from multiple telecommunications providers about the communication graph formed by phone calls and text messages.
-Using this protocol, the agencies can retrieve a set of encrypted records from multiple telecoms, {\it each of which holds only part of a larger communication graph}.
-This set of encrypted data
-contains the identities of users within a certain distance of a target, but the identities cannot be decrypted unless the agencies cooperate.
-Under the lawful processes we propose, this cooperation would take the form of intersecton with other sets of encrypted data.
-These sets can come from privacy-preserving contact chaining, from cell-tower dumps, or from other sources of information about suspects.
-Importantly, while any set may contain encrypted data about many untargeted users, very few users will appear in \emph{all} the sets, and those few users will be suitable targets for further lawful investigation.
+we recognize the potential law-enforce\-ment value of information about the
+social contacts of targeted invidivuals. Therefore, we propose a \emph{lawful
+contact-chaining protocol}. Such a protocol permits multiple government agencies
+working together to provide oversight and accountability~\cite{sff-foci2014}.
+Our protocol focuses on the case in which the government seeks information from
+multiple telecommunications providers about the communication graph formed by
+phone calls and text messages. Using this protocol, the agencies can retrieve a
+set of encrypted records from multiple telecoms, {\it each of which holds only
+part of a larger communication graph}. This set of encrypted data 
+contains the identities of users within a certain distance of a target, but the
+identities cannot be decrypted unless the agencies cooperate. Under the lawful
+processes we propose, this cooperation would take the form of intersecton with
+other sets of encrypted data. These sets can come from privacy-preserving
+contact chaining, from cell-tower dumps, or from other sources of information
+about suspects. While any set may contain encrypted data about
+many untargeted users, few users will appear in \emph{all} the sets, and
+those few will be suitable targets for further lawful investigation.
 
-The same principles of oversight and accountability provided by multiple government agencies can apply to contact chaining searches in other types of communication graphs, such as the social network graph of Twitter or Facebook.
-These cases do not require our protocol, however, since if one provider knows the entire communication graph, it can compute the output of the protocol without any interaction.
+The same principles of oversight and accountability provided by multiple government agencies can apply to contact-chaining searches in other types of communication graphs, such as the social-network graph of Twitter or Facebook.
+These cases do not require our protocol, however: if one provider knows the entire communication graph, it can compute the output of the protocol without any interaction.
 
-\subsection{Protocols For Privacy-Preserving Contact Chaining}
+\subsection{Privacy-Preserving Contact Chaining}
 
@@
 
-We can assume that business phone numbers have many more contacts than personal phone numbers do.
-In most cases, knowing that two individuals have contacted the same business does not indicate that those individuals have a personal relationship.
-Therefore, the warrant also includes $d$, an upper bound on the degree of users that the agencies are willing to ``chain through.'' If a phone number has more than $d$ contacts, then the agencies do not follow paths to other users through that phone number in their search (but do include that number in the output).
-The agencies disregard $d$ for the initial target $x$, however, because they have already determined that contacts of $x$ are of potential interest, even if $x$ is a business.
+Business phone numbers often have many more contacts than personal
+phone numbers do, and knowing that two individuals have contacted
+the same business does not usually indicate
+a relationship between those individuals.
+Therefore, the warrant also includes $d$, an upper bound on the
+degree of users that the agencies will ``chain through.'' If a phone
+number has more than $d$ contacts, then the agencies do not follow paths to
+other users through that phone number in their search (but do include that
+number in the output). The agencies disregard $d$ for the initial target $x$,
+however, because they have already determined that contacts of $x$ are of
+potential interest, even if $x$ is a business.
 
@@
 Every phone number in this set must be encrypted with each of the agencies' public ElGamal keys. The agencies should all have the same output.
-
 The telecoms should not learn the agency's output.
@@
 
-With the encryptions of these phone numbers, the agencies can act as appropriate to further investigate them.
-In particular, the set of encrypted phone numbers can be intersected with, say, the encrypted numbers of people on a terrorist
+The agencies can act as
+appropriate to further investigate these encrypted phone numbers.
+The set of encrypted
+phone numbers can be intersected with, say, the encrypted numbers of people on
+a terrorist
 watch list~\cite{sff-foci2014}.
@@
 
-The agencies will represent their output as a list $\mathbf{C}$, containing agency ciphertexts.
-Each telecom $T$ will represent its output as a list $\mathbf{L}_T$, listing plaintext users served by that telecom whose information the agencies requested.
-The protocol is as follows:
+The agencies represent their output as a list $\mathbf{C}$ of agency
+ciphertexts. Each telecom $T$ represents its output as a list
+$\mathbf{L}_T$ of plaintext users served by that telecom whose
+information the agencies requested.  The protocol is as follows:
 
@@
 
-\item Otherwise, $T(a)$ encrypts each neighbor $b$ of $a$ under the public key of $T(b)$, creating a telecom ciphertext for $b$.
+\item Otherwise, $T(a)$ encrypts each neighbor $b$ of $a$ under $T(b)$'s public key, creating a telecom ciphertext for $b$.
 
@@
 
-\item If $\de(a)>d$ and $j\neq k$ (i.e.
-$a\neq x$), the agencies discard all telecom ciphertexts received for $a$'s neighbors (i.e., agencies refuse to sign these ciphertexts in future steps of the protocol, and do not send them on to the telecoms).
+\item If $\de(a)>d$ and $j\neq k$ (i.e. $a\neq x$), the agencies discard all
+telecom ciphertexts received for $a$'s neighbors (they refuse to sign
+these ciphertexts in future protocol steps, and do not send them to
+telecoms).
 
@@
 
-Note that the inner loop can be executed many times in parallel, up to the point of completely emptying $\mathbf{Q}$ at the beginning of the loop.
-Many messages to the same telecom can also be batched and sent together, thereby reducing the number of signing and verifying operations so that they depend only on $k$ and not on the size of the input or output.
+The inner loop can be executed many times in parallel, up to the
+point of completely emptying $\mathbf{Q}$ at the beginning of the loop. Many
+messages to the same telecom can also be batched and sent together, thereby
+reducing the number of signing and verifying operations so that they depend
+only on $k$ and not on the size of the input or output.
 
 Correctness and privacy of the basic protocol are argued 
-in~\cite[Section 4.2]{sff-TR}.
+in the longer technical report~\cite[Section 4.2]{sff-TR}.
 
-\subsection{Performance of Privacy-Preserving Contact Chaining Protocol}
+\subsection{Contact-Chaining Protocol Performance}
 
-We implemented the basic protocol in Java and tested the implementation's 
-running time, CPU time used, and data sent over the network. 
+\input{fig-chaining}
+
+We implemented the basic protocol in Java and tested its
+running time, CPU time, and network utilization.
 Our implementation uses the variant of our protocol in which the agencies 
@@
 sending all queries at any given distance from $x$ to the 
-telecoms at once in batches. This variant allows for greater parallelism. 
-All of the telecoms receive their batch of queries at the same time and 
-operate on those queries using eight parallel threads of computation.
+telecoms at once in batches, for greater parallelism. 
+All telecoms receive their batch of queries at the same time and 
+operate on those queries using eight parallel threads.
 
@@
 
-For our underlying communication graph, we used an a\-no\-ny\-mized data set of 1.6 million users from Pokec, a Slovakian social network~\cite{snapnets}.
-To replicate the multi-provider environment, we assigned each user to one of four telecom servers.
-The telecoms were each given a different number of the users, in proportion to the subscriber base of the largest four telecoms in the world~\cite{mobiforge}.
+For our contact graph, we used an anonymized data set of 1.6
+million users from Pokec, a Slovakian social network~\cite{snapnets}. To
+simulate multiple providers, we assigned each user to one of four
+telecom servers.
+Each telecom server was given a different number of the users,
+in proportion to the subscriber bases
+of the world's largest four telecoms~\cite{mobiforge}.
 
-These results are important in evaluating how practical our lawful contact-chaining protocol would be it were put into practice by government agencies and telecoms.
-However, our data set is relatively small compared to the data\-ba\-ses held by real telecommunications companies, and each company handles that data using different technologies.
-The absolute running time and CPU usage of executing this protocol could vary from telecom to telecom.
-Therefore, we also produced a implementation of the contact-chaining protocol which omits all cryptographic operations.
-This version of the protocol does not preserve the privacy of users.
-By comparing the performance of our lawful contact-chaining protocol with the zero-cryptography contact-chaining protocol, however, we can get a sense of the ``cost of privacy and accountability.''
+These results help in evaluating how practical our lawful
+contact-chaining protocol would be in practice.
+However, our data set is small compared to
+the data\-ba\-ses held by real telecommunications companies, each company
+handles that data using different technologies, and absolute costs
+might vary.
+Therefore, we also produced a implementation of the contact-chaining protocol
+that omits all cryptographic operations, and does not
+preserve the privacy of users. By comparing the performance of our lawful
+contact-chaining protocol with the zero-cryptography protocol,
+we can get a sense of the ``cost of privacy and accountability.''
 
@@
 
-%NOTE: Adding blank lines to this environment will interfere with the formatting.
-\begin{figure*}[t]
-\centering
-\begin{subfigure}{0.66\columnwidth}
-\centering
-\begin{tikzpicture}[scale=0.66]
-\begin{loglogaxis}[
-	title={Protocol Runtime},
-	title style={font=\Large,},
-	xlabel={Ciphertexts in Result},
-	ylabel={Running Time [min]},
-	ylabel style={overlay},
-	ticklabel style = {font=\large},
-	xmin=10, xmax=1000000,
-	ymin=0.01, ymax=100,
-	%xtick={10, 100, 1000, 10000, 100000},
-	%ytick={0.01, 0.1, 1, 10, 100, 1000},
-	%log ticks with fixed point,
-	legend pos=north west,
-	ymajorgrids=true,
-	xmajorgrids=true,
-	grid style=dashed,
-	legend style={cells={anchor=west}},
-]
-\addplot[
-	color=blue,
-	mark=o,
-	only marks,
-	mark size=1.5pt,
-	]
-	table [x=Ciphertexts, y=RunningTime, col sep=comma] {chainingrsa.csv};	
-\addplot[
-	color=red,
-	mark=square,
-	only marks,
-	mark size=1.5pt,
-	]
-	table [x=Ciphertexts, y=RunningTime, col sep=comma] {chainingnocrypto.csv};
-\legend{Lawful contact-chaining, Zero-crypto}
-\end{loglogaxis}
-\end{tikzpicture}
-%\captionsetup{justification=centering}
-%\caption{Protocol Runtime}
-\label{fig:runtime}
-\end{subfigure}\hfill
-\begin{subfigure}{0.66\columnwidth}
-\centering
-\begin{tikzpicture}[scale=0.66]
-\begin{loglogaxis}[
-	title={All-Telecom CPU Time},
-	title style={font=\Large,},
-	xlabel={Ciphertexts in Result},
-	ylabel={Total CPU Time [min]},
-	ylabel style={overlay, anchor=north,},
-	ticklabel style = {font=\large},
-	xmin=10, xmax=1000000,
-	ymin=0.1, ymax=1000,
-	%xtick={10, 100, 1000, 10000, 100000},
-	%ytick={0.01, 0.1, 1, 10, 100, 1000},
-	%log ticks with fixed point,
-	legend pos=north west,
-	ymajorgrids=true,
-	xmajorgrids=true,
-	grid style=dashed,
-	legend style={cells={anchor=west}},
-]
-\addplot[
-	color=blue,
-	mark=o,
-	only marks,
-	mark size=1.5pt,
-	]
-	table [x=Ciphertexts, y=CPUTime, col sep=comma] {chainingrsa.csv};
-\addplot[
-	color=red,
-	mark=square,
-	only marks,
-	mark size=1.5pt,
-	]
-	table [x=Ciphertexts, y=CPUTime, col sep=comma] {chainingnocrypto.csv};
-\legend{Lawful contact-chaining, Zero-crypto}
-\end{loglogaxis}
-\end{tikzpicture}
-%\captionsetup{justification=centering}
-%\caption{CPU Time}
-\label{fig:cputime}
-\end{subfigure}\hfill
-\begin{subfigure}{0.66\columnwidth}
-\centering
-\begin{tikzpicture}[scale=0.66]
-\begin{loglogaxis}[
-	title={Data transferred},
-	title style={font=\Large,},
-	xlabel={Ciphertexts in Result},
-	ylabel={Data transferred [MB]},
-	ylabel style={overlay, anchor=north,},
-	ticklabel style = {font=\large},
-	xmin=10, xmax=1000000,
-	ymin=0.1, ymax=10000,
-	%xtick={10, 100, 1000, 10000, 100000},
-	%ytick={0.01, 0.1, 1, 10, 100, 1000},
-	%log ticks with fixed point,
-	legend pos=north west,
-	ymajorgrids=true,
-	xmajorgrids=true,
-	grid style=dashed,
-	legend style={cells={anchor=west}},
-]
-\addplot[
-	color=blue,
-	mark=o,
-	only marks,
-	mark size=1.5pt,
-	]
-	table [x=Ciphertexts, y=Bytes, col sep=comma] {chainingrsa.csv};	
-\addplot[
-	color=red,
-	mark=square,
-	only marks,
-	mark size=1.5pt,
-	]
-	table [x=Ciphertexts, y=Bytes, col sep=comma] {chainingnocrypto.csv};
-\legend{Lawful contact-chaining, Zero-crypto}
-\end{loglogaxis}
-\end{tikzpicture}
-%\captionsetup{justification=centering}
-%\caption{Network Data}
-\label{fig:data}
-\end{subfigure}
-\captionsetup{justification=centering}
-\caption{Performance of Lawful Contact-Chaining}
-\label{fig:performance}
-\end{figure*}
-
-Our implementation of lawful contact-chaining performed well.
-Our experiments showed a linear relationship between the number of ciphertexts in the output and the running time, CPU time, and data usage of the protocol.
-We display graphs of our recorded data in Figure~\ref{fig:performance}.
+Our implementation of lawful contact-chaining performed well,
+showing a linear relationship between the number of ciphertexts in the output
+and the running time, CPU time, and data usage of the protocol. We display
+graphs of our recorded data in Figure~\ref{fig:performance}. 
 %Taking the average of all cases with $d>25$, the telecoms used 58.2 ms of CPU time per ciphertext.
@@
 
-We found that our protocol was able to process, in the average case, 197.4 ciphertexts per second.
-To return to our example from earlier of a network with an average of 30 contacts per user, a lawful contact-chaining search with $k=2$ would have 900 users in the output, and a search with $k=3$ would have 27,000 users in the output.
-To compare these times to some of our actual experiments, we found that a search that returned 937 ciphertexts took 6.86 seconds to run, and a search that returned 27,338 ciphertexts took 109.55 seconds to run.
+We found that our protocol was able to process about 197
+ciphertexts per second on average.
+Returning to our example of a network with
+an average of 30 contacts per user, a search with $k=2$
+would have 900 users in the output, and a search with $k=3$ would have 27,000
+users in the output. In our experiments,
+we found that a search that returned 937 ciphertexts took 6.86 seconds to run,
+and a search that returned 27,338 ciphertexts took 109.55 seconds to run.
+
 %To provide another point of comparison, recall that, in~\cite{sff-foci2014}, we studied the ``High Country Bandits'' case, in which the FBI performed an intersection of 150,000 phone number to help solve a series of bank robberies.
@@
 
-More detailed performance analysis is presented in~\cite[Section 4.3]{sff-TR}.
+More detailed analysis is presented in~\cite[Section 4.3]{sff-TR}.

### 2016-08-03 paper/wpes16/intro.tex
WPES submission edit pass done, down to 4 pages with good formatting

@@
 lawfully targeted users~\cite{techdirt}. 
-Government agencies can then investigate those associates to determine whether
+Agencies can then investigate those associates to determine whether
 they deserve further attention.
@@
 network can sweep in a huge number of untargeted users.
-In Section~\ref{sec-chaining}, we provide an accountable contact-chaining
+Section~\ref{sec-chaining} presents an accountable contact-chaining
 protocol that bounds the scope of the search, uses encryption to protect 
-untargeted users, and is computationally efficient (in that its time
-complexity and communication complexity are both linear in the size of the 
-output).
+untargeted users, and is computationally efficient,
+with time and communication complexity linear in the size of the output.
 
@@
 \item[(b)] private information about targeted users obtained under 
-authorized warrants via open surveillance processes.
+authorized warrants via open processes.
 \end{compactenum}
